### 2020-05-17 rebuttal/mobihoc2020_rebuttal_767.tex
first commit

\documentclass[nonacm,sigconf]{acmart}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}

\begin{document}

\title{Rebuttal for ACM MobiHoc 2020 Submission}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% DO NOT CHANGE the meta setting of this template such as line spacing, font size, etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% You can update the followings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Paper Information}

{\bf \noindent Paper Title:} ``COFlood: Concurrent Opportunistic Flooding in Asynchronous Duty Cycle Networks''

{\bf \noindent Paper \#: 767}

%\noindent Thanks for three reviewers' constructive and insightful comments.

\section{Response to Reviewer A}
Thanks for your constructive and insightful comments.

\textbf{(2.1)} In section 3.1, there is no proof that the minimization problem is NP-hard. Be mindful that you need to show a polynomial reduction for the minimum weight connected dominating set problem to this problem.

\textbf{Response:} Indeed, we do not provide the proof details to reduct our problem to the MWCDS problem. For simplicity, we present the specific definition of our problem, then use an illustrative example to show our problem is kind of MWCDS problem. We can add the details in the next version.

\textbf{(2.2)} It is very hard to understand what the algorithm does from the description in 3.2. Two issues contribute to the challenge. First there is no overview of how the sender selection works. Second the three algorithms refer to each other and the cross reference adds to the challenge for readers.

\textbf{Response:} 
%下面这句话是不是可以不说？直接解释我们的算法就行？
%We fully understand your points about our algorithm descriptions. 
The basic structure of our algorithm is similar with that of distance vector routing algorithm which adopts Bellman-Ford equation to update routing entries, but a node needs to maintain two network metrics (e.g., EBQ and PBT). We split the whole algorithm to three parts to make each of them short. Algorithm 1 summarizes the whole algorithm operated by a node in a distributed manner, then Algorithm 2 and 3 present the strategies to update the node's EBQ and PBT metrics according to the new received neighbors' metrics.

\section{Response to Reviewer B}
Thanks for your constructive and insightful comments.

\textbf{(3.1)} The performance is evaluated by two indicators, completion time and radio duty cycle. It may be more convincing to evaluate by more indicators.

% 不知道reviewer是不是准确知道tail length含义？
\textbf{Response:} That is true. It would be more comprehensive to evaluate our protocol with more indicators such as the number of concurrent senders, the number of retransmissions, the tail length of concurrent transmission.

\textbf{(3.2)} In the first paragraph of Section 3.2, the sentences related to EBQ may be not very accurate. EBQ is related to both variables. %i.e., expected time of preamble packet broadcast and number of children. 
One must be controlled for the other variable.

\textbf{Response:} We agree with your comments. We can modify the sentences to remove the ambiguity.

%\textbf{(3.3)} There are some grammatical errors and typos which need to be corrected. The notation $i$ may be confused in Equation (5) of $p_i$ and the loop variable $i$. The values of W in Figure 6(b)(c) leave out the factor $T$.

%\textbf{Response:} Thanks again for your careful reading.

\section{Response to Reviewer C}
Thanks for your constructive and insightful comments.

\textbf{(4.1)} %The main objective of this paper is to develop a broadcasting scheme in asynchronous duty cycle networks with minimum expected completion time. The network is represented by an edge-weighted graph in which each edge weight is the packet reception ratio of the corresponding wireless link. A broadcasting scheme is then represented by a rooted spanning tree. The expected delay of each non-leaf node is the maximum expected delay of the links to its children.
The paper incorrectly uses the total expected delays of all non-leaf nodes as the completion time. While minimizing the total delay is a generalization of the minimum connected dominating set (instead of the minimum dominating set claimed in the paper) and is thus NP-hard, minimizing the completion time may have different computation hardness. Thus, the heuristics developed in this paper does not address the targeted broadcasting problem.

\textbf{Response:} That is true that our primary objective is to minimize the completion time, but we cannot directly model the completion time since our under-layer protocol~\cite{chase} does not rely on any time synchronization. 
%下面这个concurrent sender 与completion time高度相关是否可能有参考文献？如果有其他工作支撑一下，似乎说服力更强些？
Moreover, according to our empirical study in Section 2, we have observed that the number of concurrent senders is highly related to the completion time. 
Then, we mainly focus on developing the optimal strategy of concurrent sender selection. As shown in Section 3, our strategy consists of two parts. One is to select a small set of concurrent senders, which covers the whole network with the minimum transmissions. In this way, we guarantee both network coverage and the efficiency of concurrent broadcast. Indeed, this minimization problem is not the full picture of completion time minimization. Hence, based on the concurrent flooding tree, we further take the advantage of the early wake-up leaf nodes, which satisfy two opportunistic conditions, to further shorten the completion time.

\textbf{(4.2)} The model of the expected delay as the ratio of the sleep interval length to the expected packet reception ratio (PRR) is an over-simplification. It seems that the PRR only captures the impact of noise. However, when multiple nearby nodes transmit at the same time, a receiving node may suffer from wireless interference. The amount of wireless interference further depends on the choice of the rooted spanning tree. The paper totally ignores the impact of the wireless interference, and thus the simulation results does not reflect the real performance. In contrast, as mentioned in Section 1, the prior works did consider the impact of the interference. For example in~\cite{chase}, when several signals are overlapped, a receiver successfully receives the strongest signal when its signal strength is 3dBm larger than the sum of others and it comes no later than 160祍 than the earliest coming weak signal.

\textbf{Response:} We agree with you that the expected delay is easily affected if the interference is not carefully handled. To deal with the potential contention and collision, our protocol is sitting on \emph{Chase}~\cite{chase}. As you already noticed, \emph{Chase} enables efficient concurrent broadcast with capture effect. If the efficiency of concurrent broadcast is guaranteed, the interference among multiple neighbor senders has neglectable influence on the expected delay. During the construction of our concurrent flooding tree, we improve the efficiency of concurrent broadcast by minimizing the total transmissions. Therefore, we can estimate the expected delay by only considering the PRR.

\textbf{(4.3)} The performance analysis with only empirical study is a little bit weak.

\textbf{Response:} Thanks for your comment. We will add more theoretic analysis about our proposed algorithms in the next version.

\bibliographystyle{ACM-Reference-Format}

\bibliography{main}

\end{document}

### 2020-05-17 rebuttal/mobihoc2020_rebuttal_template.tex
first commit

--- 2020-05-17 rebuttal/mobihoc2020_rebuttal_767.tex
@@
 
-%\noindent Thanks for three reviewers' constructive and insightful comments.
+Thanks for three reviewers' constructive and insightful comments.
 
 \section{Response to Reviewer A}
-Thanks for your constructive and insightful comments.
+%Thanks for your constructive and insightful comments.
 
@@
 
-\textbf{Response:} Indeed, we do not provide the proof details to reduct our problem to the MWCDS problem.
+\textbf{Response:} Indeed, we do not provide the detailed proof to reduct our problem to the MWCDS problem.
 For simplicity, we present the specific definition of our problem, then use an illustrative example to show our problem is kind of MWCDS problem.
-We can add the details in the next version.
+We will add the detailed proof in the next version.
 
@@
 
-\textbf{Response:} 
-%下面这句话是不是可以不说？直接解释我们的算法就行？
-%We fully understand your points about our algorithm descriptions. 
+\textbf{Response:} We fully understand your points about our algorithm descriptions.
 The basic structure of our algorithm is similar with that of distance vector routing algorithm which adopts Bellman-Ford equation to update routing entries, but a node needs to maintain two network metrics (e.g., EBQ and PBT).
-We split the whole algorithm to three parts to make each of them short.
-Algorithm 1 summarizes the whole algorithm operated by a node in a distributed manner, then Algorithm 2 and 3 present the strategies to update the node's EBQ and PBT metrics according to the new received neighbors' metrics.
+We split the whole algorithm to 3 parts to make each of them short.
+Algorithm 1 summarizes the whole algorithm operated by a node in a distributed manner, then Algorithm 2 and 3 present the strategies to update the node's EBQ and PBT metrics with the new received neighbor metrics.
 
 \section{Response to Reviewer B}
-Thanks for your constructive and insightful comments.
+%Thanks for your constructive and insightful comments.
 
@@
 
-% 不知道reviewer是不是准确知道tail length含义？
-\textbf{Response:} That is true.
-It would be more comprehensive to evaluate our protocol with more indicators such as the number of concurrent senders, the number of retransmissions, the tail length of concurrent transmission.
+\textbf{Response:} That is true. It would be more comprehensive to evaluate our protocol with more indicators such as tail length, retransmission counter.
 
-\textbf{(3.2)} In the first paragraph of Section 3.2, the sentences related to EBQ may be not very accurate.
-EBQ is related to both variables.
-%i.e., expected time of preamble packet broadcast and number of children.
+\textbf{(3.2)} The sentences in the first paragraph in Section 3.2 may be not very accurate.
+EBQ is related to both variables, i.e., expected time of preamble packet broadcast and number of children.
 One must be controlled for the other variable.
 
-\textbf{Response:} We agree with your comments. We can modify the sentences to remove the ambiguity.
+\textbf{Response:} We agree with your comments. We should modify the sentences to remove the ambiguity.
 
@@
 \section{Response to Reviewer C}
-Thanks for your constructive and insightful comments.
+%Thanks for your constructive and insightful comments.
 
@@
 \textbf{Response:} That is true that our primary objective is to minimize the completion time, but we cannot directly model the completion time since our under-layer protocol~\cite{chase} does not rely on any time synchronization.
-%下面这个concurrent sender 与completion time高度相关是否可能有参考文献？如果有其他工作支撑一下，似乎说服力更强些？
-Moreover, according to our empirical study in Section 2, we have observed that the number of concurrent senders is highly related to the completion time. 
+Moreover, according to our empirical study, we have observed that the number of concurrent senders is highly related to the completion time.
 Then, we mainly focus on developing the optimal strategy of concurrent sender selection.
@@
 Indeed, this minimization problem is not the full picture of completion time minimization.
-Hence, based on the concurrent flooding tree, we further take the advantage of the early wake-up leaf nodes, which satisfy two opportunistic conditions, to further shorten the completion time.
+Hence, based on the concurrent flooding tree, we further take the advantage of the early wake-up leaf nodes, which satisfy two opportunistic conditions, to shorten the completion time.
 
@@
 In contrast, as mentioned in Section 1, the prior works did consider the impact of the interference.
-For example in~\cite{chase}, when several signals are overlapped, a receiver successfully receives the strongest signal when its signal strength is 3dBm larger than the sum of others and it comes no later than 160祍 than the earliest coming weak signal.
+For example in~\cite{chase}, when several signals are overlapped, a receiver successfully receives the strongest signal when its signal strength is 3dBm larger than the sum of others and it comes no later than 160µs than the earliest coming weak signal.
 

### 2020-05-17 abstract-old.tex
first commit

\begin{abstract}
\label{abstract}
In energy constraint wireless networks, radios usually operate in duty cycle mode. With low maintenance cost, asynchronous duty cycle management is widely adopted. Due to the diverse active schedules of different nodes, to achieve fast network flooding is challenge. Recently, concurrent flooding is a promising approach to speed up network flooding in asynchronous duty cycle networks. However, when all nodes are involved in flooding,
%Although it cannot miss any early delivery chances when all nodes are involved in flooding, the efficiency of concurrent flooding may be significantly degraded, especially in dense networks. The energy is also overused.
the key is an efficient approach to select a set of senders to simultaneously achieve fast concurrent flooding and efficient energy consumption. In this paper, we propose COFlood (Concurrent Opportunistic Flooding), which achieves the fast and energy-efficient concurrent flooding by opportunistically selecting senders based on an energy optimal flooding tree. The flooding tree structure provides full network coverage and keeps a low energy baseline. Then, with no extra control overhead, the opportunistic sender selection further filters out the additional early wake-up opportunities and bounds the number of total senders. We evaluate COFlood on two real testbeds. The results show both completion time and energy consumption are greatly reduced on the two testbeds.
\end{abstract}

### 2020-05-17 design.tex
first commit

\section{System Design}
\label{sec-design}
We designed an end-to-end network architecture consisting of several identical layers in which:
	Each input image (or each lane from the output of the previous layer) is assigned to its own lane and processed by several convolutional layers. These layers share parameters across channels; however, each image is processed individually and do not interact with each other in this stage. Each channel will present a feature map of n channels.
	The features extracted from all layers are merged broadwise with the following function:

    $${x'_k=\sum x_ie^{kx_i}/\sum e^{kx_i}}$$

Where k varies from -1 to 1. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to a process similar to max operator and k=${-\infty}$ leads to min operator. This process merges information from every lane into one. The output is n channels for each value of k. 
	The original input images are accessed again. These images are also processed separately by several convolutional layers (sharing parameters across lanes) to extract features. The output of these images (m channels each) are stacked with the n channels from step 2) as m+n channels each lane. Some more convolution and an upscaling layer may follow, merging the data more thoroughly. These will be the input for the next layer.
The above 3 steps are stacked as one layer. The functional network often consists of 5 to 8 layers to achieve 4x super resolution. The network ends with a merging process similar to the 2) step and a few more layers of convolution. The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.

\begin{figure}
 \centering
    \includegraphics[width=0.375\textwidth]{./pic/system}
    \caption{Network Architecture of SRPeek.}
    \label{fig-system}
\end{figure}

### 2020-05-17 evaluation.tex
first commit

\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions.
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters. On average the model achieves … accuracy.
Data	Daytime,1.2m… 	Nighttime,1.2m…	Daytime,1.4m…					
Difference(PSNR)								
OCR Accuracy								
We compare the results to discover the influence of the surrounding environment: The model performs best in nighttime and strong sunlight may decrease its ability…
\subsection{Performance In Random Environment}
We train the model with data captured in 10 different environments and test its ability in another 10 different environments. The model achieves … accuracy. It has a better performance in daytime…

Data	Training Environment  	Test
Environment1	Test2	Test3				
Difference(PSNR)								
OCR Accuracy								
\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
Groups of Data	All 10	Night only	1.2m distance only	Direct angle only				
Difference(PSNR)								
OCR Accuracy								
Variations in light parameter in training data is crucial to a robust model. Variations in distance is not so influential to the results.
\subsection{Data Amount}
We use less numbers of images in each group of data and see the performance of the models.
Amount	60,000	40,000	30,000	10,000				
Difference(PSNR)								
OCR Accuracy								
\subsection{Model Size}
We cut the model size for better performance in smartphones. We modify the number of layers, channels in convolution layers, and output channels in merging processes.
Model	Full	5 layer	32channel					
Parameter Count								
Total training time								
Difference(PSNR)								
OCR Accuracy								
\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results.
Model	Ours	SRCNN						
Parameter Count								
Difference(PSNR)								
OCR Accuracy

\section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with … smartphone for the attacker and … smartphone for the victim. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
Scenario	Home	Office	Public Transport	Theater
Valid images				
Running time				
OCR Accuracy				
Human Recognition Accuracy(raw data)				
Human Recognition Accuracy(processed image)				
Human Recognition Time				
\subsection{Influence of distance}
We repeat our experiment in different distances and evaluate the accuracy.
Accuracy	Scenario	Home	Office	Public Transport	Theater
Distance					
1m					
1.2m					
1.4m					
1.6m					
2m					
\subsection{Influence of hand tremors}
We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort(Handheld camera). We process these images and let them read the results. We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions(Handheld target). The user may freely interact with the phone when reading. We capture images of the phone at the same time to see how our system deal with a moving target screen.
Scenario	Stationary	Handheld camera	Handheld target	‘Handheld camera and target
Valid images				
Running time				
OCR Accuracy				
Human Recognition Accuracy(raw data)				
Human Recognition Accuracy(processed image)				
Human Recognition Time				
\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant perform several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters. The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone. For the first two tasks,we ask the observing participant several questions to test if he/she have collected the vital information(e.g. the name or the location mentioned in the text). For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric.
Scenario	Read text	Type text	Enter PIN	Enter complex password
Accuracy				
Accuracy per character				
Human Recognition Accuracy(raw image)				
Human Recognition Accuracy(Processed image)				
Human Recognition Time				
\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario.
\section{Limitations}
\subsection{Image Capturing Ability}
Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in models 3~4 years old. Heavily used phones also performs less than ideal when capturing images in burst mode. Also, when capturing images the user need to hold their phone as still as possible to avoid motion blur and assist image alignment. The user also has to keep a sharp focus on the target phone.
\subsection{Processing Ability}
To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time. As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
\subsection{Motion and Tremors}
In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often. However some users may tilt their phones during interactions—especially when typing with one hand. Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.

### 2020-05-17 implementation.tex
first commit

\section{Implementation and Training}

\label{sec-implementation-and-evaluation}

\subsection{Experiment Setting}
Collect data with a stationary smartphone at 1.5m range…
Display random characters on screen, with a box surrounding it for supplementary alignment…
Takes 6 hours to gather one set of training data…
\subsection{Model Specifications}
8 layers with two 2x upsampling layers; 64 channels…
\subsection{Training Process}
Collect 10 sets of data at different surroundings: different angles, distance, font size and color…
Step 1. Train the network with each one of the 10 sets, the model should fit perfectly…
Step 2. Select the set of data the model is best adapted to, and add a small percentage of images from another set…
Step 3. When the model stabilizes again, gradually increase the percentage…
Step 4. Add another set of data, and repeat step2 and 3, until all data is used.

### 2020-05-17 introduction.tex
first commit

\section{Introduction}
\label{sec-introduction}

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some concerns of privacy have arisen about nearby parties peeking at our screen, or ‘shoulder surfing’. Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet.

On the other hand, many works in this area are built on a threat model of an attacker observing with his/hers naked eye, as they assume that the attacker is not malicious and merely take several peeks out of curiosity. However, it is the rare but malicious and prepared attacker that can do the most harm, and leave aside special equipment, if we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. Moreover, smartphone cameras have seen great improvement these years, and as a highly-accessible ‘extension of the eye’, it is possible that ‘shoulder surfers’ peek at others’ screen through their smartphone lenses to obtain critical information like passwords or private e-mails. What’s more, recent developments in the field of super resolution (SR) pose a greater threat to smartphone privacy. Attackers can take multiple snapshots of the victim’s screen and process them with multiple image super resolution algorithms in real time, making them able to see clearly while keeping a longer distance. However, most SR methods are designed for and trained on naturally taken images \cite{nasrollahi2020deep} \cite{lyn2020image}; few works have focused on reconstructing blurry snapshots taken at extreme distances, and a new architecture needs to be designed.

To explore this rarely studied privacy threat of the attacker looking through a smartphone camera, we have developed a holistic system for shoulder surfing. The fictional attacker captures multiple images of the victim’s screen in burst mode from his smartphone, and enhances its resolution with our multi-frame super resolution neural network. The network is designed and trained for this purpose, targeting several blurry images taken in quick succession of a screen at a distance. As the information of interest is mostly displayed on screen in the form of text (e.g. passwords or e-mails), our network focuses on reconstructing text, specifically, Chinese characters, English letters, and numbers. The system is deployed on a smartphone for demonstration, capturing and processing images at real time. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition of video clips.

\subsection{Difficulties}
There are several difficulties unique to this SR application. The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.

Another difficulty unique to our task is the subject—mainly, Chinese characters. Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/zeros}
    \caption{ Fig 1. 4 photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. Note how they exhibit different blurriness and display no consistency between neighboring frames.}
	\label{fig-zeros}
\end{figure}

\subsection{Network Architecture} 
 As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach. Most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Figure~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others. If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.

Considering the unique challenges of our application, we believe that if these images are processed iteratively, alternating between the following two processes, our network will be able to solve this ‘jigsaw puzzle’:

\begin{enumerate}
  \item Every single image of the input collection will be processed solely (by several layers of CNN), with access of the output of step (2) of the last iteration;
  \item The processed results will be merged (with weighted averaging methods) and distributed to each photo for the next iteration.
\end{enumerate}

This architecture is beneficial to our task. On one hand, the deep learning part is assigned to each single image, reducing computational complexity and parameter growth, while receiving a global view of all the images, renewed at each layer, thanks to the merging process; on the other hand, information can be shared horizontally with weighted averaging methods, meaning no consideration of sequential order and no reliance of consistency between neighboring frames. Thus, this architecture solves the dilemma mentioned above, and proves perfectly functional in our application.

The details of our architecture will be discussed in section 4.

This paper makes the following contributions:

\begin{itemize}
  \item	We propose SRPeek, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images. This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
  \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shouler surfing senarios.
  \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.
\end{itemize}

% describe the organization of the paper
The rest of the paper is organized as follows. Section 2 describes the threat model of our  carefully studies the performance of state-of-the-art concurrent flooding. The detailed design of COFlood protocol is shown in Section~\ref{sec-design}. We show the implementation details and evaluation results in Section~\ref{sec-implementation-and-evaluation}. The related work is introduced in Section~\ref{sec-related-work}. Finally, we conclude our work in Section~\ref{sec-conclusion}.

### 2020-05-17 related_work.tex
first commit

\section{Related Work}
\label{sec-related-work}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily in recent years. Surveys of shoulder surfing provides evidence of this behavior in real world \cite{eiband2017understanding} \cite{goucher2011look}, often more efficient than expected\cite{kwon2013covert}. Various techniques and systems have been designed to mitigate this threat. Some systems sense malicious passers-by and hide information \cite{brudy2014anyone} or warn the user\cite{saad2018communicating}; others modify the user interfaces to create honeypots (for passwords)\cite{chakraborty2014tag}, confuse unauthorized parties\cite{wiedenbeck2006design}, or making the interactions invisible\cite{kumar2007reducing} or unreadable from a distance\cite{Chun2019Keep}. Most of the works designing defenses against shoulder surfing assume that the attacker is a casual passer-by, taking occasional peeks with his/hers naked eye, as is the case most of the time\cite{eiband2017understanding}. However, it is the malicious ones, although few, that can utilize the information (passwords, business correspondence, etc.) they obtained to do real harm. On the other hand, the threat model of tool-assisted shoulder surfing is also studied. Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}. Maggi, et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}, but without the help of SR techniques, this method can only function when the attacker is standing at close range, which is a barely practical scenario. With the development of smartphone camera, processing ability, and SR technology over the years, we propose a stronger shoulder surfing system in which attackers can successfully obtain information while keeping a distance to avoid suspicion, and prove that this threat is eminent in our daily life.

\subsection{Super Resolution}
Image super-resolution is the process of reconstructing an image with a higher spatial resolution. Single image super-resolution techniques accept a single low-res image as input, and based on its structural pattern, self-similarity \cite{suetake2008image}, or previous knowledge of the genre of the image, deduces missing information and reconstructs the missing pixels to form a sharp, high-res image. On the other hand, multiple image super-resolution techniques work on a set of pictures on the same scene, e.g. multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip. Although they picture the same scene and are mostly identical to each other, those low-res pictures can be viewed as replicas of a certain high-res scene with random pixels blurred and removed, and multiple image super-resolution algorithms reconstruct the high-res scene by merging these incomplete information sources, often exhibiting better performance than single image super-resolution.

As mentioned above, multiple image super-resolution algorithms are based on the assumption that all input images are reflections of the same scene. It can be assumed that there exists a high-res image H, and each input low-res image Li is a version of an aliased, blurred, downsampled and noised H. By modelling the alias, blur and noise effects, and comparing these low-res inputs, we can grasp an estimation of those degrading effects and neutralize them, and the output of our super-resolution algorithm will be a high-res image H’ with the most possibility to single-handedly generate all the input images Li via the aliasing, blurring, downsampling and noising processes.

Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem. Early works focus on the analysis of the images on frequency or special domains, focusing on their pixel level differences and merging their information. Spatial domain methods mostly work on the interpolation approach, trying to insert new pixels between pixels of the low-res images. One of the well-known methods in the spatial domain is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images with gradient decent methods. On the other hand, frequency domain approaches focus on the Fourier transform of the images, and reconstruct high-res images based on patterns of the images in the frequency domain. Downsampling processes remove high-frequency components of the images, preserving low-frequency components; Noises often exists in a certain frequency band and can thus be identified and removed. By assuming that the high-res scene is band-limited, with CFT and DFT transformations, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time. A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc. and achieve best performance only in their own field.

More recent works of Super Resolution are often based on deep learning approaches. In 2016, SRCNN \cite{dong2015image} was developed from CNN replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. This work focuses on single image super-resolution, as the neural network accepts a single image as input. As Generative Adversarial Networks (GAN) were proposed, the network good at constructing images pleasant to the human eye was also introduced into the domain of super resolution \cite{ledig2017photo}. These networks generate photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene. Note that super resolution is an ill-posed problem, that is, we do not have a ‘ground truth’ to begin with, and traditional evaluation methods, e.g. mean square error (MSE) might not be suitable according to the application. Although SRGAN might score slightly lower on MSE, it can reconstruct more high-frequency and realistic details and score much higher on the mean opinion score (MOS). However, when published, the above works were limited to single input images. Because of increasing complexity and training difficulty, we cannot directly modify these super resolution neural networks to accept multiple images as input. There are also various works adapting neural networks to perform multi-image SR tasks. The most common variation is video SR\cite{shi2016real, kappeler2016video}, accepting complete video clips as input, and functioning on the similarity between frames. The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily. Other works face image groups without consistency or sequential information, e.g. satellite images. To achieve appreciable results, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures. They commonly function by merging the results of single image SR algorithms to efficiently utilize input information\cite{kawulok2019deep}, or building a multi-image network to create a course view and support it with single image SR networks\cite{8834937}. These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.

However, the methods mentioned above are not suitable for our application and we need a novel approach. The blurriness of our photos exceeds the processing ability of non-learning methods; furthermore, these photos are extremely blurred, defocused and full of noise so that few information can be extracted from them via single image SR methods; The adjacent frames display drastically different blurring patterns so that they lack consistency between adjacent frames. Only from an overall view of all the images can we distinguish noise from facts, and we need a network that can comprehend the similarities and differences between each frame to recover the buried information, and indeed, building an end-to-end multi-image SR network without assuming sequential consistency between frames is still a very much underexplored field of study, and our work aims at filling that gap.

### 2020-05-17 threat_model.tex
first commit

\section{Threat Model}
\label{sec-threat-model} 
The objective of the attacker is to acquire the information on the smartphone screen of the victim, reading the numbers and English/Chinese characters on screen, with the help of his smartphone’s camera equipped with the SR network we designed. To reduce suspicion, the attacker will probably position himself at about 1.5 meters from the target screen, at an angle within 30 degrees. At this distance few people will be on guard of strangers even when viewing sensitive data or entering passwords. The attacker may raise his phone (one of the latest models with powerful lenses and computational abilities), pretending to be interacting with it, while pointing his camera at the victim. He will extend his zooming ability to the maximum, try to get a focus on the screen (which is difficult to achieve), and take 20 to 30 images in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process will take about 2 seconds, and we assume the information on the screen will not change in this period, nor the position of the screen. These images will be fed to a multi-frame SR network and the result, one single image with higher resolution, will be displayed on the screen soon afterwards. The characters in the image will be reconstructed to the best of the network’s ability, and if successful, the attacker will be able to decipher the information. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.

### 2020-05-17 code/chase/apps/ChaseTest/ChaseEnergyMsg.java

@@ -1,0 +1,422 @@
+/**
+ * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
+ * This class implements a Java interface to the 'ChaseEnergyMsg'
+ * message type.
+ */
+
+public class ChaseEnergyMsg extends net.tinyos.message.Message {
+
+    /** The default size of this message type in bytes. */
+    public static final int DEFAULT_MESSAGE_SIZE = 10;
+
+    /** The Active Message type associated with this message. */
+    public static final int AM_TYPE = 77;
+
+    /** Create a new ChaseEnergyMsg of size 10. */
+    public ChaseEnergyMsg() {
+        super(DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /** Create a new ChaseEnergyMsg of the given data_length. */
+    public ChaseEnergyMsg(int data_length) {
+        super(data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseEnergyMsg with the given data_length
+     * and base offset.
+     */
+    public ChaseEnergyMsg(int data_length, int base_offset) {
+        super(data_length, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseEnergyMsg using the given byte array
+     * as backing store.
+     */
+    public ChaseEnergyMsg(byte[] data) {
+        super(data);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseEnergyMsg using the given byte array
+     * as backing store, with the given base offset.
+     */
+    public ChaseEnergyMsg(byte[] data, int base_offset) {
+        super(data, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseEnergyMsg using the given byte array
+     * as backing store, with the given base offset and data length.
+     */
+    public ChaseEnergyMsg(byte[] data, int base_offset, int data_length) {
+        super(data, base_offset, data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseEnergyMsg embedded in the given message
+     * at the given base offset.
+     */
+    public ChaseEnergyMsg(net.tinyos.message.Message msg, int base_offset) {
+        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
[…]

### 2020-05-17 code/chase/apps/ChaseTest/ChaseTest.h

@@ -1,0 +1,8 @@
+#ifndef CHASETEST_H_
+#define CHASETEST_H_
+
+typedef nx_struct {
+  nx_uint8_t data[100];
+} flood_payload_t;
+
+#endif

### 2020-05-17 code/chase/script/Indriya/deludge_power7_2/delay_analysis_contiki.pl

@@ -1,0 +1,157 @@
+@delay[3000];
+@is_cal[3000];
+@rec[3000];
+@src[3000];
+@hop[3000];
+@time_rec[3000];
+@src_delay[3000];
+
+@count[20];
+@avg_delay[20];
+@comp_time[20];
+
+@duty_cycle[150];
+
+for ($i = 0; $i < 150; $i++) {
+	@duty_cycle[$i] = 0;
+}
+
+for ($i = 0; $i < 20; $i++) {
+	@delay[20+$i] = 0;
+	@time_rec[20+$i] = 0;
+	@is_cal[20+$i] = 1;
+	@rec[20+$i] = 1;
+	@hop[20+$i] = 0;
+}
+
+$log_file = "flood.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "seq_no") { next; }
+
+	$seq_no = @log[0];
+	if ($seq_no < 20) {
+		@rec[20+$seq_no] = 1;
+		$time_flood = @log[1] * 65536 + @log[2];
+		@time_rec[20+$seq_no] = $time_flood;
+	}
+}
+close fin;
+
+$log_file = "delay.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+	$seq_no = @log[1];
+	if ($seq_no < 20) {
+		@rec[$nodeid*20+$seq_no] = 1;
+        @src[$nodeid*20+$seq_no] = @log[2];
+        $tmp_time = @log[3] * 65536 + @log[4];
+        @time_rec[$nodeid*20+$seq_no] = $tmp_time;
+        $tmp_time = @log[5] * 65536 + @log[6];
+        @src_delay[$nodeid*20+$seq_no] = $tmp_time;
+	}
+}
+close fin;
+
+$log_file = "energy.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+    $total_time = @log[1] * 65536 + @log[2];
+    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-05-17 code/chase/script/chase/chase2/delay_analysis.pl

@@ -1,0 +1,108 @@
+@delay[500];
+@is_cal[500];
+@rec[500];
+@src[500];
+@time_rec[500];
+@src_delay[500];
+
+@count[10];
+@avg_delay[10];
+@com_time[10];
+
+@duty_cyle[50];
+
+for ($i = 0; $i < 10; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 10; $j++) {
+		@rec[$i*10+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 10) {
+        	@rec[$i*10+$seq_no] = 1;
+        	@src[$i*10+$seq_no] = @log[2];
+        	@time_rec[$i*10+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*10+$seq_no] = @log[5] * 65535 + @log[6];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 10) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
+        $radio_on_time = @log[3]*65535 + @log[4];
+        $time_now = @log[1]*65535 + @log[2];
+        @duty_cycle[$i] = $radio_on_time / $time_now;
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 10; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*10+$i] == 1) {
+			if (@is_cal[$j*10+$i] == 0) {
+				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
+					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
[…]

### 2020-05-17 code/chase/script/chase/chase_payload20/delay_analysis.pl

@@ -1,0 +1,108 @@
+@delay[2000];
+@is_cal[2000];
+@rec[2000];
+@src[2000];
+@time_rec[2000];
+@src_delay[2000];
+
+@count[40];
+@avg_delay[40];
+@com_time[40];
+
+@duty_cyle[50];
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 40; $j++) {
+		@rec[$i*40+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 40) {
+        	@rec[$i*40+$seq_no] = 1;
+        	@src[$i*40+$seq_no] = @log[2];
+        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 40) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
+        $radio_on_time = @log[3]*65535 + @log[4];
+        $time_now = @log[1]*65535 + @log[2];
+        @duty_cycle[$i] = $radio_on_time / $time_now;
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 40; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*40+$i] == 1) {
+			if (@is_cal[$j*40+$i] == 0) {
+				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
+					@delay[$j*40+$i] = @delay[@src[$j*40+$i]*40+$i] + @src_delay[$j*40+$i] - @time_rec[@src[$j*40+$i]*40+$i];
[…]

### 2020-05-17 code/chase/script/contiki log/contiki2/delay_analysis_contiki.pl

@@ -1,0 +1,107 @@
+@delay[1000];
+@is_cal[1000];
+@rec[1000];
+@src[1000];
+@hop[1000];
+@time_rec[1000];
+@src_delay[1000];
+
+@count[20];
+@avg_delay[20];
+@com_time[20];
+
+for ($i = 0; $i < 20; $i++) {
+	@delay[20+$i] = 0;
+	@time_rec[20+$i] = 0;
+	@is_cal[20+$i] = 1;
+	@rec[20+$i] = 1;
+	@hop[20+$i] = 0;
+}
+
+for ($i = 1; $i < 50; $i++) {
+	for ($j = 0; $j < 20; $j++) {
+		@rec[$i*20+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+
+      if (@log[0] eq "delay:") {
+        $seq_no = @log[1];
+        if ($seq_no < 20) {
+        	@rec[$i*20+$seq_no] = 1;
+        	@src[$i*20+$seq_no] = @log[4];
+        	@time_rec[$i*20+$seq_no] = @log[6];
+        	@src_delay[$i*20+$seq_no] = @log[7];
+        }
+      } elsif (@log[0] eq "flood:") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 20) {
+      		@rec[$i*20+$seq_no] = 1;
+      		@time_rec[$i*20+$seq_no] = @log[2];
+      	}
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 20; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*20+$i] == 1) {
+			if (@is_cal[$j*20+$i] == 0) {
+				if (@is_cal[@src[$j*20+$i]*20+$i] == 1) {
+					@delay[$j*20+$i] = @delay[@src[$j*20+$i]*20+$i] + @src_delay[$j*20+$i] - @time_rec[@src[$j*20+$i]*20+$i];
+					@hop[$j*20+$i] = @hop[@src[$j*20+$i]*20+$i] + 1;
+					#if ($hops == 1) {
[…]

### 2020-05-17 code/chase/script/deludge log/deludge2/delay_analysis.pl

@@ -1,0 +1,80 @@
+@delay[500];
+@is_cal[500];
+@rec[500];
+@src[500];
+@time_rec[500];
+@src_delay[500];
+
+@count[10];
+@avg_delay[10];
+
+for ($i = 0; $i < 10; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 10; $j++) {
+		@rec[$i*10+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 10) {
+        	@rec[$i*10+$seq_no] = 1;
+        	@src[$i*10+$seq_no] = @log[2];
+        	@time_rec[$i*10+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*10+$seq_no] = @log[5] * 65535 + @log[6];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 10) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 10; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*10+$i] == 1) {
+			if (@is_cal[$j*10+$i] == 0) {
+				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
+					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
+					#if ($hops == 1) {
+					#	printf "hops $hops nodeid $j srcid @src[$j*10+$i] src_delay @src_delay[$j*10+$i] delay @delay[$j*10+$i]\n";
+					#}
+					@is_cal[$j*10+$i] = 1;
+				} 
+			}
+		} 
+	}
+}
+$hops++;
+}
+
+
[…]

### 2020-05-17 code/chase/script/deludge log/deludge6/delay_analysis.pl

@@ -1,0 +1,98 @@
+@delay[2000];
+@is_cal[2000];
+@rec[2000];
+@src[2000];
+@time_rec[2000];
+@src_delay[2000];
+@hop[2000];
+
+@count[40];
+@avg_delay[40];
+@com_time[40];
+
+@duty_cyle[50];
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+	@hop[$i] = 0;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 40; $j++) {
+		@rec[$i*40+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 40) {
+        	@rec[$i*40+$seq_no] = 1;
+        	@src[$i*40+$seq_no] = @log[2];
+        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 40) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
+        $radio_on_time = @log[3]*65535 + @log[4];
+        $time_now = @log[1]*65535 + @log[2];
+        @duty_cycle[$i] = $radio_on_time / $time_now;
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 40; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*40+$i] == 1) {
+			if (@is_cal[$j*40+$i] == 0) {
+				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
[…]

### 2020-05-17 code/chase/script/log 3-27 10_27/delay_analysis_contiki.pl

@@ -1,0 +1,86 @@
+@delay[500];
+@is_cal[500];
+@rec[500];
+@src[500];
+@hop[500];
+@time_rec[500];
+@src_delay[500];
+
+@count[10];
+@avg_delay[10];
+
+for ($i = 0; $i < 10; $i++) {
+	@delay[10+$i] = 0;
+	@time_rec[10+$i] = 0;
+	@is_cal[10+$i] = 1;
+	@rec[10+$i] = 1;
+	@hop[10+$i] = 0;
+}
+
+for ($i = 1; $i < 50; $i++) {
+	for ($j = 0; $j < 10; $j++) {
+		@rec[$i*10+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+
+      if (@log[0] eq "delay:") {
+        $seq_no = @log[1];
+        if ($seq_no < 10) {
+        	@rec[$i*10+$seq_no] = 1;
+        	@src[$i*10+$seq_no] = @log[4];
+        	@time_rec[$i*10+$seq_no] = @log[6];
+        	@src_delay[$i*10+$seq_no] = @log[7];
+        }
+      } elsif (@log[0] eq "flood:") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 10) {
+      		@rec[$i*10+$seq_no] = 1;
+      		@time_rec[$i*10+$seq_no] = @log[2];
+      	}
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 10; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*10+$i] == 1) {
+			if (@is_cal[$j*10+$i] == 0) {
+				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
+					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
+					@hop[$j*10+$i] = @hop[@src[$j*10+$i]*10+$i] + 1;
+					#if ($hops == 1) {
[…]

### 2020-05-17 code/chase/script/log 3-28 8_25/delay_analysis_contiki.pl

@@ -1,0 +1,86 @@
+@delay[1000];
+@is_cal[1000];
+@rec[1000];
+@src[1000];
+@hop[1000];
+@time_rec[1000];
+@src_delay[1000];
+
+@count[20];
+@avg_delay[20];
+
+for ($i = 0; $i < 20; $i++) {
+	@delay[20+$i] = 0;
+	@time_rec[20+$i] = 0;
+	@is_cal[20+$i] = 1;
+	@rec[20+$i] = 1;
+	@hop[20+$i] = 0;
+}
+
+for ($i = 1; $i < 50; $i++) {
+	for ($j = 0; $j < 20; $j++) {
+		@rec[$i*20+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+
+      if (@log[0] eq "delay:") {
+        $seq_no = @log[1];
+        if ($seq_no < 20) {
+        	@rec[$i*20+$seq_no] = 1;
+        	@src[$i*20+$seq_no] = @log[4];
+        	@time_rec[$i*20+$seq_no] = @log[6];
+        	@src_delay[$i*20+$seq_no] = @log[7];
+        }
+      } elsif (@log[0] eq "flood:") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 20) {
+      		@rec[$i*20+$seq_no] = 1;
+      		@time_rec[$i*20+$seq_no] = @log[2];
+      	}
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 20; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*20+$i] == 1) {
+			if (@is_cal[$j*20+$i] == 0) {
+				if (@is_cal[@src[$j*20+$i]*20+$i] == 1) {
+					@delay[$j*20+$i] = @delay[@src[$j*20+$i]*20+$i] + @src_delay[$j*20+$i] - @time_rec[@src[$j*20+$i]*20+$i];
+					@hop[$j*20+$i] = @hop[@src[$j*20+$i]*20+$i] + 1;
+					#if ($hops == 1) {
[…]

### 2020-05-17 code/chase/script/multi-protocol.pl

@@ -1,0 +1,65 @@
+{
+	$gnufile = "multi-protocol.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	print gnuout "set boxwidth 0.8 absolute\n";
+    print gnuout "set xrange [0:26] noreverse nowriteback\n";
+    print gnuout "set xtics (\"Chase\" 1, \"LPL\" 7, \"AMAC\" 13, \"Flooding\" 19, \"Contiki\" 25)\n";
+	print gnuout "set output 'mp_ct.eps'\n";
+	print gnuout "set ylabel 'Completion Time (ms)'\n";
+	#print gnuout "set xrange [20:130]\n";
+	#print gnuout "set xlabel 'Packet Length (Bytes)'\n";
+	#print gnuout "set ylabel 'Completion Time (ms)'\n";
+	#print gnuout "set ylabel 'PRR'\n";
+	#print gnuout "set yrange [0.9:1]\n";
+	#print gnuout "set ytics 0.9,0.02,1\n";
+	print gnuout "set yrange [0:21000]\n";
+	print gnuout "set ytics 0,3000,21000\n";
+	#print gnuout "set xtics 20,10,130\n";
+    #print gnuout "set key off\n";
+	print gnuout "set size ratio 0.66\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "set key top left\n";
+	print gnuout "set key samplen 3 spacing 2 font ',22'\n";
+	#print gnuout "plot 'pl_ct.txt' u 1:2:3:4 with yerrorlines pt 4 ps 3 lw 6 notitle";
+	#print gnuout "plot 'prr_ippi.txt' u 1:2 with linespoints pt 4 ps 2 lw 6 title '1344{/Symbol=22 \\155}s', '' u 1:3 with linespoints pt 6 ps 2 lw 6 title '2624{/Symbol=22 \\155}s', '' u 1:4 with linespoints pt 8 ps 2 lw 6 title '3904{/Symbol=22 \\155}s'";
+	#print gnuout "'x_distribution.txt' u 1:3 title 'Uniform' with linespoints pt 1 ps 1 lw 2,";
+	#print gnuout "'x_distribution.txt' u 1:4 title 'Gaussian' with linespoints pt 10 ps 1 lw 2";
[…]

### 2020-05-17 code/chase/script/packet_length.pl

@@ -1,0 +1,55 @@
+{
+	$gnufile = "packet_length.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	print gnuout "set output 'pl_ct.eps'\n";
+	print gnuout "set xrange [20:130]\n";
+	print gnuout "set xlabel 'Packet Length (Bytes)'\n";
+	print gnuout "set ylabel 'Completion Time (ms)'\n";
+	#print gnuout "set ylabel 'PRR'\n";
+	#print gnuout "set yrange [0.9:1]\n";
+	#print gnuout "set ytics 0.9,0.02,1\n";
+	#print gnuout "set yrange [0:480]\n";
+	#print gnuout "set ytics 0,60,480\n";
+	print gnuout "set xtics 20,10,130\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.66\n";
+	#print gnuout "set key bottom right\n";
+    #print gnuout "set key top right\n";
+	#print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
+	print gnuout "plot 'pl_ct.txt' u 1:2:3:4 with yerrorlines pt 4 ps 3 lw 6 notitle";
+	#print gnuout "plot 'prr_ippi.txt' u 1:2 with linespoints pt 4 ps 2 lw 6 title '1344{/Symbol=22 \\155}s', '' u 1:3 with linespoints pt 6 ps 2 lw 6 title '2624{/Symbol=22 \\155}s', '' u 1:4 with linespoints pt 8 ps 2 lw 6 title '3904{/Symbol=22 \\155}s'";
+	#print gnuout "'x_distribution.txt' u 1:3 title 'Uniform' with linespoints pt 1 ps 1 lw 2,";
+	#print gnuout "'x_distribution.txt' u 1:4 title 'Gaussian' with linespoints pt 10 ps 1 lw 2";
+	close gnuout;
+	
+	system "gnuplot packet_length.plt";
+}
+
+{
+	$gnufile = "packet_length.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	print gnuout "set output 'pl_eg.eps'\n";
+	print gnuout "set xrange [20:130]\n";
[…]

### 2020-05-17 code/chase/script/trickle-amac log/trickle-amac3/delay_analysis.pl

@@ -1,0 +1,95 @@
+@delay[2000];
+@is_cal[2000];
+@rec[2000];
+@src[2000];
+@time_rec[2000];
+@src_delay[2000];
+
+@count[40];
+@avg_delay[40];
+@com_time[40];
+
+@duty_cyle[50];
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 40; $j++) {
+		@rec[$i*40+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 40) {
+        	@rec[$i*40+$seq_no] = 1;
+        	@src[$i*40+$seq_no] = @log[2];
+        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no+1 < 40) {
+      		@time_rec[$seq_no+1] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
+        $radio_on_time = @log[3]*65535 + @log[4];
+        $time_now = @log[1]*65535 + @log[2];
+        @duty_cycle[$i] = $radio_on_time / $time_now;
+      }
+    }
+    close fin;
+}
+
+$hops = 1;
+
+while ($hops < 10) {
+for ($i = 0; $i < 40; $i++) {
+	for ($j = 1; $j < 50; $j++) {
+		if (@rec[$j*40+$i] == 1) {
+			if (@is_cal[$j*40+$i] == 0) {
+				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
+					@delay[$j*40+$i] = @delay[@src[$j*40+$i]*40+$i] + @src_delay[$j*40+$i] - @time_rec[@src[$j*40+$i]*40+$i];
+					if ($hops == 1) {
[…]

### 2020-05-17 code/coflood/apps/COFloodTest/ChaseDelayMsg.java

@@ -1,0 +1,1016 @@
+/**
+ * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
+ * This class implements a Java interface to the 'ChaseDelayMsg'
+ * message type.
+ */
+
+public class ChaseDelayMsg extends net.tinyos.message.Message {
+
+    /** The default size of this message type in bytes. */
+    public static final int DEFAULT_MESSAGE_SIZE = 25;
+
+    /** The Active Message type associated with this message. */
+    public static final int AM_TYPE = 44;
+
+    /** Create a new ChaseDelayMsg of size 25. */
+    public ChaseDelayMsg() {
+        super(DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /** Create a new ChaseDelayMsg of the given data_length. */
+    public ChaseDelayMsg(int data_length) {
+        super(data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg with the given data_length
+     * and base offset.
+     */
+    public ChaseDelayMsg(int data_length, int base_offset) {
+        super(data_length, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store.
+     */
+    public ChaseDelayMsg(byte[] data) {
+        super(data);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store, with the given base offset.
+     */
+    public ChaseDelayMsg(byte[] data, int base_offset) {
+        super(data, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store, with the given base offset and data length.
+     */
+    public ChaseDelayMsg(byte[] data, int base_offset, int data_length) {
+        super(data, base_offset, data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg embedded in the given message
+     * at the given base offset.
+     */
+    public ChaseDelayMsg(net.tinyos.message.Message msg, int base_offset) {
+        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg embedded in the given message
[…]

### 2020-05-17 code/coflood/apps/COFloodTest/ChaseSerial.h

@@ -1,0 +1,41 @@
+#ifndef CHASE_SERIAL_H_
+#define CHASE_SERIAL_H_
+
+typedef nx_struct chase_flood_msg {
+  nx_uint16_t seq_no;
+  nx_uint16_t time_flood_h;
+  nx_uint16_t time_flood_l;
+} chase_flood_msg_t;
+
+typedef nx_struct chase_delay_msg {
+  nx_uint16_t nodeid;
+  nx_uint16_t seq_no;
+  nx_uint16_t src_id;
+  nx_uint16_t rec_time_h;
+  nx_uint16_t rec_time_l;
+  nx_uint16_t hop_delay_h;
+  nx_uint16_t hop_delay_l;
+  nx_uint16_t parent_ETD;
+  nx_uint16_t local_ETD;
+  nx_uint16_t delta_ETD;
+  nx_uint8_t long_link_sender;
+  nx_uint16_t MPD;
+  nx_uint8_t shortcut_sender;
+  nx_uint8_t tree_sender;
+} chase_delay_msg_t;
+
+typedef nx_struct chase_energy_msg {
+  nx_uint16_t nodeid;
+  nx_uint16_t clock_time_h;
+  nx_uint16_t clock_time_l;
+  nx_uint16_t dc_time_h;
+  nx_uint16_t dc_time_l;
+} chase_energy_msg_t;
+
+enum {
+  AM_CHASE_FLOOD_MSG = 22,
+  AM_CHASE_DELAY_MSG = 44,
+  AM_CHASE_ENERGY_MSG = 77,
+};
+
+#endif

### 2020-05-17 code/coflood/apps/COFloodTest/TreeBeaconMsg.java

@@ -1,0 +1,554 @@
+/**
+ * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
+ * This class implements a Java interface to the 'TreeBeaconMsg'
+ * message type.
+ */
+
+public class TreeBeaconMsg extends net.tinyos.message.Message {
+
+    /** The default size of this message type in bytes. */
+    public static final int DEFAULT_MESSAGE_SIZE = 14;
+
+    /** The Active Message type associated with this message. */
+    public static final int AM_TYPE = 68;
+
+    /** Create a new TreeBeaconMsg of size 14. */
+    public TreeBeaconMsg() {
+        super(DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /** Create a new TreeBeaconMsg of the given data_length. */
+    public TreeBeaconMsg(int data_length) {
+        super(data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new TreeBeaconMsg with the given data_length
+     * and base offset.
+     */
+    public TreeBeaconMsg(int data_length, int base_offset) {
+        super(data_length, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new TreeBeaconMsg using the given byte array
+     * as backing store.
+     */
+    public TreeBeaconMsg(byte[] data) {
+        super(data);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new TreeBeaconMsg using the given byte array
+     * as backing store, with the given base offset.
+     */
+    public TreeBeaconMsg(byte[] data, int base_offset) {
+        super(data, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new TreeBeaconMsg using the given byte array
+     * as backing store, with the given base offset and data length.
+     */
+    public TreeBeaconMsg(byte[] data, int base_offset, int data_length) {
+        super(data, base_offset, data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new TreeBeaconMsg embedded in the given message
+     * at the given base offset.
+     */
+    public TreeBeaconMsg(net.tinyos.message.Message msg, int base_offset) {
+        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
[…]

### 2020-05-17 code/coflood/apps/RadioCountToLeds/RadioCountToLeds.h

@@ -1,0 +1,57 @@
+/*
+ * Copyright (c) 2004-2005 The Regents of the University  of California.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ * - Redistributions of source code must retain the above copyright
+ *   notice, this list of conditions and the following disclaimer.
+ * - Redistributions in binary form must reproduce the above copyright
+ *   notice, this list of conditions and the following disclaimer in the
+ *   documentation and/or other materials provided with the
+ *   distribution.
+ * - Neither the name of the University of California nor the names of
+ *   its contributors may be used to endorse or promote products derived
+ *   from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
+ * FOR A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL
+ * THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT,
+ * INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+ * (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
+ * SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+ * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT,
+ * STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
+ * ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED
+ * OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ * Copyright (c) 2002-2003 Intel Corporation
+ * All rights reserved.
+ *
+ * This file is distributed under the terms in the attached INTEL-LICENSE
[…]

### 2020-05-17 code/coflood/apps/SenderNumber/ChaseDelayMsg.java

@@ -1,0 +1,554 @@
+/**
+ * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
+ * This class implements a Java interface to the 'ChaseDelayMsg'
+ * message type.
+ */
+
+public class ChaseDelayMsg extends net.tinyos.message.Message {
+
+    /** The default size of this message type in bytes. */
+    public static final int DEFAULT_MESSAGE_SIZE = 14;
+
+    /** The Active Message type associated with this message. */
+    public static final int AM_TYPE = 44;
+
+    /** Create a new ChaseDelayMsg of size 14. */
+    public ChaseDelayMsg() {
+        super(DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /** Create a new ChaseDelayMsg of the given data_length. */
+    public ChaseDelayMsg(int data_length) {
+        super(data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg with the given data_length
+     * and base offset.
+     */
+    public ChaseDelayMsg(int data_length, int base_offset) {
+        super(data_length, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store.
+     */
+    public ChaseDelayMsg(byte[] data) {
+        super(data);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store, with the given base offset.
+     */
+    public ChaseDelayMsg(byte[] data, int base_offset) {
+        super(data, base_offset);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg using the given byte array
+     * as backing store, with the given base offset and data length.
+     */
+    public ChaseDelayMsg(byte[] data, int base_offset, int data_length) {
+        super(data, base_offset, data_length);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg embedded in the given message
+     * at the given base offset.
+     */
+    public ChaseDelayMsg(net.tinyos.message.Message msg, int base_offset) {
+        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
+        amTypeSet(AM_TYPE);
+    }
+
+    /**
+     * Create a new ChaseDelayMsg embedded in the given message
+     * at the given base offset and length.
[…]

### 2020-05-17 code/coflood/include/Chase.h

@@ -1,0 +1,68 @@
+#ifndef CHASE_H_
+#define CHASE_H_
+
+#include "CC2420.h"
+
+#define RSSI_SAMPLES_NUM 128
+
+#define CC2420_FIFOP_DISABLE()\
+                              do {\
+                                P1IFG &= ~(1 << 0); \
+                                P1IE &= ~(1 << 0);  \
+                              } while(0)
+
+#define CC2420_FIFOP_ENABLE() \
+                              do { \
+                                P1IFG &= ~(1 << 0); \
+                                P1IE |= (1 << 0);   \
+                              } while(0)
+
+#define ABS_VALUE(a, b) ( (a > b) ? a-b : b-a )
+
+typedef enum {
+  DUTY_CYCLE_IDL,
+  DUTY_CYCLE_DET,
+  DUTY_CYCLE_LIS,
+  DUTY_CYCLE_REC,
+  DUTY_CYCLE_SND,
+  DUTY_CYCLE_OFF,
+} chase_radio_state_t;
+
+typedef nx_struct {
+  nx_uint16_t src_id;
+  nx_uint16_t seq_no;
+  nx_uint16_t fwd_id;
+  nx_uint16_t local_delay;
+  nx_uint16_t start_time_h;
+  nx_uint16_t start_time_l;
+  nx_uint16_t fwd_time_h;
+  nx_uint16_t fwd_time_l;
+} chase_header_t;
+
+typedef struct {
+  uint16_t src_id;
+  uint16_t seq_no;
+  uint16_t last_hop_id;
+  uint16_t per_hop_delay_h;
+  uint16_t per_hop_delay_l;
+  uint16_t parent_ETD;
+  uint16_t local_ETD;
+  uint16_t delta_ETD;
+  uint8_t long_link_sender;
+  uint16_t MPD;
+  uint8_t shortcut_sender;
+  uint8_t tree_sender;
+} chase_delay_t;
+
+typedef nx_struct chase_tail_msg {
+  nx_uint16_t nodeid;
+  nx_uint16_t seq_no;
+  nx_uint16_t tail_time_h;
+  nx_uint16_t tail_time_l;
+} chase_tail_msg_t;
+
+enum {
+  AM_CHASE_TAIL_MSG = 99,
+};
+
+#endif

### 2020-05-17 code/coflood/script/Indriya/auto_tree.pl

@@ -1,0 +1,113 @@
+@node[150];
+@ebw[150];
+@path_ebw[150];
+@elder_id[150];
+@delay[150];
+@children_num[150];
+@is_sender[150];
+
+$total_node = 0;
+$total_sender = 0;
+
+for ($i = 0; $i < 150; $i++) {
+    @node[$i] = 0;
+}
+
+$s_counter = 0;
+
+$sender_file = "sender.dat";
+open fin, "<$sender_file" or "could not open file!\n";
+while (<fin>) {
+    chomp;
+    @log = split;
+
+    if (@log[0] eq "id") { next; }
+
+    $id = @log[0];
+    @node[$id] = 1;
+    @ebw[$id] = @log[1];
+    @path_ebw[$id] = @log[2];
+    @elder_id[$id] = @log[3];
+    @delay[$id] = @log[4];
+    @children_num[$id] = @log[5];
+    @is_sender[$id] = @log[6];
+
+    $total_node++;
+    if (@log[6] == 1) {
+        $total_sender++;
+    }
+
+    if ( ($id % 6) == 0 ) {
+        $s_counter++;
+        printf "$id ";
+    }
+}
+
+printf "$s_counter\n";
+
+$root = 3;
+@hop[150];
+
+for ($i = 0; $i < 150; $i++) {
+    @hop[$i] = 0;
+}
+
+@hop[$root] = 1;
+$max_hop = 0;
+$change = 0;
+
+while ($change == 0) {
+    $change = 1;
+    for ($i = 0; $i < 150; $i++) {
+        if ( (@hop[$i] == 0) && (@hop[@elder_id[$i]] != 0) ) {
+            @hop[$i] = @hop[@elder_id[$i]] + 1;
+            $change = 0;
+        }
+    }
+}
+
+for ($i = 0; $i < 150; $i++) {
+    if (@hop[$i] > $max_hop) {
+        $max_hop = @hop[$i];
+    }
+}
+
+for ($i = 1; $i <= $max_hop; $i++) {
+    printf "Hop $i:\n";
+    for ($j = 0; $j < 150; $j++) {
+        if (@hop[$j] == $i) {
+            printf "    $j(EBW @ebw[$j] | Path_EBW @path_ebw[$j] | Elder_ID @elder_id[$j] | Delay @delay[$j] | Children# @children_num[$j] | Is_Sender @is_sender[$j])\n";
+        }
+    }
[…]

### 2020-05-17 code/coflood/script/Indriya/diff_senders/30_22_31/delay_analysis_contiki.pl

@@ -1,0 +1,235 @@
+@delay[6000];
+@is_cal[6000];
+@rec[6000];
+@src[6000];
+@hop[6000];
+@time_rec[6000];
+@src_delay[6000];
+@tail[6000];
+
+@count[40];
+@avg_delay[40];
+@comp_time[40];
+
+@duty_cycle[150];
+
+for ($i = 0; $i < 150; $i++) {
+	@duty_cycle[$i] = 0;
+}
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[3*40+$i] = 0;
+	@time_rec[3*40+$i] = 0;
+	@is_cal[3*40+$i] = 1;
+	@rec[3*40+$i] = 1;
+	@hop[3*40+$i] = 0;
+}
+
+$log_file = "flood.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "seq_no") { next; }
+
+	$seq_no = @log[0];
+	if ($seq_no < 40) {
+		@rec[3*40+$seq_no] = 1;
+		$time_flood = @log[1] * 65536 + @log[2];
+		@time_rec[3*40+$seq_no] = $time_flood;
+	}
+}
+close fin;
+
+$log_file = "delay.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+	$seq_no = @log[1];
+	if ($seq_no < 40) {
+		@rec[$nodeid*40+$seq_no] = 1;
+        @src[$nodeid*40+$seq_no] = @log[2];
+        $tmp_time = @log[3] * 65536 + @log[4];
+        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
+        $tmp_time = @log[5] * 65536 + @log[6];
+        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
+	}
+}
+close fin;
+
+$log_file = "energy.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+    $total_time = @log[1] * 65536 + @log[2];
+    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-05-17 code/coflood/script/Indriya/diff_senders/40sender_chase_long_all/delay_analysis_contiki.pl

@@ -1,0 +1,235 @@
+@delay[6000];
+@is_cal[6000];
+@rec[6000];
+@src[6000];
+@hop[6000];
+@time_rec[6000];
+@src_delay[6000];
+@tail[6000];
+
+@count[40];
+@avg_delay[40];
+@comp_time[40];
+
+@duty_cycle[150];
+
+for ($i = 0; $i < 150; $i++) {
+	@duty_cycle[$i] = 0;
+}
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[3*40+$i] = 0;
+	@time_rec[3*40+$i] = 0;
+	@is_cal[3*40+$i] = 1;
+	@rec[3*40+$i] = 1;
+	@hop[3*40+$i] = 0;
+}
+
+$log_file = "flood.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "seq_no") { next; }
+
+	$seq_no = @log[0];
+	if ($seq_no < 40) {
+		@rec[3*40+$seq_no] = 1;
+		$time_flood = @log[1] * 65536 + @log[2];
+		@time_rec[3*40+$seq_no] = $time_flood;
+	}
+}
+close fin;
+
+$log_file = "delay.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+	$seq_no = @log[1];
+	if ($seq_no < 40) {
+		@rec[$nodeid*40+$seq_no] = 1;
+        @src[$nodeid*40+$seq_no] = @log[2];
+        $tmp_time = @log[3] * 65536 + @log[4];
+        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
+        $tmp_time = @log[5] * 65536 + @log[6];
+        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
+	}
+}
+close fin;
+
+$log_file = "energy.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+    $total_time = @log[1] * 65536 + @log[2];
+    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-05-17 code/coflood/script/Lab testbed/10senders_chase2/delay_analysis.pl

@@ -1,0 +1,228 @@
+@delay[1650];
+@is_cal[1650];
+@rec[1650];
+@src[1650];
+@time_rec[1650];
+@src_delay[1650];
+@tail_time[1650];
+@hop[1650];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[51];
+@tmp_tail_time[51];
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      #if (@log[0] eq "Thread[Thread-1,5,main]") {
+      #	@log[0] = @log[1];
+      #	@log[1] = @log[2];
+      #	@log[2] = @log[3];
+      #}
+      if (@log[0] eq "Thread[Thread-1,5,main]radio") {
+        @log[0] = "radio";
+      }
+
+      if (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 30) {
+        	@rec[$i*30+$seq_no] = 1;
+        	@src[$i*30+$seq_no] = @log[2];
+        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
+
+            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 30) {
[…]

### 2020-05-17 code/coflood/script/Lab testbed/delay_plot.pl

@@ -1,0 +1,26 @@
+{
+	$gnufile = "delay.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+	print gnuout "set output 'delay.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
+	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
+	print gnuout "set ylabel 'Completion Time (ms)'\n";
+	print gnuout "set yrange [1000:2000]\n";
+	print gnuout "set ytics 1000,200,2000\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
+	print gnuout "plot 'data.txt' using 1:3 with linespoints t 'Lab Testbed' lt 7 lw 4 ps 2 pt 4\n";
+	close gnuout;
+
+	system "gnuplot delay.plt";
+}

### 2020-05-17 code/coflood/script/Lab testbed/energy_plot.pl

@@ -1,0 +1,26 @@
+{
+	$gnufile = "energy.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+	print gnuout "set output 'energy.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
+	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
+	print gnuout "set ylabel 'Radio Duty Cycle (%)'\n";
+	print gnuout "set yrange [0:14]\n";
+	print gnuout "set ytics 0,2,14\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
+	print gnuout "plot 'data.txt' using 1:2 with linespoints t 'Lab Testbed' lt 7 lw 4 ps 2 pt 4\n";
+	close gnuout;
+
+	system "gnuplot energy.plt";
+}

### 2020-05-17 code/coflood/script/control-topo/delay_plot.pl

@@ -1,0 +1,24 @@
+{
+	$gnufile = "delay.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	print gnuout "set style data histograms\n";
+    print gnuout "set style histogram rowstacked\n";
+    print gnuout "set boxwidth 0.6 relative\n";
+    print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+	print gnuout "set output 'delay.eps'\n";
+	#print gnuout "set xrange [0:100000]\n";
+	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
+	print gnuout "set ylabel 'Receiving Delay of R (ms)'\n";
+	#print gnuout "set yrange [0:1]\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "set key top center\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
+	print gnuout "plot 'delay.txt' using 4 t 'Sleep' lc rgb 'grey' lw 4, '' using 3:xticlabels(1) t 'Tail' lc rgb 'black' lw 4\n";
+	close gnuout;
+
+	system "gnuplot delay.plt";
+}

### 2020-05-17 code/coflood/script/control-topo/local-testbed-control-topo/20senders6/delay_analysis.pl

@@ -1,0 +1,220 @@
+@delay[1650];
+@is_cal[1650];
+@rec[1650];
+@src[1650];
+@time_rec[1650];
+@src_delay[1650];
+@tail_time[1650];
+@hop[1650];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[51];
+@tmp_tail_time[51];
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 51; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      #if (@log[0] eq "Thread[Thread-1,5,main]") {
+      #	@log[0] = @log[1];
+      #	@log[1] = @log[2];
+      #	@log[2] = @log[3];
+      #}
+      if (@log[0] eq "Thread[Thread-1,5,main]radio") {
+        @log[0] = "radio";
+      }
+
+      if (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 30) {
+        	@rec[$i*30+$seq_no] = 1;
+        	@src[$i*30+$seq_no] = @log[2];
+        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
+
+            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 30) {
[…]

### 2020-05-17 code/coflood/script/control-topo/local-testbed-control-topo/2senders/delay_analysis.pl

@@ -1,0 +1,210 @@
+@delay[1650];
+@is_cal[1650];
+@rec[1650];
+@src[1650];
+@time_rec[1650];
+@src_delay[1650];
+@tail_time[1650];
+@hop[1650];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[51];
+@tmp_tail_time[51];
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 51; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "Thread[Thread-1,5,main]") {
+      	@log[0] = @log[1];
+      	@log[1] = @log[2];
+      	@log[2] = @log[3];
+      }
+
+      if (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 30) {
+        	@rec[$i*30+$seq_no] = 1;
+        	@src[$i*30+$seq_no] = @log[2];
+        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
+
+            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 30) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
[…]

### 2020-05-17 code/coflood/script/control-topo/local-testbed-control-topo/8senders/delay_analysis.pl

@@ -1,0 +1,201 @@
+@delay[1650];
+@is_cal[1650];
+@rec[1650];
+@src[1650];
+@time_rec[1650];
+@src_delay[1650];
+@tail_time[1650];
+@hop[1650];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[51];
+@tmp_tail_time[51];
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$i] = 0;
+	@time_rec[$i] = 0;
+	@is_cal[$i] = 1;
+	@rec[$i] = 1;
+}
+
+for ($i = 0; $i < 51; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      if (@log[0] eq "Thread[Thread-1,5,main]") {
+      	@log[0] = @log[1];
+      	@log[1] = @log[2];
+      	@log[2] = @log[3];
+      }
+
+      if (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
+        if ($seq_no < 30) {
+        	@rec[$i*30+$seq_no] = 1;
+        	@src[$i*30+$seq_no] = @log[2];
+        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
+        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
+
+            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
+        }
+      } elsif (@log[0] eq "flood") {
+      	$seq_no = @log[1];
+      	if ($seq_no < 30) {
+      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
+      	}
+      } elsif (@log[0] eq "energy") {
[…]

### 2020-05-17 code/coflood/script/control-topo/local-testbed-control-topo/topo1/topo.pl

@@ -1,0 +1,133 @@
+@node[50];
+@neighbor[2500];
+@link[2500];
+@rssi[2500];
+
+for ($i = 0; $i < 50; $i++) {
+    @node[$i] = 0;
+}
+
+for ($i = 0; $i < 2500; $i++) {
+    @neighbor[$i] = 0;
+    @link[$i] = 0;
+    @rssi[$i] = 0;
+}
+
+for ($i = 0; $i < 50; $i++) {
+$topo_file = "$i.log";
+open fin, "<$topo_file" or "could not open file!\n";
+while (<fin>) {
+    chomp;
+    @log = split;
+
+    #if (@log[0] eq "id") { next; }
+
+    $id = @log[3];
+    $src = @log[1];
+    $rssi = @log[4];
+
+    #printf "$id $src\n";
+
+    if ($rssi > 127) {
+        $rssi = $rssi - 256 - 45;
+    } else {
+        $rssi = $rssi - 45;
+    }
+
+    $index = $src * 50 + $id;
+    @neighbor[$index] = 1;
+    @link[$index] = @link[$index] + 1;
+    @rssi[$index] = @rssi[$index] + $rssi;
+}
+}
+
+for ($i = 0; $i < 50; $i++) {
+    for ($j = 0; $j < 50; $j++) {
+        $index = $i * 50 + $j;
+        if (@neighbor[$index] == 1) {
+            $node[$i]++;
+        }
+    }
+}
+
+$total_node = 0;
+$max_neighbor = 0;
+$min_neighbor = 50;
+$avg_neighbor = 0;
+
+for ($i = 0; $i < 50; $i++) {
+    for ($j = 0; $j < 50; $j++) {
+        $index = $i * 50 + $j;
+        if (@neighbor[$index] == 1) {
+            @rssi[$index] = @rssi[$index] / @link[$index];
+            @link[$index] = @link[$index] / 10;
+            if (@link[$index] < 0.8) {
+                @neighbor[$index] = 0;
+                @node[$i]--;
+            } else {
+                printf "link[$i, $j]: quality @link[$index], rssi @rssi[$index]\n";
+            }
+        }
+    }
+    if (@node[$i] > 0) {
+        if (@node[$i] > $max_neighbor) {
+            $max_neighbor = @node[$i];
+        }
+        if (@node[$i] < $min_neighbor) {
+            $min_neighbor = @node[$i];
+        }
+        $avg_neighbor += @node[$i];
+        $total_node++;
[…]

### 2020-05-17 code/coflood/script/control-topo/local-testbed-control-topo/topo2/topo.pl

@@ -1,0 +1,133 @@
+@node[50];
+@neighbor[2500];
+@link[2500];
+@rssi[2500];
+
+for ($i = 0; $i < 50; $i++) {
+    @node[$i] = 0;
+}
+
+for ($i = 0; $i < 2500; $i++) {
+    @neighbor[$i] = 0;
+    @link[$i] = 0;
+    @rssi[$i] = 0;
+}
+
+for ($i = 0; $i < 50; $i++) {
+$topo_file = "$i.log";
+open fin, "<$topo_file" or "could not open file!\n";
+while (<fin>) {
+    chomp;
+    @log = split;
+
+    #if (@log[0] eq "id") { next; }
+
+    $id = @log[3];
+    $src = @log[1];
+    $rssi = @log[4];
+
+    #printf "$id $src\n";
+
+    if ($rssi > 127) {
+        $rssi = $rssi - 256 - 45;
+    } else {
+        $rssi = $rssi - 45;
+    }
+
+    $index = $src * 50 + $id;
+    @neighbor[$index] = 1;
+    @link[$index] = @link[$index] + 1;
+    @rssi[$index] = @rssi[$index] + $rssi;
+}
+}
+
+for ($i = 0; $i < 50; $i++) {
+    for ($j = 0; $j < 50; $j++) {
+        $index = $i * 50 + $j;
+        if (@neighbor[$index] == 1) {
+            $node[$i]++;
+        }
+    }
+}
+
+$total_node = 0;
+$max_neighbor = 0;
+$min_neighbor = 50;
+$avg_neighbor = 0;
+
+for ($i = 0; $i < 50; $i++) {
+    for ($j = 0; $j < 50; $j++) {
+        $index = $i * 50 + $j;
+        if (@neighbor[$index] == 1) {
+            @rssi[$index] = @rssi[$index] / @link[$index];
+            @link[$index] = @link[$index] / 10;
+            if (@link[$index] < 0.6) {
+                @neighbor[$index] = 0;
+                @node[$i]--;
+            } else {
+                printf "link[$i, $j]: quality @link[$index], rssi @rssi[$index]\n";
+            }
+        }
+    }
+    if (@node[$i] > 0) {
+        if (@node[$i] > $max_neighbor) {
+            $max_neighbor = @node[$i];
+        }
+        if (@node[$i] < $min_neighbor) {
+            $min_neighbor = @node[$i];
+        }
+        $avg_neighbor += @node[$i];
+        $total_node++;
[…]

### 2020-05-17 code/coflood/script/delay_plot.pl

@@ -1,0 +1,34 @@
+{
+	$gnufile = "delay.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+    #print gnuout "set tmargin 0\n";
+    #print gnuout "set bmargin 0\n";
+    #print gnuout "set lmargin 3\n";
+    #print gnuout "set rmargin 3\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+    #print gnuout "set multiplot layout 2,1\n";
+    print gnuout "set output 'delay.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+    #print gnuout "unset xtics\n";
+    #print gnuout "unset ytics\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
+	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
+	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
+    print gnuout "set ylabel 'Completion Time (ms)'\n";
+    print gnuout "set yrange [1000:2200]\n";
+    print gnuout "set ytics 1000,200,2200\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+	print gnuout "plot 'lab_data.txt' using 1:3 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'indriya_data.txt' using 1:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
+    #print gnuout "unset multiplot\n";
+	close gnuout;
+
+	system "gnuplot delay.plt";
+}

### 2020-05-17 code/coflood/script/energy_plot.pl

@@ -1,0 +1,26 @@
+{
+	$gnufile = "energy.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+	print gnuout "set output 'energy.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
+	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
+	print gnuout "set ylabel 'Radio Duty Cycle (%)'\n";
+	print gnuout "set yrange [4:14]\n";
+	print gnuout "set ytics 4,2,14\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
+	print gnuout "plot 'lab_data.txt' using 1:2 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'indriya_data.txt' using 1:2 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
+	close gnuout;
+
+	system "gnuplot energy.plt";
+}

### 2020-05-17 impl&eva/Indriya/COFlood/exp1/tree_topo.pl

@@ -1,0 +1,84 @@
+@node[150];
+@neighbor[2100];
+@link[2100];
+@sender[150];
+
+for ($i = 0; $i < 150; $i++) {
+    @node[$i] = 0;
+    @sender[$i] = 0;
+}
+
+for ($i = 0; $i < 2100; $i++) {
+    @neighbor[$i] = 0;
+    @link[$i] = 0;
+}
+
+$total_node = 0;
+
+$tree_file = "tree.dat";
+open fin, "<$tree_file" or "could not open file!\n";
+while (<fin>) {
+    chomp;
+    @log = split;
+
+    if (@log[0] eq "addr") { next; }
+
+    $id = @log[0];
+    @node[$id] = @log[1];
+
+    printf "Node $id has @node[$id] neighbors:\n";
+
+    $total_node++;
+
+    for ($i = 0; $i < @node[$id]; $i++) {
+        @neighbor[$id*14+$i] = @log[2+$i];
+        @link[$id*14+$i] = @log[16+$i];
+        printf "Neighbor @log[2+$i], Link Quality @log[16+$i]\n";
+    }
+}
+
+printf "Total Node: $total_node\n";
+
+$root = 3;
+@hop[150];
+
+for ($i = 0; $i < 150; $i++) {
+    @hop[$i] = 0;
+}
+
+@hop[$root] = 1;
+$max_hop = 0;
+$change = 0;
+
+while ($change == 0) {
+    $change = 1;
+    for ($i = 0; $i < 150; $i++) {
+        if (@hop[$i] != 0) {
+            for ($j = 0; $j < $node[$i]; $j++) {
+                $new_hop = @hop[$i] + 1;
+                if ( (@hop[@neighbor[$i*14+$j]] == 0) || ($new_hop < @hop[@neighbor[$i*14+$j]]) ) {
+                    @hop[@neighbor[$i*14+$j]] = $new_hop;
+                    @sender[@neighbor[$i*14+$j]] = $i;
+                    $change = 0;
+                }
+            }
+        }
+    }
+}
+
+for ($i = 0; $i < 150; $i++) {
+    if (@hop[$i] > $max_hop) {
+        $max_hop = @hop[$i];
+    }
+}
+
+for ($i = 1; $i <= $max_hop; $i++) {
+    printf "Hop $i:";
+    for ($j = 0; $j < 150; $j++) {
+        if (@hop[$j] == $i) {
+            printf " $j(@sender[$j])";
[…]

### 2020-05-17 impl&eva/Indriya/LL-COFlood/1-thresh/exp3-fail/delay_analysis_contiki.pl

@@ -1,0 +1,286 @@
+@delay[6000];
+@is_cal[6000];
+@rec[6000];
+@src[6000];
+@hop[6000];
+@time_rec[6000];
+@src_delay[6000];
+@tail[6000];
+@tree_sender[6000];
+@long_link_sender[6000];
+@shortcut_sender[6000];
+@mpd[6000];
+@parent_etd[6000];
+@local_etd[6000];
+@delta_etd[6000];
+
+@count[40];
+@avg_delay[40];
+@comp_time[40];
+@sender_number[40];
+@tree_sender_number[40];
+@long_link_sender_number[40];
+@shortcut_sender_number[40];
+
+@duty_cycle[150];
+
+for ($i = 0; $i < 150; $i++) {
+	@duty_cycle[$i] = 0;
+}
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[3*40+$i] = 0;
+	@time_rec[3*40+$i] = 0;
+	@is_cal[3*40+$i] = 1;
+	@rec[3*40+$i] = 1;
+	@hop[3*40+$i] = 0;
+}
+
+$log_file = "flood.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "seq_no") { next; }
+
+	$seq_no = @log[0];
+	if ($seq_no < 40) {
+		@rec[3*40+$seq_no] = 1;
+		$time_flood = @log[1] * 65536 + @log[2];
+		@time_rec[3*40+$seq_no] = $time_flood;
+	}
+}
+close fin;
+
+$log_file = "delay.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+	$seq_no = @log[1];
+	if ($seq_no < 40) {
+		@rec[$nodeid*40+$seq_no] = 1;
+        @src[$nodeid*40+$seq_no] = @log[2];
+        $tmp_time = @log[3] * 65536 + @log[4];
+        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
+        $tmp_time = @log[5] * 65536 + @log[6];
+        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
+
+        @parent_etd[$nodeid*40+$seq_no] = @log[7];
+        @local_etd[$nodeid*40+$seq_no] = @log[8];
[…]

### 2020-05-17 impl&eva/Indriya/LL-COFlood/1-thresh/exp7-fail/delay_analysis_contiki.pl

@@ -1,0 +1,285 @@
+@delay[6000];
+@is_cal[6000];
+@rec[6000];
+@src[6000];
+@hop[6000];
+@time_rec[6000];
+@src_delay[6000];
+@tail[6000];
+@tree_sender[6000];
+@long_link_sender[6000];
+@shortcut_sender[6000];
+@mpd[6000];
+@parent_etd[6000];
+@local_etd[6000];
+@delta_etd[6000];
+
+@count[40];
+@avg_delay[40];
+@comp_time[40];
+@sender_number[40];
+@tree_sender_number[40];
+@long_link_sender_number[40];
+@shortcut_sender_number[40];
+
+@duty_cycle[150];
+
+for ($i = 0; $i < 150; $i++) {
+	@duty_cycle[$i] = 0;
+}
+
+for ($i = 0; $i < 40; $i++) {
+	@delay[3*40+$i] = 0;
+	@time_rec[3*40+$i] = 0;
+	@is_cal[3*40+$i] = 1;
+	@rec[3*40+$i] = 1;
+	@hop[3*40+$i] = 0;
+}
+
+$log_file = "flood.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "seq_no") { next; }
+
+	$seq_no = @log[0];
+	if ($seq_no < 40) {
+		@rec[3*40+$seq_no] = 1;
+		$time_flood = @log[1] * 65536 + @log[2];
+		@time_rec[3*40+$seq_no] = $time_flood;
+	}
+}
+close fin;
+
+$log_file = "delay.log";
+open fin, "<$log_file" or "could not open file!\n";
+while (<fin>) {
+	chomp;
+	@log = split;
+
+	if (@log[0] eq "nodeid") { next; }
+
+	$nodeid = @log[0];
+	$seq_no = @log[1];
+	if ($seq_no < 40) {
+		@rec[$nodeid*40+$seq_no] = 1;
+        @src[$nodeid*40+$seq_no] = @log[2];
+        $tmp_time = @log[3] * 65536 + @log[4];
+        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
+        $tmp_time = @log[5] * 65536 + @log[6];
+        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
+
+        @parent_etd[$nodeid*40+$seq_no] = @log[7];
+        @local_etd[$nodeid*40+$seq_no] = @log[8];
[…]

### 2020-05-17 impl&eva/Lab/beacon number/15/coflood3/delay_analysis.pl

@@ -1,0 +1,286 @@
+@delay[1500];
+@is_cal[1500];
+@rec[1500];
+@src[1500];
+@time_rec[1500];
+@src_delay[1500];
+@tail_time[1500];
+@hop[1500];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[50];
+@tmp_tail_time[50];
+
+@ebw[50];
+@path_ebw[50];
+@elder_id[50];
+@delay[50];
+@children_num[50];
+@is_sender[50];
+
+$total_sender = 0;
+$root = 0;
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$root*30+$i] = 0;
+	@time_rec[$root*30+$i] = 0;
+	@is_cal[$root*30+$i] = 1;
+	@rec[$root*30+$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      #if (@log[0] eq "Thread[Thread-1,5,main]") {
+      #	@log[0] = @log[1];
+      #	@log[1] = @log[2];
+      #	@log[2] = @log[3];
+      #}
+      if (@log[0] eq "Thread[Thread-1,5,main]tree") {
+        @log[0] = "tree";
+      }
+
+      if (@log[0] eq "tree") {
+        @ebw[$i] = @log[1];
+        @path_ebw[$i] = @log[2];
+        @elder_id[$i] = @log[3];
+        @delay[$i] = @log[4];
+        @children_number[$i] = @log[5];
+        @is_sender[$i] = @log[6];
+
+        if (@log[6] == 1) {
+          $total_sender++;
+        }
+      } elsif (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
[…]

### 2020-05-17 impl&eva/Lab/ll-coflood/threshold-20_2/delay_analysis.pl

@@ -1,0 +1,289 @@
+@delay[1500];
+@is_cal[1500];
+@rec[1500];
+@src[1500];
+@time_rec[1500];
+@src_delay[1500];
+@tail_time[1500];
+@hop[1500];
+
+@count[30];
+@avg_delay[30];
+@com_time[30];
+@last_id[30];
+@max_tail_time[30];
+@max_tail_id[30];
+@avg_tail_time[30];
+
+@all_tail[1650];
+$tail_count;
+
+@duty_cyle[50];
+@tmp_tail_time[50];
+
+@ebw[50];
+@path_ebw[50];
+@elder_id[50];
+@delay[50];
+@children_num[50];
+@is_sender[50];
+
+$total_sender = 0;
+$root = 0;
+
+for ($i = 0; $i < 30; $i++) {
+	@delay[$root*30+$i] = 0;
+	@time_rec[$root*30+$i] = 0;
+	@is_cal[$root*30+$i] = 1;
+	@rec[$root*30+$i] = 1;
+}
+
+for ($i = 0; $i < 50; $i++) {
+	for ($j = 0; $j < 30; $j++) {
+		@rec[$i*30+$j] = 0;
+	}
+	$log_file = "$i.log";
+	open fin, "<$log_file" or die "could not open file!\n";
+	while (<fin>) {
+      chomp;
+      @log = split;
+      #if (@log[0] eq "Thread[Thread-1,5,main]") {
+      #	@log[0] = @log[1];
+      #	@log[1] = @log[2];
+      #	@log[2] = @log[3];
+      #}
+      if (@log[0] eq "Thread[Thread-1,5,main]tree") {
+        @log[0] = "tree";
+      }
+
+      if (@log[0] eq "tree") {
+        @ebw[$i] = @log[1];
+        @path_ebw[$i] = @log[2];
+        @elder_id[$i] = @log[3];
+        @delay[$i] = @log[4];
+        @children_number[$i] = @log[5];
+        @is_sender[$i] = @log[6];
+
+        if (@log[6] == 1) {
+          $total_sender++;
+        }
+      } elsif (@log[0] eq "radio") {
+      	$time_h = @log[1];
+      	$time_l = @log[2];
+        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
+      } elsif (@log[0] eq "delay") {
+        $seq_no = @log[1];
[…]

### 2020-05-17 impl&eva/beacon-number-result-plot.pl

@@ -1,0 +1,34 @@
+{
+	$gnufile = "beacon-number-result-plot.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+    #print gnuout "set tmargin 0\n";
+    #print gnuout "set bmargin 0\n";
+    #print gnuout "set lmargin 3\n";
+    #print gnuout "set rmargin 3\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+    #print gnuout "set multiplot layout 2,1\n";
+    print gnuout "set output 'beacon_number.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+    #print gnuout "unset xtics\n";
+    #print gnuout "unset ytics\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
+	print gnuout "set xtics ('5' 1, '10' 2, '15' 3, '20' 4, '25' 5)\n";
+	print gnuout "set xlabel 'Number of Beacons'\n";
+    print gnuout "set ylabel 'Average Expected Broadcasts'\n";
+    print gnuout "set yrange [0:30]\n";
+    print gnuout "set ytics 0,5,30\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "plot 'beacon-number-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'beacon-number-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
+    #print gnuout "unset multiplot\n";
+	close gnuout;
+
+	system "gnuplot beacon-number-result-plot.plt";
+}

### 2020-05-17 impl&eva/completion-time-result.pl

@@ -1,0 +1,23 @@
+{
+	$gnufile = "completion-time-result.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 24\n";
+	print gnuout "set output 'completion-time-result.eps'\n";
+	print gnuout "set style data histogram\n";
+	print gnuout "set style histogram cluster gap 2\n";
+	print gnuout "set style fill pattern 2 border\n";
+	print gnuout "set boxwidth 1\n";
+	print gnuout "set xlabel 'Testbed'\n";
+	print gnuout "set ylabel 'Completion Time (ms)'\n";
+	#print gnuout "set size ratio 0.25\n";
+	print gnuout "set yrange [0:2400]\n";
+	#print gnuout "set xrange [0:4]\n";
+	print gnuout "set ytics 0,400,2400\n";
+	#print gnuout "set boxwidth 0.25\n";
+	print gnuout "set key top left\n";
+	#print gnuout "set key bottom right\n";
+	print gnuout "plot 'completion-time-result.txt' using 2:xtic(1) ti col lt -1 lw 4, '' u 3 ti col lt -1 lw 4, '' u 4 ti col lt -1 lw 4, '' u 5 ti col lt -1 lw 4, '' u 6 ti col lt -1 lw 4";
+	close gnuout;
+	
+	system "gnuplot completion-time-result.plt";
+}

### 2020-05-17 impl&eva/duty-cycle-result.pl

@@ -1,0 +1,23 @@
+{
+	$gnufile = "duty-cycle-result.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 24\n";
+	print gnuout "set output 'duty-cycle-result.eps'\n";
+	print gnuout "set style data histogram\n";
+	print gnuout "set style histogram cluster gap 2\n";
+	print gnuout "set style fill pattern 2 border\n";
+	print gnuout "set boxwidth 1\n";
+	print gnuout "set xlabel 'Testbed'\n";
+	print gnuout "set ylabel 'Radio Duty Cycle (%)'\n";
+	#print gnuout "set size ratio 0.25\n";
+	print gnuout "set yrange [0:12]\n";
+	#print gnuout "set xrange [0:4]\n";
+	print gnuout "set ytics 0,3,12\n";
+	#print gnuout "set boxwidth 0.25\n";
+	print gnuout "set key top right\n";
+	#print gnuout "set key bottom right\n";
+	print gnuout "plot 'duty-cycle-result.txt' using 2:xtic(1) ti col lt -1 lw 4, '' u 3 ti col lt -1 lw 4, '' u 4 ti col lt -1 lw 4, '' u 5 ti col lt -1 lw 4, '' u 6 ti col lt -1 lw 4";
+	close gnuout;
+
+	system "gnuplot duty-cycle-result.plt";
+}

### 2020-05-17 impl&eva/link-threshold-result-plot.pl

@@ -1,0 +1,34 @@
+{
+	$gnufile = "link-threshold-result-plot.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+    #print gnuout "set tmargin 0\n";
+    #print gnuout "set bmargin 0\n";
+    #print gnuout "set lmargin 3\n";
+    #print gnuout "set rmargin 3\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+    #print gnuout "set multiplot layout 2,1\n";
+    print gnuout "set output 'link_threshold.eps'\n";
+	print gnuout "set xrange [0:6]\n";
+    #print gnuout "unset xtics\n";
+    #print gnuout "unset ytics\n";
+    print gnuout "set key top left\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
+	print gnuout "set xtics ('0.5' 1, '0.6' 2, '0.7' 3, '0.8' 4, '0.9' 5)\n";
+	print gnuout "set xlabel 'Threshold of Link Quality'\n";
+    print gnuout "set ylabel 'Average Expected Broadcasts'\n";
+    print gnuout "set yrange [0:30]\n";
+    print gnuout "set ytics 0,5,30\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "plot 'link-threshold-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'link-threshold-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
+    #print gnuout "unset multiplot\n";
+	close gnuout;
+
+	system "gnuplot link-threshold-result-plot.plt";
+}

### 2020-05-17 impl&eva/sp-coflood-result-plot.pl

@@ -1,0 +1,34 @@
+{
+	$gnufile = "sp-coflood-result-plot.plt";
+	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
+    #print gnuout "set tmargin 0\n";
+    #print gnuout "set bmargin 0\n";
+    #print gnuout "set lmargin 3\n";
+    #print gnuout "set rmargin 3\n";
+	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
+	#print gnuout "set style data histograms\n";
+    #print gnuout "set style histogram rowstacked\n";
+    #print gnuout "set boxwidth 0.6 relative\n";
+    #print gnuout "set style fill pattern 2 border -1\n";
+    #print gnuout "set style line 2 lt 1 lw 7\n";
+    #print gnuout "set multiplot layout 2,1\n";
+    print gnuout "set output 'sp-coflood.eps'\n";
+	print gnuout "set xrange [0:8]\n";
+    #print gnuout "unset xtics\n";
+    #print gnuout "unset ytics\n";
+    print gnuout "set key top right\n";
+	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
+	print gnuout "set xtics ('64' 1, '128' 2, '192' 3, '256' 4, '320' 5, '384' 6, '448' 7)\n";
+	print gnuout "set xlabel 'Shortcut Path Threshold (ms)'\n";
+    print gnuout "set ylabel 'Completion Time (ms)'\n";
+    print gnuout "set yrange [800:2400]\n";
+    print gnuout "set ytics 800,400,2400\n";
+    #print gnuout "set key off\n";
+	#print gnuout "set size ratio 0.25\n";
+	#print gnuout "set key bottom right\n";
+    print gnuout "plot 'sp-coflood-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'sp-coflood-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
+    #print gnuout "unset multiplot\n";
+	close gnuout;
+
+	system "gnuplot sp-coflood-result-plot.plt";
+}

### 2020-05-21 abstract.tex
add abstract

\begin{abstract}
\label{abstract}
We use smartphones everywhere and concerns have arisen about ‘shoulder surfing’, or the act of strangers peeking at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms. We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR. We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment’s circumstances) and is robust in different environments. Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
\end{abstract}

### 2020-05-24 evaluation.tex
add implementation

@@
 We train and test the model with the images captured with exactly the same environment parameters. On average the model achieves … accuracy.
-Data	Daytime,1.2m… 	Nighttime,1.2m…	Daytime,1.4m…					
+\begin{table}
+
+\begin{tabular}{c|c|c|c|c} 
+Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
+PSNR(db) & 14.64 & 11.17 & 9.744 & 9.558 \\ \hline
+OCR Accuracy(\%) & 100 & 
+\end{tabular} 
+\caption{Performance in Controlled Environment}
+\end{table}
+DataDaytime,1.2m… Nighttime,1.2m…Daytime,1.4m…
 Difference(PSNR)
@@
 
-Data	Training Environment  	Test
-Environment1	Test2	Test3				
+DataTraining Environment  Test
+Environment1Test2Test3
 Difference(PSNR)
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-Groups of Data	All 10	Night only	1.2m distance only	Direct angle only				
+Groups of DataAll 10Night only1.2m distance onlyDirect angle only
 Difference(PSNR)
@@
 We use less numbers of images in each group of data and see the performance of the models.
-Amount	60,000	40,000	30,000	10,000				
+Amount60,00040,00030,00010,000
 Difference(PSNR)
@@
 We cut the model size for better performance in smartphones. We modify the number of layers, channels in convolution layers, and output channels in merging processes.
-Model	Full	5 layer	32channel					
+ModelFull5 layer32channel
 Parameter Count
@@
 We train and test other commonly used architectures with the same sets of data and evaluate their results.
-Model	Ours	SRCNN						
+ModelOursSRCNN
 Parameter Count
@@
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-Scenario	Home	Office	Public Transport	Theater
+ScenarioHomeOfficePublic TransportTheater
 Valid images
@@
 We repeat our experiment in different distances and evaluate the accuracy.
-Accuracy	Scenario	Home	Office	Public Transport	Theater
+AccuracyScenarioHomeOfficePublic TransportTheater
 Distance
@@
 We capture images of the phone at the same time to see how our system deal with a moving target screen.
-Scenario	Stationary	Handheld camera	Handheld target	‘Handheld camera and target
+ScenarioStationaryHandheld cameraHandheld target‘Handheld camera and target
 Valid images
@@
 For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric.
-Scenario	Read text	Type text	Enter PIN	Enter complex password
+ScenarioRead textType textEnter PINEnter complex password
 Accuracy

### 2020-05-24 implementation.tex
add implementation

@@
 \subsection{Experiment Setting}
-Collect data with a stationary smartphone at 1.5m range…
-Display random characters on screen, with a box surrounding it for supplementary alignment…
-Takes 6 hours to gather one set of training data…
+\label{sec-experiment-setting}
+In our experiment, we are forced to collect the training dataset on our own instead of using public datasets.
+Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing.
+Modern network architectures work with naturally obtained images, e.g.
+ordinary photos, satellite images, scanned documents, YouTube videos, etc.
+where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g.
+the face or the printed word, at least visible to the naked eye.
+and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges.
+However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke.
+Noise and details are not the main issue here, as we need only the facts, deeming it a victory if the neural network returns a noised, wrapped, but readable image.
+These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets.
+And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.
+
+The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network.
+We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset.
+Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.
+However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
+ \begin{figure}
+     \centering
+     \subfigure[input from same environment]{
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1}
+         \label{fig-train-single-1}
+         }
+     \subfigure[output of (a)]{
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2}
+         \label{fig-train-single-2}
+         }
+     \subfigure[input from different environment]{
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5}
+         \label{fig-train-single-3}
+         }
+     \subfigure[output of (c)]{
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4}
+         \label{fig-train-single-4}
+         }
+     \subfigure[ground truth]{
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3}
+         \label{fig-train-single-5}
+         }
+        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
+        \label{fig-train-single}
+\end{figure}
+
+As a result of these observations, we have to collect images in varied environments.
+Our experiment consists of 2 smartphones at a distance between 1 and 2 meters, one for the attacker and one the victim.
+An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos.
+Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture.
+The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets.
+As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters.
+As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker.
+We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones.
+The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees.
+We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection.
+Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
+
+The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.).
+We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter.
+The position of the phones is also a crucial factor in this parameter, and we avoid having the sunlight directly shone on the camera of the attacker or the screen of the victim, as it is extremely difficult to see anything in these extreme circumstances.
+We also draw a box around the characters on the victim's screen for alignment purposes, as although in production our system can detect the edges of the screen for alignment, this method provides more accurate results and possibly accelerates training.
+After collecting the images, we crop them along these boxes, retaining only the characters.
+In the training phase we randomly crop out squares of 9x9 pixels at the corresponding position on the training dataset and ground truth, and feed them into the neural network.
+We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels).
+This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.
+
 \subsection{Model Specifications}
-8 layers with two 2x upsampling layers; 64 channels…
+It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features.
+Thus, the specifications of our model are only for reference and may not work when reproduced on another phone.
+
+Our model accepts 20 images at a time, with a size of 9x9 pixels.
+The model consists of 5 blocks described in the previous section.
+In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output.
+the 20x32 feature maps are then merged horizontally with the max-min-average process, and the output is 5x32 channels.
+Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5x32 channels to form a dataflow of 6x32 channels for each one of the 20 images.
+These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block.
+The kernels in each convolutional layer is 3x3.
+We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks.
+A single 1x1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer.
+This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs.
+As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9x9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.
+
 \subsection{Training Process}
-Collect 10 sets of data at different surroundings: different angles, distance, font size and color…
-Step 1. Train the network with each one of the 10 sets, the model should fit perfectly…
-Step 2. Select the set of data the model is best adapted to, and add a small percentage of images from another set…
-Step 3. When the model stabilizes again, gradually increase the percentage…
-Step 4. Add another set of data, and repeat step2 and 3, until all data is used.
+Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming.
+Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset.
+The model should be able to handle this task easily.
+After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters.
+We add a small percentage of image data from another similar experiment setting into the training data and resume training.
+When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections.
+Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result.
+This phenomenon can be mitigated with dropout and normalization layers.
+As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 2.0m and 1.5m range in the training process, the model fits 1.75m photos easily.
+After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.

### 2020-05-24 abstract.tex
template and double-blind

@@
 \label{abstract}
-We use smartphones everywhere and concerns have arisen about ‘shoulder surfing’, or the act of strangers peeking at our phone in public areas.
+We use smartphones everywhere and concerns have arisen about ``€˜shoulder surfing'',™ or the act of strangers peeking at our phone in public areas.
 This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye.
@@
 We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR.
-We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment’s circumstances) and is robust in different environments.
+We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment's circumstances) and is robust in different environments.
 Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.

### 2020-05-25 evaluation.tex
add evaluation

--- 2020-05-17 evaluation.tex
@@
 \subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters. On average the model achieves … accuracy.
-Data	Daytime,1.2m… 	Nighttime,1.2m…	Daytime,1.4m…					
-Difference(PSNR)								
-OCR Accuracy								
-We compare the results to discover the influence of the surrounding environment: The model performs best in nighttime and strong sunlight may decrease its ability…
+We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control}).
+Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
+On average the model achieves 96.5\% OCR accuracy.
+Considering the complexity of Chinese characters, and the assist of context when read by a human being, we believe this result proves that this model is highly functional when ignoring the environmental parameters.
+
+\begin{table}  
+\begin{tabular}{c|c|c|c|c} 
+Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
+PSNR(db) & 14.64 & 12.39 & 10.728 & 10.259 \\ \hline
+OCR Accuracy(\%) & 100 & 97 & 95 & 94 \\
+\end{tabular} 
+\caption{Performance in Controlled Environment}
+\label{table-control}
+\end{table}
+
 \subsection{Performance In Random Environment}
-We train the model with data captured in 10 different environments and test its ability in another 10 different environments. The model achieves … accuracy. It has a better performance in daytime…
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random}). The model achieves 93.5\% accuracy.
 
-Data	Training Environment  	Test
-Environment1	Test2	Test3				
-Difference(PSNR)								
-OCR Accuracy								
+\begin{table}  
+\begin{tabular}{c|c|c|c|c} 
+Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
+PSNR(db) & 13.32 & 11.17 & 9.744 & 9.558 \\ \hline
+OCR Accuracy(\%) & 100 & 97 & 92 & 85 \\
+\end{tabular} 
+\caption{Performance in Random Environment}
+\label{table-random}
+\end{table}
+
+We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability.
+Also, the model performs better at closer distances, but this difference is trivial.
+
 \subsection{Adapting Ability}
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-Groups of Data	All 10	Night only	1.2m distance only	Direct angle only				
-Difference(PSNR)								
-OCR Accuracy								
-Variations in light parameter in training data is crucial to a robust model. Variations in distance is not so influential to the results.
-\subsection{Data Amount}
-We use less numbers of images in each group of data and see the performance of the models.
-Amount	60,000	40,000	30,000	10,000				
-Difference(PSNR)								
-OCR Accuracy								
-\subsection{Model Size}
-We cut the model size for better performance in smartphones. We modify the number of layers, channels in convolution layers, and output channels in merging processes.
-Model	Full	5 layer	32channel					
-Parameter Count								
-Total training time								
-Difference(PSNR)								
-OCR Accuracy								
+The results are shown in Table~\ref{table-adapt}.
+
+\begin{table*}  
+\begin{tabular}{c|c|c|c|c} 
+Data & All Data & Night only & 1.2m distance only & Direct angle only \\ \hline
+PSNR(db) & 13.32 & 9.17 & 9.94 & 8.84\\ \hline
+OCR Accuracy & 100 & 73 & 80 & 52\\
+\end{tabular} 
+\caption{Adapting Ability}
+\label{table-adapt}
+\end{table*}
+
+We observed that variations in light and angle parameter in training data is crucial to a robust model.
+Variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
+Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size.
+However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process.
+
 \subsection{Comparison with other architectures}
 We train and test other commonly used architectures with the same sets of data and evaluate their results.
-Model	Ours	SRCNN						
-Parameter Count								
-Difference(PSNR)								
-OCR Accuracy
+We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing.
+We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR).
+However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results.
+We used the relatively easys 'daytime 1.2m-distance direct' group of data for testing.
+The results are shown in Table~\ref{table-comp}.
+
+\begin{table}  
+\begin{tabular}{c|c|c|c} 
+Model & Ours & SRCNN & VideoSR \\ \hline
+PSNR(db) & 13.32 & 7.690 & 8.403 \\ \hline
+OCR Accuracy(\%) & 100 & 10 & 23 \\
+\end{tabular} 
+\caption{Comparison with other architectures}
+\label{table-comp}
+\end{table}
 
@@
 We build the system on smartphone and evaluate its performance in real-life environments.
-We experiment with … smartphone for the attacker and … smartphone for the victim.
+We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
 We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model.
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-Scenario	Home	Office	Public Transport	Theater
-Valid images				
-Running time				
-OCR Accuracy				
-Human Recognition Accuracy(raw data)				
-Human Recognition Accuracy(processed image)				
-Human Recognition Time				
-\subsection{Influence of distance}
-We repeat our experiment in different distances and evaluate the accuracy.
-Accuracy	Scenario	Home	Office	Public Transport	Theater
-Distance					
-1m					
-1.2m					
-1.4m					
-1.6m					
-2m					
+The results are shown in Table~\ref{table-accuracy}.
+
+\begin{table*}  
+\begin{tabular}{c|c|c|c} 
+Scenario & Home & Transport & Theater\\ \hline
+Valid images & 20 & 20 & 20\\ \hline
+OCR Accuracy(\%) & 95 & 80 & 65\\ \hline
+Human Recognition Accuracy(raw data)(\%) & 5 & 0 & 0\\ \hline
+Human Recognition Accuracy(processed image)(\%) & 95 & 85 & 70 \\
+\end{tabular} 
+\caption{Accuracy in different real-life scenarios}
+\label{table-accuracy}
+\end{table*}
+
 \subsection{Influence of hand tremors}
@@
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.
-Scenario	Stationary	Handheld camera	Handheld target	‘Handheld camera and target
-Valid images				
-Running time				
-OCR Accuracy				
-Human Recognition Accuracy(raw data)				
-Human Recognition Accuracy(processed image)				
-Human Recognition Time				
+We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Table~\ref{table-tremor}.
+\begin{table*}  
+\begin{tabular}{c|c|c|c|c} 
+Scenario &Stationary & Handheld camera & Handheld target & Handheld camera and target\\ \hline
+Valid images & 20 & 19 & 20 & 18\\ \hline
+OCR Accuracy(\%) & 95 & 85 & 80 & 80\\ \hline
+Human Recognition Accuracy(raw data)(\%) & 5 & 0 & 5 & 5\\ \hline
+Human Recognition Accuracy(processed image)(\%) & 95 & 85 & 80 & 85
+\end{tabular} 
+\caption{Influence of hand tremors}
+\label{table-tremor}
+\end{table*}
+
+We conclude from the results that hand tremors can impact the performance of our system.
+Although the edges of the phone are notable marks for image alignment, small shifts in the sub-pixel level will cause blurriness in the results of the networks, lowering the readability of the outputs.
+
 \subsection{Success rate in different tasks}
@@
 For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric.
-Scenario	Read text	Type text	Enter PIN	Enter complex password
-Accuracy				
-Accuracy per character				
-Human Recognition Accuracy(raw image)				
-Human Recognition Accuracy(Processed image)				
-Human Recognition Time				
+The results are shown in Table~\ref{table-task}.
+
+\begin{table*}  
+\begin{tabular}{c|c|c|c|c} 
+Scenario & Read text & Type text & Enter PIN & Enter complex password\\ \hline
+Human Recognition Accuracy(raw image) & 5 & 0 & 0 & 0\\ \hline
+Accuracy & 100 & 100 & - & -\\ \hline
+Accuracy per character& - & - & 100 & 80\\ 
+\end{tabular}
+\caption{Success rate in different tasks}
+\label{table-task}
+\end{table*}
+
+We prove from this experiment that our system functions normally in everyday scenarios and poses a threat to screen privacy.
+
 \subsection{Perceived shoulder surfing susceptibility}
 We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario.
+The attacker will be sitting or standing behind the participant at 1.5m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.
+None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing.
+We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.
 \section{Limitations}

### 2020-06-14 abstract.tex
modified introduction

@@
 \label{abstract}
-We use smartphones everywhere and concerns have arisen about ``€˜shoulder surfing'',™ or the act of strangers peeking at our phone in public areas.
+We use smartphones everywhere and concerns have arisen about ``shoulder surfing'', or the act of strangers peeking at our phone in public areas.
 This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye.

### 2020-06-14 introduction.tex
modified introduction

@@
 As a result, some concerns of privacy have arisen about nearby parties peeking at our screen, or ‘shoulder surfing’.
-Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet.
+Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet on the privacy critical stages (e.g.
+password entry) of most everyday apps.
 
 On the other hand, many works in this area are built on a threat model of an attacker observing with his/hers naked eye, as they assume that the attacker is not malicious and merely take several peeks out of curiosity.
-However, it is the rare but malicious and prepared attacker that can do the most harm, and leave aside special equipment, if we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim.
+Although studies have shown that a great portion of these attacks are casual and opportunistic without technical equipment\cite{eiband2017understanding}, however, a mere stranger can hardly do any harm reading a fragment of your correspondence or acquiring your password without knowing your account(which, in critical apps like Alipay, seldom appears on screen in common usage).
+It is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm.
+The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents, and, unaware that electronic payments consists of 'real' money, ends up spending them lavishly in their games.
+What's more, specially made equipment are not a necessity for these attacks to happen.
+If we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim.
 For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
-Moreover, smartphone cameras have seen great improvement these years, and as a highly-accessible ‘extension of the eye’, it is possible that ‘shoulder surfers’ peek at others’ screen through their smartphone lenses to obtain critical information like passwords or private e-mails.
-What’s more, recent developments in the field of super resolution (SR) pose a greater threat to smartphone privacy.
-Attackers can take multiple snapshots of the victim’s screen and process them with multiple image super resolution algorithms in real time, making them able to see clearly while keeping a longer distance.
-However, most SR methods are designed for and trained on naturally taken images \cite{nasrollahi2020deep} \cite{lyn2020image}; few works have focused on reconstructing blurry snapshots taken at extreme distances, and a new architecture needs to be designed.
+Moreover, smartphones have seen great improvement these years.
+Equipped with multiple cameras, the newest generation of smartphones can perform 100x zooming compared to the standard 5x of single camera phones.
+Improvements in memory hardware also allows burst mode at tremendous frame rates and even high-speed photography, recording videos with thousands of frames per second, and more images means more information.
+By capturing multiple images of the victim's phone, and processing them with multi-frame super resolution (SR) methods, the attacker can gain vital data from even further away.
+In this present era where the leakage of a password can cost thousands, and the disclosure of correspondence of public figures can cause huge sensations in media and great damage to the victim, we believe that it's imminent to recall attention on this privacy threat and propose a new standard of screen protection based on modern circumstances.
 
-To explore this rarely studied privacy threat of the attacker looking through a smartphone camera, we have developed a holistic system for shoulder surfing.
-The fictional attacker captures multiple images of the victim’s screen in burst mode from his smartphone, and enhances its resolution with our multi-frame super resolution neural network.
-The network is designed and trained for this purpose, targeting several blurry images taken in quick succession of a screen at a distance.
-As the information of interest is mostly displayed on screen in the form of text (e.g.
-passwords or e-mails), our network focuses on reconstructing text, specifically, Chinese characters, English letters, and numbers.
-The system is deployed on a smartphone for demonstration, capturing and processing images at real time.
-Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition of video clips.
+While exploring this privacy threat, we need to implement a multi-frame SR algorithm on a smartphone in order to monitor the target phone in real time.
+However, we discovered that there is no published SR algorithm suitable for this scenario.
+Apparently, the blurriness of the images calls for deep-learning based methods, however most of these methods function on a handful of clearer images(scenary, scanned images, etc.) \cite{nasrollahi2020deep} \cite{lyn2020image}, but we have to merge the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances(to test the theorectical limits of the privacy threat).
+The different nature between videos and multiple snapshots also rules out the video super resolution methods.
+The algorithms cannot be adapted to function on larger numbers of input images, because 1) either increased input leads to increases in model complexity, making it unsuitable for mobile deployment, or 2) they lack emphesis on the process of horizontal comparison, relying heavily on the information extracted from each single image, and thus merges the information inefficiency and show unsatisfactory performance.
+
+To explore this privacy threat and to fill the gap in deep-learning based multi-frame super resolution, we designed an end-to-end CNN-based architecture for shoulder surfing and similar multi-frame SR applications with massive input and blurry images.
+To utilize the large amount of data with low computational complexity, we designed a unique merging layer and placed it between convolutional layers in the SR pipeline.
+The input images are processed independently and the information extracted are then merged together, serving as a reference for the following convolutions.
+With the network as core, We then implemented a holistic system for shoulder surfing on a smartphone, which captures multiple images in burst mode, process them with our neural network to generate a high-res image, and repeating this process for constant monitoring.
+As the information of interest is mostly in the form of text (e.g.
+passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios.
+Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.
 

### 2020-06-14 code/chase/apps/ChaseTest/ChaseSerial.h

@@ -1,34 +1,0 @@
-#ifndef CHASE_SERIAL_H_
-#define CHASE_SERIAL_H_
-
-typedef nx_struct chase_flood_msg {
-  nx_uint16_t seq_no;
-  nx_uint16_t time_flood_h;
-  nx_uint16_t time_flood_l;
-} chase_flood_msg_t;
-
-typedef nx_struct chase_delay_msg {
-  nx_uint16_t nodeid;
-  nx_uint16_t seq_no;
-  nx_uint16_t src_id;
-  nx_uint16_t rec_time_h;
-  nx_uint16_t rec_time_l;
-  nx_uint16_t hop_delay_h;
-  nx_uint16_t hop_delay_l;
-} chase_delay_msg_t;
-
-typedef nx_struct chase_energy_msg {
-  nx_uint16_t nodeid;
-  nx_uint16_t clock_time_h;
-  nx_uint16_t clock_time_l;
-  nx_uint16_t dc_time_h;
-  nx_uint16_t dc_time_l;
-} chase_energy_msg_t;
-
-enum {
-  AM_CHASE_FLOOD_MSG = 22,
-  AM_CHASE_DELAY_MSG = 44,
-  AM_CHASE_ENERGY_MSG = 77,
-};
-
-#endif

### 2020-06-14 code/chase/include/cc2420_x_control.h

@@ -1,18 +1,0 @@
-#ifndef _CC2420_X_CONTROL_H_
-#define _CC2420_X_CONTROL_H_
-
-#include "CC2420.h"
-#include "cc2420_x_spi.h"
-
-// RSSI and CCA Status and Control Register
-static inline int cc2420_get_rssi() {
-  int rssi = ( 0xff & get_register(CC2420_RSSI) );
-  if (rssi > 128) {
-    rssi = rssi - 256 - 45;
-  } else {
-    rssi = rssi - 45;
-  }
-  return rssi;
-}
-
-#endif

### 2020-06-14 code/chase/include/pr.h

@@ -1,24 +1,0 @@
-#ifndef PR_H
-#define PR_H
-
-#ifdef ENABLE_PR
-
-
-#ifndef TOSSIM
-#include "printf.h"
-
-#define pr(fmt, args...) do { printf(fmt, ##args); printfflush(); } while (0)
-#else
-
-#define pr(fmt, args...) dbg("Sim", fmt, ##args)
-
-#endif // TOSSIM
-
-#else
-
-#define pr(fmt, args...) 
-
-#endif // ENABLE_PR
-
-
-#endif /* PR_H */

### 2020-06-14 code/chase/script/Indriya/chase_power3_2/delay_analysis_contiki.pl

@@ -1,125 +1,0 @@
-@delay[3000];
-@is_cal[3000];
-@rec[3000];
-@src[3000];
-@hop[3000];
-@time_rec[3000];
-@src_delay[3000];
-
-@count[20];
-@avg_delay[20];
-
-for ($i = 0; $i < 20; $i++) {
-	@delay[20+$i] = 0;
-	@time_rec[20+$i] = 0;
-	@is_cal[20+$i] = 1;
-	@rec[20+$i] = 1;
-	@hop[20+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 20) {
-		@rec[20+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[20+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 20) {
-		@rec[$nodeid*20+$seq_no] = 1;
-        @src[$nodeid*20+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*20+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*20+$seq_no] = $tmp_time;
-	}
-}
-close fin;
-
-=pod
-for ($i = 1; $i < 50; $i++) {
-	for ($j = 0; $j < 20; $j++) {
-		@rec[$i*20+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-
-      if (@log[0] eq "delay:") {
-        $seq_no = @log[1];
-        if ($seq_no < 20) {
-        	@rec[$i*20+$seq_no] = 1;
[…]

### 2020-06-14 code/chase/script/chase/chase1/delay_analysis.pl

@@ -1,108 +1,0 @@
-@delay[500];
-@is_cal[500];
-@rec[500];
-@src[500];
-@time_rec[500];
-@src_delay[500];
-
-@count[10];
-@avg_delay[10];
-@com_time[10];
-
-@duty_cyle[50];
-
-for ($i = 0; $i < 10; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 10; $j++) {
-		@rec[$i*10+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 10) {
-        	@rec[$i*10+$seq_no] = 1;
-        	@src[$i*10+$seq_no] = @log[2];
-        	@time_rec[$i*10+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*10+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 10) {
-      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
-        $radio_on_time = @log[3]*65535 + @log[4];
-        $time_now = @log[1]*65535 + @log[2];
-        @duty_cycle[$i] = $radio_on_time / $time_now;
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 10; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*10+$i] == 1) {
-			if (@is_cal[$j*10+$i] == 0) {
-				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
-					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
[…]

### 2020-06-14 code/chase/script/contiki log/contiki0/delay_analysis_contiki.pl

@@ -1,114 +1,0 @@
-@delay[1000];
-@is_cal[1000];
-@rec[1000];
-@src[1000];
-@hop[1000];
-@time_rec[1000];
-@src_delay[1000];
-
-@count[20];
-@avg_delay[20];
-@com_time[20];
-
-@duty_cycle[50];
-
-for ($i = 0; $i < 20; $i++) {
-	@delay[20+$i] = 0;
-	@time_rec[20+$i] = 0;
-	@is_cal[20+$i] = 1;
-	@rec[20+$i] = 1;
-	@hop[20+$i] = 0;
-}
-
-for ($i = 1; $i < 50; $i++) {
-	for ($j = 0; $j < 20; $j++) {
-		@rec[$i*20+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-
-      if (@log[0] eq "delay:") {
-        $seq_no = @log[1];
-        if ($seq_no < 20) {
-        	@rec[$i*20+$seq_no] = 1;
-        	@src[$i*20+$seq_no] = @log[4];
-        	@time_rec[$i*20+$seq_no] = @log[6];
-        	@src_delay[$i*20+$seq_no] = @log[7];
-        }
-      } elsif (@log[0] eq "flood:") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 20) {
-      		@rec[$i*20+$seq_no] = 1;
-      		@time_rec[$i*20+$seq_no] = @log[2];
-      	}
-      } elsif (@log[1] eq "P") {
-      	@duty_cycle[$i] = @log[17];
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 20; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*20+$i] == 1) {
-			if (@is_cal[$j*20+$i] == 0) {
-				if (@is_cal[@src[$j*20+$i]*20+$i] == 1) {
-					@delay[$j*20+$i] = @delay[@src[$j*20+$i]*20+$i] + @src_delay[$j*20+$i] - @time_rec[@src[$j*20+$i]*20+$i];
-					@hop[$j*20+$i] = @hop[@src[$j*20+$i]*20+$i] + 1;
[…]

### 2020-06-14 code/chase/script/contiki log/contiki4/delay_analysis_contiki.pl

@@ -1,107 +1,0 @@
-@delay[1000];
-@is_cal[1000];
-@rec[1000];
-@src[1000];
-@hop[1000];
-@time_rec[1000];
-@src_delay[1000];
-
-@count[20];
-@avg_delay[20];
-@com_time[20];
-
-for ($i = 0; $i < 20; $i++) {
-	@delay[20+$i] = 0;
-	@time_rec[20+$i] = 0;
-	@is_cal[20+$i] = 1;
-	@rec[20+$i] = 1;
-	@hop[20+$i] = 0;
-}
-
-for ($i = 1; $i < 50; $i++) {
-	for ($j = 0; $j < 20; $j++) {
-		@rec[$i*20+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-
-      if (@log[0] eq "delay:") {
-        $seq_no = @log[1];
-        if ($seq_no < 20) {
-        	@rec[$i*20+$seq_no] = 1;
-        	@src[$i*20+$seq_no] = @log[4];
-        	@time_rec[$i*20+$seq_no] = @log[6];
-        	@src_delay[$i*20+$seq_no] = @log[7];
-        }
-      } elsif (@log[0] eq "flood:") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 20) {
-      		@rec[$i*20+$seq_no] = 1;
-      		@time_rec[$i*20+$seq_no] = @log[2];
-      	}
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 20; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*20+$i] == 1) {
-			if (@is_cal[$j*20+$i] == 0) {
-				if (@is_cal[@src[$j*20+$i]*20+$i] == 1) {
-					@delay[$j*20+$i] = @delay[@src[$j*20+$i]*20+$i] + @src_delay[$j*20+$i] - @time_rec[@src[$j*20+$i]*20+$i];
-					@hop[$j*20+$i] = @hop[@src[$j*20+$i]*20+$i] + 1;
-					#if ($hops == 1) {
[…]

### 2020-06-14 code/chase/script/deludge log/deludge2/delay_analysis.pl

@@ -1,80 +1,0 @@
-@delay[500];
-@is_cal[500];
-@rec[500];
-@src[500];
-@time_rec[500];
-@src_delay[500];
-
-@count[10];
-@avg_delay[10];
-
-for ($i = 0; $i < 10; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 10; $j++) {
-		@rec[$i*10+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 10) {
-        	@rec[$i*10+$seq_no] = 1;
-        	@src[$i*10+$seq_no] = @log[2];
-        	@time_rec[$i*10+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*10+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 10) {
-      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
-      	}
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 10; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*10+$i] == 1) {
-			if (@is_cal[$j*10+$i] == 0) {
-				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
-					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
-					#if ($hops == 1) {
-					#	printf "hops $hops nodeid $j srcid @src[$j*10+$i] src_delay @src_delay[$j*10+$i] delay @delay[$j*10+$i]\n";
-					#}
-					@is_cal[$j*10+$i] = 1;
-				} 
-			}
-		} 
-	}
-}
-$hops++;
-}
-
-
[…]

### 2020-06-14 code/chase/script/deludge log/deludge6/delay_analysis.pl

@@ -1,98 +1,0 @@
-@delay[2000];
-@is_cal[2000];
-@rec[2000];
-@src[2000];
-@time_rec[2000];
-@src_delay[2000];
-@hop[2000];
-
-@count[40];
-@avg_delay[40];
-@com_time[40];
-
-@duty_cyle[50];
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-	@hop[$i] = 0;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 40; $j++) {
-		@rec[$i*40+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 40) {
-        	@rec[$i*40+$seq_no] = 1;
-        	@src[$i*40+$seq_no] = @log[2];
-        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 40) {
-      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
-        $radio_on_time = @log[3]*65535 + @log[4];
-        $time_now = @log[1]*65535 + @log[2];
-        @duty_cycle[$i] = $radio_on_time / $time_now;
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 40; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*40+$i] == 1) {
-			if (@is_cal[$j*40+$i] == 0) {
-				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
[…]

### 2020-06-14 code/chase/script/log 3-27 10_27/delay_analysis_contiki.pl

@@ -1,86 +1,0 @@
-@delay[500];
-@is_cal[500];
-@rec[500];
-@src[500];
-@hop[500];
-@time_rec[500];
-@src_delay[500];
-
-@count[10];
-@avg_delay[10];
-
-for ($i = 0; $i < 10; $i++) {
-	@delay[10+$i] = 0;
-	@time_rec[10+$i] = 0;
-	@is_cal[10+$i] = 1;
-	@rec[10+$i] = 1;
-	@hop[10+$i] = 0;
-}
-
-for ($i = 1; $i < 50; $i++) {
-	for ($j = 0; $j < 10; $j++) {
-		@rec[$i*10+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-
-      if (@log[0] eq "delay:") {
-        $seq_no = @log[1];
-        if ($seq_no < 10) {
-        	@rec[$i*10+$seq_no] = 1;
-        	@src[$i*10+$seq_no] = @log[4];
-        	@time_rec[$i*10+$seq_no] = @log[6];
-        	@src_delay[$i*10+$seq_no] = @log[7];
-        }
-      } elsif (@log[0] eq "flood:") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 10) {
-      		@rec[$i*10+$seq_no] = 1;
-      		@time_rec[$i*10+$seq_no] = @log[2];
-      	}
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 10; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*10+$i] == 1) {
-			if (@is_cal[$j*10+$i] == 0) {
-				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
-					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
-					@hop[$j*10+$i] = @hop[@src[$j*10+$i]*10+$i] + 1;
-					#if ($hops == 1) {
[…]

### 2020-06-14 code/chase/script/log 3-28 8_25/delay_analysis_contiki.pl

@@ -1,86 +1,0 @@
-@delay[1000];
-@is_cal[1000];
-@rec[1000];
-@src[1000];
-@hop[1000];
-@time_rec[1000];
-@src_delay[1000];
-
-@count[20];
-@avg_delay[20];
-
-for ($i = 0; $i < 20; $i++) {
-	@delay[20+$i] = 0;
-	@time_rec[20+$i] = 0;
-	@is_cal[20+$i] = 1;
-	@rec[20+$i] = 1;
-	@hop[20+$i] = 0;
-}
-
-for ($i = 1; $i < 50; $i++) {
-	for ($j = 0; $j < 20; $j++) {
-		@rec[$i*20+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-
-      if (@log[0] eq "delay:") {
-        $seq_no = @log[1];
-        if ($seq_no < 20) {
-        	@rec[$i*20+$seq_no] = 1;
-        	@src[$i*20+$seq_no] = @log[4];
-        	@time_rec[$i*20+$seq_no] = @log[6];
-        	@src_delay[$i*20+$seq_no] = @log[7];
-        }
-      } elsif (@log[0] eq "flood:") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 20) {
-      		@rec[$i*20+$seq_no] = 1;
-      		@time_rec[$i*20+$seq_no] = @log[2];
-      	}
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 20; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*20+$i] == 1) {
-			if (@is_cal[$j*20+$i] == 0) {
-				if (@is_cal[@src[$j*20+$i]*20+$i] == 1) {
-					@delay[$j*20+$i] = @delay[@src[$j*20+$i]*20+$i] + @src_delay[$j*20+$i] - @time_rec[@src[$j*20+$i]*20+$i];
-					@hop[$j*20+$i] = @hop[@src[$j*20+$i]*20+$i] + 1;
-					#if ($hops == 1) {
[…]

### 2020-06-14 code/chase/script/trickle log/trickle4/delay_analysis.pl

@@ -1,95 +1,0 @@
-@delay[2000];
-@is_cal[2000];
-@rec[2000];
-@src[2000];
-@time_rec[2000];
-@src_delay[2000];
-
-@count[40];
-@avg_delay[40];
-@com_time[40];
-
-@duty_cyle[50];
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 40; $j++) {
-		@rec[$i*40+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 40) {
-        	@rec[$i*40+$seq_no] = 1;
-        	@src[$i*40+$seq_no] = @log[2];
-        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no+1 < 40) {
-      		@time_rec[$seq_no+1] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
-        $radio_on_time = @log[3]*65535 + @log[4];
-        $time_now = @log[1]*65535 + @log[2];
-        @duty_cycle[$i] = $radio_on_time / $time_now;
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 40; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*40+$i] == 1) {
-			if (@is_cal[$j*40+$i] == 0) {
-				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
-					@delay[$j*40+$i] = @delay[@src[$j*40+$i]*40+$i] + @src_delay[$j*40+$i] - @time_rec[@src[$j*40+$i]*40+$i];
-					if ($hops == 1) {
[…]

### 2020-06-14 code/chase/script/trickle-amac log/trickle-amac1/delay_analysis.pl

@@ -1,80 +1,0 @@
-@delay[500];
-@is_cal[500];
-@rec[500];
-@src[500];
-@time_rec[500];
-@src_delay[500];
-
-@count[10];
-@avg_delay[10];
-
-for ($i = 0; $i < 10; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 10; $j++) {
-		@rec[$i*10+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 10) {
-        	@rec[$i*10+$seq_no] = 1;
-        	@src[$i*10+$seq_no] = @log[2];
-        	@time_rec[$i*10+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*10+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no+1 < 10) {
-      		@time_rec[$seq_no+1] = @log[2] * 65535 + @log[3];
-      	}
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 10; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*10+$i] == 1) {
-			if (@is_cal[$j*10+$i] == 0) {
-				if (@is_cal[@src[$j*10+$i]*10+$i] == 1) {
-					@delay[$j*10+$i] = @delay[@src[$j*10+$i]*10+$i] + @src_delay[$j*10+$i] - @time_rec[@src[$j*10+$i]*10+$i];
-					if ($hops == 1) {
-						printf "hops $hops nodeid $j srcid @src[$j*10+$i] src_delay @src_delay[$j*10+$i] time_rec @time_rec[@src[$j*10+$i]*10+$i] delay @delay[$j*10+$i]\n";
-					}
-					@is_cal[$j*10+$i] = 1;
[…]

### 2020-06-14 code/chase/script/trickle-amac log/trickle-amac3/delay_analysis.pl

@@ -1,95 +1,0 @@
-@delay[2000];
-@is_cal[2000];
-@rec[2000];
-@src[2000];
-@time_rec[2000];
-@src_delay[2000];
-
-@count[40];
-@avg_delay[40];
-@com_time[40];
-
-@duty_cyle[50];
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 40; $j++) {
-		@rec[$i*40+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 40) {
-        	@rec[$i*40+$seq_no] = 1;
-        	@src[$i*40+$seq_no] = @log[2];
-        	@time_rec[$i*40+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*40+$seq_no] = @log[5] * 65535 + @log[6];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no+1 < 40) {
-      		@time_rec[$seq_no+1] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
-        $radio_on_time = @log[3]*65535 + @log[4];
-        $time_now = @log[1]*65535 + @log[2];
-        @duty_cycle[$i] = $radio_on_time / $time_now;
-      }
-    }
-    close fin;
-}
-
-$hops = 1;
-
-while ($hops < 10) {
-for ($i = 0; $i < 40; $i++) {
-	for ($j = 1; $j < 50; $j++) {
-		if (@rec[$j*40+$i] == 1) {
-			if (@is_cal[$j*40+$i] == 0) {
-				if (@is_cal[@src[$j*40+$i]*40+$i] == 1) {
-					@delay[$j*40+$i] = @delay[@src[$j*40+$i]*40+$i] + @src_delay[$j*40+$i] - @time_rec[@src[$j*40+$i]*40+$i];
-					if ($hops == 1) {
[…]

### 2020-06-14 code/coflood/apps/COFloodTest/ChaseDelayMsg.java

@@ -1,1016 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'ChaseDelayMsg'
- * message type.
- */
-
-public class ChaseDelayMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 25;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 44;
-
-    /** Create a new ChaseDelayMsg of size 25. */
-    public ChaseDelayMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new ChaseDelayMsg of the given data_length. */
-    public ChaseDelayMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg with the given data_length
-     * and base offset.
-     */
-    public ChaseDelayMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store.
-     */
-    public ChaseDelayMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public ChaseDelayMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public ChaseDelayMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg embedded in the given message
-     * at the given base offset.
-     */
-    public ChaseDelayMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg embedded in the given message
[…]

### 2020-06-14 code/coflood/apps/COFloodTest/ChaseEnergyMsg.java

@@ -1,422 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'ChaseEnergyMsg'
- * message type.
- */
-
-public class ChaseEnergyMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 10;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 77;
-
-    /** Create a new ChaseEnergyMsg of size 10. */
-    public ChaseEnergyMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new ChaseEnergyMsg of the given data_length. */
-    public ChaseEnergyMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg with the given data_length
-     * and base offset.
-     */
-    public ChaseEnergyMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg using the given byte array
-     * as backing store.
-     */
-    public ChaseEnergyMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public ChaseEnergyMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public ChaseEnergyMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg embedded in the given message
-     * at the given base offset.
-     */
-    public ChaseEnergyMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseEnergyMsg embedded in the given message
[…]

### 2020-06-14 code/coflood/apps/COFloodTest/ChaseSerial.h

@@ -1,41 +1,0 @@
-#ifndef CHASE_SERIAL_H_
-#define CHASE_SERIAL_H_
-
-typedef nx_struct chase_flood_msg {
-  nx_uint16_t seq_no;
-  nx_uint16_t time_flood_h;
-  nx_uint16_t time_flood_l;
-} chase_flood_msg_t;
-
-typedef nx_struct chase_delay_msg {
-  nx_uint16_t nodeid;
-  nx_uint16_t seq_no;
-  nx_uint16_t src_id;
-  nx_uint16_t rec_time_h;
-  nx_uint16_t rec_time_l;
-  nx_uint16_t hop_delay_h;
-  nx_uint16_t hop_delay_l;
-  nx_uint16_t parent_ETD;
-  nx_uint16_t local_ETD;
-  nx_uint16_t delta_ETD;
-  nx_uint8_t long_link_sender;
-  nx_uint16_t MPD;
-  nx_uint8_t shortcut_sender;
-  nx_uint8_t tree_sender;
-} chase_delay_msg_t;
-
-typedef nx_struct chase_energy_msg {
-  nx_uint16_t nodeid;
-  nx_uint16_t clock_time_h;
-  nx_uint16_t clock_time_l;
-  nx_uint16_t dc_time_h;
-  nx_uint16_t dc_time_l;
-} chase_energy_msg_t;
-
-enum {
-  AM_CHASE_FLOOD_MSG = 22,
-  AM_CHASE_DELAY_MSG = 44,
-  AM_CHASE_ENERGY_MSG = 77,
-};
-
-#endif

### 2020-06-14 code/coflood/apps/COFloodTest/TreeBeaconMsg.java

@@ -1,554 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'TreeBeaconMsg'
- * message type.
- */
-
-public class TreeBeaconMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 14;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 68;
-
-    /** Create a new TreeBeaconMsg of size 14. */
-    public TreeBeaconMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new TreeBeaconMsg of the given data_length. */
-    public TreeBeaconMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg with the given data_length
-     * and base offset.
-     */
-    public TreeBeaconMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg using the given byte array
-     * as backing store.
-     */
-    public TreeBeaconMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public TreeBeaconMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public TreeBeaconMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg embedded in the given message
-     * at the given base offset.
-     */
-    public TreeBeaconMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TreeBeaconMsg embedded in the given message
-     * at the given base offset and length.
-     */
[…]

### 2020-06-14 code/coflood/apps/ChaseTest/ChaseTailMsg.java

@@ -1,356 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'ChaseTailMsg'
- * message type.
- */
-
-public class ChaseTailMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 8;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 99;
-
-    /** Create a new ChaseTailMsg of size 8. */
-    public ChaseTailMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new ChaseTailMsg of the given data_length. */
-    public ChaseTailMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg with the given data_length
-     * and base offset.
-     */
-    public ChaseTailMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg using the given byte array
-     * as backing store.
-     */
-    public ChaseTailMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public ChaseTailMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public ChaseTailMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg embedded in the given message
-     * at the given base offset.
-     */
-    public ChaseTailMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseTailMsg embedded in the given message
-     * at the given base offset and length.
-     */
[…]

### 2020-06-14 code/coflood/apps/ChaseTest/ChaseTest.h

@@ -1,8 +1,0 @@
-#ifndef CHASETEST_H_
-#define CHASETEST_H_
-
-typedef nx_struct {
-  nx_uint8_t data[100];
-} flood_payload_t;
-
-#endif

### 2020-06-14 code/coflood/apps/SenderNumber/ChaseDelayMsg.java

@@ -1,554 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'ChaseDelayMsg'
- * message type.
- */
-
-public class ChaseDelayMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 14;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 44;
-
-    /** Create a new ChaseDelayMsg of size 14. */
-    public ChaseDelayMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new ChaseDelayMsg of the given data_length. */
-    public ChaseDelayMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg with the given data_length
-     * and base offset.
-     */
-    public ChaseDelayMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store.
-     */
-    public ChaseDelayMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public ChaseDelayMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public ChaseDelayMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg embedded in the given message
-     * at the given base offset.
-     */
-    public ChaseDelayMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new ChaseDelayMsg embedded in the given message
-     * at the given base offset and length.
[…]

### 2020-06-14 code/coflood/apps/TopologyTest/TopologyMsg.java

@@ -1,290 +1,0 @@
-/**
- * This class is automatically generated by mig. DO NOT EDIT THIS FILE.
- * This class implements a Java interface to the 'TopologyMsg'
- * message type.
- */
-
-public class TopologyMsg extends net.tinyos.message.Message {
-
-    /** The default size of this message type in bytes. */
-    public static final int DEFAULT_MESSAGE_SIZE = 5;
-
-    /** The Active Message type associated with this message. */
-    public static final int AM_TYPE = 34;
-
-    /** Create a new TopologyMsg of size 5. */
-    public TopologyMsg() {
-        super(DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /** Create a new TopologyMsg of the given data_length. */
-    public TopologyMsg(int data_length) {
-        super(data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg with the given data_length
-     * and base offset.
-     */
-    public TopologyMsg(int data_length, int base_offset) {
-        super(data_length, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg using the given byte array
-     * as backing store.
-     */
-    public TopologyMsg(byte[] data) {
-        super(data);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg using the given byte array
-     * as backing store, with the given base offset.
-     */
-    public TopologyMsg(byte[] data, int base_offset) {
-        super(data, base_offset);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg using the given byte array
-     * as backing store, with the given base offset and data length.
-     */
-    public TopologyMsg(byte[] data, int base_offset, int data_length) {
-        super(data, base_offset, data_length);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg embedded in the given message
-     * at the given base offset.
-     */
-    public TopologyMsg(net.tinyos.message.Message msg, int base_offset) {
-        super(msg, base_offset, DEFAULT_MESSAGE_SIZE);
-        amTypeSet(AM_TYPE);
-    }
-
-    /**
-     * Create a new TopologyMsg embedded in the given message
-     * at the given base offset and length.
-     */
-    public TopologyMsg(net.tinyos.message.Message msg, int base_offset, int data_length) {
[…]

### 2020-06-14 code/coflood/apps/TopologyTest/TopologyTest.h

@@ -1,20 +1,0 @@
-#ifndef TOPOLOGYTEST_H_
-#define TOPOLOGYTEST_H_
-
-typedef nx_struct topology_msg {
-    nx_uint16_t id;
-    nx_uint16_t src;
-    nx_uint8_t rssi;
-} topology_msg_t;
-
-typedef nx_struct tree_beacon {
-    nx_uint16_t id;
-    nx_uint16_t ebw;
-    nx_uint16_t elder_id;
-} tree_beacon_t;
-
-enum {
-    AM_TOPOLOGY_MSG = 0x22,
-};
-
-#endif

### 2020-06-14 code/coflood/include/Chase.h

@@ -1,68 +1,0 @@
-#ifndef CHASE_H_
-#define CHASE_H_
-
-#include "CC2420.h"
-
-#define RSSI_SAMPLES_NUM 128
-
-#define CC2420_FIFOP_DISABLE()\
-                              do {\
-                                P1IFG &= ~(1 << 0); \
-                                P1IE &= ~(1 << 0);  \
-                              } while(0)
-
-#define CC2420_FIFOP_ENABLE() \
-                              do { \
-                                P1IFG &= ~(1 << 0); \
-                                P1IE |= (1 << 0);   \
-                              } while(0)
-
-#define ABS_VALUE(a, b) ( (a > b) ? a-b : b-a )
-
-typedef enum {
-  DUTY_CYCLE_IDL,
-  DUTY_CYCLE_DET,
-  DUTY_CYCLE_LIS,
-  DUTY_CYCLE_REC,
-  DUTY_CYCLE_SND,
-  DUTY_CYCLE_OFF,
-} chase_radio_state_t;
-
-typedef nx_struct {
-  nx_uint16_t src_id;
-  nx_uint16_t seq_no;
-  nx_uint16_t fwd_id;
-  nx_uint16_t local_delay;
-  nx_uint16_t start_time_h;
-  nx_uint16_t start_time_l;
-  nx_uint16_t fwd_time_h;
-  nx_uint16_t fwd_time_l;
-} chase_header_t;
-
-typedef struct {
-  uint16_t src_id;
-  uint16_t seq_no;
-  uint16_t last_hop_id;
-  uint16_t per_hop_delay_h;
-  uint16_t per_hop_delay_l;
-  uint16_t parent_ETD;
-  uint16_t local_ETD;
-  uint16_t delta_ETD;
-  uint8_t long_link_sender;
-  uint16_t MPD;
-  uint8_t shortcut_sender;
-  uint8_t tree_sender;
-} chase_delay_t;
-
-typedef nx_struct chase_tail_msg {
-  nx_uint16_t nodeid;
-  nx_uint16_t seq_no;
-  nx_uint16_t tail_time_h;
-  nx_uint16_t tail_time_l;
-} chase_tail_msg_t;
-
-enum {
-  AM_CHASE_TAIL_MSG = 99,
-};
-
-#endif

### 2020-06-14 code/coflood/script/Indriya/diff_senders/20_22_31_long/delay_analysis_contiki.pl

@@ -1,235 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-
-@duty_cycle[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
-	}
-}
-close fin;
-
-$log_file = "energy.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-    $total_time = @log[1] * 65536 + @log[2];
-    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-06-14 code/coflood/script/Indriya/diff_senders/30_22_31/delay_analysis_contiki.pl

@@ -1,235 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-
-@duty_cycle[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
-	}
-}
-close fin;
-
-$log_file = "energy.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-    $total_time = @log[1] * 65536 + @log[2];
-    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-06-14 code/coflood/script/Indriya/diff_senders/30sender_chase_long_all2/delay_analysis_contiki.pl

@@ -1,235 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-
-@duty_cycle[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
-	}
-}
-close fin;
-
-$log_file = "energy.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-    $total_time = @log[1] * 65536 + @log[2];
-    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-06-14 code/coflood/script/Indriya/diff_senders/30sender_chase_long_all5/delay_analysis_contiki.pl

@@ -1,235 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-
-@duty_cycle[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
-	}
-}
-close fin;
-
-$log_file = "energy.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-    $total_time = @log[1] * 65536 + @log[2];
-    $radio_on = @log[3] * 65536 + @log[4];
[…]

### 2020-06-14 code/coflood/script/Indriya/topo.pl

@@ -1,136 +1,0 @@
-@node[150];
-@neighbor[22500];
-@link[22500];
-@rssi[22500];
-
-for ($i = 0; $i < 150; $i++) {
-    @node[$i] = 0;
-}
-
-for ($i = 0; $i < 22500; $i++) {
-    @neighbor[$i] = 0;
-    @link[$i] = 0;
-    @rssi[$i] = 0;
-}
-
-$topo_file = "topo2.dat";
-open fin, "<$topo_file" or "could not open file!\n";
-while (<fin>) {
-    chomp;
-    @log = split;
-
-    if (@log[0] eq "id") { next; }
-
-    $id = @log[0];
-    $src = @log[1];
-    $rssi = @log[2];
-
-    #printf "$id $src\n";
-
-    if ($rssi > 127) {
-        $rssi = $rssi - 256 - 45;
-    } else {
-        $rssi = $rssi - 45;
-    }
-
-    $index = $src * 150 + $id;
-    @neighbor[$index] = 1;
-    @link[$index] = @link[$index] + 1;
-    @rssi[$index] = @rssi[$index] + $rssi;
-}
-
-for ($i = 0; $i < 150; $i++) {
-    for ($j = 0; $j < 150; $j++) {
-        $index = $i * 150 + $j;
-        if (@neighbor[$index] == 1) {
-            $node[$i]++;
-        }
-    }
-}
-
-$total_node = 0;
-$max_neighbor = 0;
-$min_neighbor = 150;
-$avg_neighbor = 0;
-
-for ($i = 0; $i < 150; $i++) {
-    for ($j = 0; $j < 150; $j++) {
-        $index = $i * 150 + $j;
-        if (@neighbor[$index] == 1) {
-            @rssi[$index] = @rssi[$index] / @link[$index];
-            @link[$index] = @link[$index] / 10;
-            if (@link[$index] < 0.9) {
-                @neighbor[$index] = 0;
-                @node[$i]--;
-            } else {
-                printf "link[$i, $j]: quality @link[$index], rssi @rssi[$index]\n";
-            }
-        }
-    }
-    if (@node[$i] > 0) {
-        $total_node++;
-        if (@node[$i] < $min_neighbor) {
-            $min_neighbor = @node[$i];
-        }
-        if (@node[$i] > $max_neighbor) {
-            $max_neighbor = @node[$i];
-        }
-        $avg_neighbor += @node[$i];
[…]

### 2020-06-14 code/coflood/script/Lab testbed/energy_plot.pl

@@ -1,26 +1,0 @@
-{
-	$gnufile = "energy.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	#print gnuout "set style data histograms\n";
-    #print gnuout "set style histogram rowstacked\n";
-    #print gnuout "set boxwidth 0.6 relative\n";
-    #print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-	print gnuout "set output 'energy.eps'\n";
-	print gnuout "set xrange [0:6]\n";
-	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
-	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
-	print gnuout "set ylabel 'Radio Duty Cycle (%)'\n";
-	print gnuout "set yrange [0:14]\n";
-	print gnuout "set ytics 0,2,14\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-    print gnuout "set key top right\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
-	print gnuout "plot 'data.txt' using 1:2 with linespoints t 'Lab Testbed' lt 7 lw 4 ps 2 pt 4\n";
-	close gnuout;
-
-	system "gnuplot energy.plt";
-}

### 2020-06-14 code/coflood/script/control-topo/delay_plot.pl

@@ -1,24 +1,0 @@
-{
-	$gnufile = "delay.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	print gnuout "set style data histograms\n";
-    print gnuout "set style histogram rowstacked\n";
-    print gnuout "set boxwidth 0.6 relative\n";
-    print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-	print gnuout "set output 'delay.eps'\n";
-	#print gnuout "set xrange [0:100000]\n";
-	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
-	print gnuout "set ylabel 'Receiving Delay of R (ms)'\n";
-	#print gnuout "set yrange [0:1]\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-    print gnuout "set key top center\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22' box lw 2\n";
-	print gnuout "plot 'delay.txt' using 4 t 'Sleep' lc rgb 'grey' lw 4, '' using 3:xticlabels(1) t 'Tail' lc rgb 'black' lw 4\n";
-	close gnuout;
-
-	system "gnuplot delay.plt";
-}

### 2020-06-14 code/coflood/script/control-topo/local-testbed-control-topo/16senders5/delay_analysis.pl

@@ -1,220 +1,0 @@
-@delay[1650];
-@is_cal[1650];
-@rec[1650];
-@src[1650];
-@time_rec[1650];
-@src_delay[1650];
-@tail_time[1650];
-@hop[1650];
-
-@count[30];
-@avg_delay[30];
-@com_time[30];
-@last_id[30];
-@max_tail_time[30];
-@max_tail_id[30];
-@avg_tail_time[30];
-
-@all_tail[1650];
-$tail_count;
-
-@duty_cyle[51];
-@tmp_tail_time[51];
-
-for ($i = 0; $i < 30; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 51; $i++) {
-	for ($j = 0; $j < 30; $j++) {
-		@rec[$i*30+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      #if (@log[0] eq "Thread[Thread-1,5,main]") {
-      #	@log[0] = @log[1];
-      #	@log[1] = @log[2];
-      #	@log[2] = @log[3];
-      #}
-      if (@log[0] eq "Thread[Thread-1,5,main]radio") {
-        @log[0] = "radio";
-      }
-
-      if (@log[0] eq "radio") {
-      	$time_h = @log[1];
-      	$time_l = @log[2];
-        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
-      } elsif (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 30) {
-        	@rec[$i*30+$seq_no] = 1;
-        	@src[$i*30+$seq_no] = @log[2];
-        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
-
-            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 30) {
[…]

### 2020-06-14 code/coflood/script/control-topo/local-testbed-control-topo/20senders/delay_analysis.pl

@@ -1,210 +1,0 @@
-@delay[1650];
-@is_cal[1650];
-@rec[1650];
-@src[1650];
-@time_rec[1650];
-@src_delay[1650];
-@tail_time[1650];
-@hop[1650];
-
-@count[30];
-@avg_delay[30];
-@com_time[30];
-@last_id[30];
-@max_tail_time[30];
-@max_tail_id[30];
-@avg_tail_time[30];
-
-@all_tail[1650];
-$tail_count;
-
-@duty_cyle[51];
-@tmp_tail_time[51];
-
-for ($i = 0; $i < 30; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 51; $i++) {
-	for ($j = 0; $j < 30; $j++) {
-		@rec[$i*30+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "Thread[Thread-1,5,main]") {
-      	@log[0] = @log[1];
-      	@log[1] = @log[2];
-      	@log[2] = @log[3];
-      }
-
-      if (@log[0] eq "radio") {
-      	$time_h = @log[1];
-      	$time_l = @log[2];
-        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
-      } elsif (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 30) {
-        	@rec[$i*30+$seq_no] = 1;
-        	@src[$i*30+$seq_no] = @log[2];
-        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
-
-            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 30) {
-      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
[…]

### 2020-06-14 code/coflood/script/control-topo/local-testbed-control-topo/8senders/delay_analysis.pl

@@ -1,201 +1,0 @@
-@delay[1650];
-@is_cal[1650];
-@rec[1650];
-@src[1650];
-@time_rec[1650];
-@src_delay[1650];
-@tail_time[1650];
-@hop[1650];
-
-@count[30];
-@avg_delay[30];
-@com_time[30];
-@last_id[30];
-@max_tail_time[30];
-@max_tail_id[30];
-@avg_tail_time[30];
-
-@all_tail[1650];
-$tail_count;
-
-@duty_cyle[51];
-@tmp_tail_time[51];
-
-for ($i = 0; $i < 30; $i++) {
-	@delay[$i] = 0;
-	@time_rec[$i] = 0;
-	@is_cal[$i] = 1;
-	@rec[$i] = 1;
-}
-
-for ($i = 0; $i < 51; $i++) {
-	for ($j = 0; $j < 30; $j++) {
-		@rec[$i*30+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      if (@log[0] eq "Thread[Thread-1,5,main]") {
-      	@log[0] = @log[1];
-      	@log[1] = @log[2];
-      	@log[2] = @log[3];
-      }
-
-      if (@log[0] eq "radio") {
-      	$time_h = @log[1];
-      	$time_l = @log[2];
-        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
-      } elsif (@log[0] eq "delay") {
-        $seq_no = @log[1];
-        if ($seq_no < 30) {
-        	@rec[$i*30+$seq_no] = 1;
-        	@src[$i*30+$seq_no] = @log[2];
-        	@time_rec[$i*30+$seq_no] = @log[3] * 65535 + @log[4];
-        	@src_delay[$i*30+$seq_no] = @log[5] * 65535 + @log[6];
-
-            @tail_time[$i*30+$seq_no] = @time_rec[$i*30+$seq_no] - @tmp_tail_time[$i];
-        }
-      } elsif (@log[0] eq "flood") {
-      	$seq_no = @log[1];
-      	if ($seq_no < 30) {
-      		@time_rec[$seq_no] = @log[2] * 65535 + @log[3];
-      	}
-      } elsif (@log[0] eq "energy") {
[…]

### 2020-06-14 code/coflood/script/control-topo/local-testbed-control-topo/topo1/topo.pl

@@ -1,133 +1,0 @@
-@node[50];
-@neighbor[2500];
-@link[2500];
-@rssi[2500];
-
-for ($i = 0; $i < 50; $i++) {
-    @node[$i] = 0;
-}
-
-for ($i = 0; $i < 2500; $i++) {
-    @neighbor[$i] = 0;
-    @link[$i] = 0;
-    @rssi[$i] = 0;
-}
-
-for ($i = 0; $i < 50; $i++) {
-$topo_file = "$i.log";
-open fin, "<$topo_file" or "could not open file!\n";
-while (<fin>) {
-    chomp;
-    @log = split;
-
-    #if (@log[0] eq "id") { next; }
-
-    $id = @log[3];
-    $src = @log[1];
-    $rssi = @log[4];
-
-    #printf "$id $src\n";
-
-    if ($rssi > 127) {
-        $rssi = $rssi - 256 - 45;
-    } else {
-        $rssi = $rssi - 45;
-    }
-
-    $index = $src * 50 + $id;
-    @neighbor[$index] = 1;
-    @link[$index] = @link[$index] + 1;
-    @rssi[$index] = @rssi[$index] + $rssi;
-}
-}
-
-for ($i = 0; $i < 50; $i++) {
-    for ($j = 0; $j < 50; $j++) {
-        $index = $i * 50 + $j;
-        if (@neighbor[$index] == 1) {
-            $node[$i]++;
-        }
-    }
-}
-
-$total_node = 0;
-$max_neighbor = 0;
-$min_neighbor = 50;
-$avg_neighbor = 0;
-
-for ($i = 0; $i < 50; $i++) {
-    for ($j = 0; $j < 50; $j++) {
-        $index = $i * 50 + $j;
-        if (@neighbor[$index] == 1) {
-            @rssi[$index] = @rssi[$index] / @link[$index];
-            @link[$index] = @link[$index] / 10;
-            if (@link[$index] < 0.8) {
-                @neighbor[$index] = 0;
-                @node[$i]--;
-            } else {
-                printf "link[$i, $j]: quality @link[$index], rssi @rssi[$index]\n";
-            }
-        }
-    }
-    if (@node[$i] > 0) {
-        if (@node[$i] > $max_neighbor) {
-            $max_neighbor = @node[$i];
-        }
-        if (@node[$i] < $min_neighbor) {
-            $min_neighbor = @node[$i];
-        }
-        $avg_neighbor += @node[$i];
-        $total_node++;
[…]

### 2020-06-14 code/coflood/script/delay_plot.pl

@@ -1,34 +1,0 @@
-{
-	$gnufile = "delay.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-    #print gnuout "set tmargin 0\n";
-    #print gnuout "set bmargin 0\n";
-    #print gnuout "set lmargin 3\n";
-    #print gnuout "set rmargin 3\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	#print gnuout "set style data histograms\n";
-    #print gnuout "set style histogram rowstacked\n";
-    #print gnuout "set boxwidth 0.6 relative\n";
-    #print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-    #print gnuout "set multiplot layout 2,1\n";
-    print gnuout "set output 'delay.eps'\n";
-	print gnuout "set xrange [0:6]\n";
-    #print gnuout "unset xtics\n";
-    #print gnuout "unset ytics\n";
-    print gnuout "set key top right\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
-	print gnuout "set xtics ('10' 1, '20' 2, '30' 3, '40' 4, '50' 5)\n";
-	print gnuout "set xlabel 'Number of Concurrent Senders'\n";
-    print gnuout "set ylabel 'Completion Time (ms)'\n";
-    print gnuout "set yrange [1000:2200]\n";
-    print gnuout "set ytics 1000,200,2200\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-	print gnuout "plot 'lab_data.txt' using 1:3 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'indriya_data.txt' using 1:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
-    #print gnuout "unset multiplot\n";
-	close gnuout;
-
-	system "gnuplot delay.plt";
-}

### 2020-06-14 impl&eva/Indriya/LL-COFlood/1-thresh/exp1-fail/delay_analysis_contiki.pl

@@ -1,284 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-@tree_sender[6000];
-@long_link_sender[6000];
-@shortcut_sender[6000];
-@mpd[6000];
-@parent_etd[6000];
-@local_etd[6000];
-@delta_etd[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-@sender_number[40];
-@tree_sender_number[40];
-@long_link_sender_number[40];
-@shortcut_sender_number[40];
-
-@duty_cycle[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
-        @src_delay[$nodeid*40+$seq_no] = $tmp_time;
-
-        @parent_etd[$nodeid*40+$seq_no] = @log[7];
-        @local_etd[$nodeid*40+$seq_no] = @log[8];
[…]

### 2020-06-14 impl&eva/Indriya/LL-COFlood/1-thresh/exp2-fail/auto_tree.pl

@@ -1,119 +1,0 @@
-@node[150];
-@ebw[150];
-@path_ebw[150];
-@elder_id[150];
-@delay[150];
-@children_num[150];
-@is_sender[150];
-
-$total_node = 0;
-$total_sender = 0;
-
-for ($i = 0; $i < 150; $i++) {
-    @node[$i] = 0;
-}
-
-$s_counter = 0;
-
-$sender_file = "sender.dat";
-open fin, "<$sender_file" or "could not open file!\n";
-while (<fin>) {
-    chomp;
-    @log = split;
-
-    if (@log[0] eq "id") { next; }
-
-    $id = @log[0];
-    @node[$id] = 1;
-    @ebw[$id] = @log[1];
-    @path_ebw[$id] = @log[2];
-    @elder_id[$id] = @log[3];
-    @delay[$id] = @log[4];
-    @children_num[$id] = @log[5];
-    @is_sender[$id] = @log[6];
-
-    $total_node++;
-    if (@log[6] == 1) {
-        $total_sender++;
-    }
-
-#    if ( ($id % 6) == 0 ) {
-#        $s_counter++;
-#        printf "$id ";
-#    }
-}
-
-# printf "$s_counter\n";
-
-$root = 3;
-@hop[150];
-
-for ($i = 0; $i < 150; $i++) {
-    @hop[$i] = 0;
-}
-
-@hop[$root] = 1;
-$max_hop = 0;
-$change = 0;
-
-while ($change == 0) {
-    $change = 1;
-    for ($i = 0; $i < 150; $i++) {
-        if ( (@hop[$i] == 0) && (@hop[@elder_id[$i]] != 0) ) {
-            @hop[$i] = @hop[@elder_id[$i]] + 1;
-            $change = 0;
-        }
-    }
-}
-
-for ($i = 0; $i < 150; $i++) {
-    if (@hop[$i] > $max_hop) {
-        $max_hop = @hop[$i];
-    }
-}
-
-$connected_node = 0;
-
-for ($i = 1; $i <= $max_hop; $i++) {
-    printf "Hop $i:\n";
-    for ($j = 0; $j < 150; $j++) {
-        if (@hop[$j] == $i) {
-            $connected_node++;
[…]

### 2020-06-14 impl&eva/Indriya/LL-COFlood/1-thresh/exp2-fail/tree_topo.pl

@@ -1,84 +1,0 @@
-@node[150];
-@neighbor[2100];
-@link[2100];
-@sender[150];
-
-for ($i = 0; $i < 150; $i++) {
-    @node[$i] = 0;
-    @sender[$i] = 0;
-}
-
-for ($i = 0; $i < 2100; $i++) {
-    @neighbor[$i] = 0;
-    @link[$i] = 0;
-}
-
-$total_node = 0;
-
-$tree_file = "tree.dat";
-open fin, "<$tree_file" or "could not open file!\n";
-while (<fin>) {
-    chomp;
-    @log = split;
-
-    if (@log[0] eq "addr") { next; }
-
-    $id = @log[0];
-    @node[$id] = @log[1];
-
-    printf "Node $id has @node[$id] neighbors:\n";
-
-    $total_node++;
-
-    for ($i = 0; $i < @node[$id]; $i++) {
-        @neighbor[$id*14+$i] = @log[2+$i];
-        @link[$id*14+$i] = @log[16+$i];
-        printf "Neighbor @log[2+$i], Link Quality @log[16+$i]\n";
-    }
-}
-
-printf "Total Node: $total_node\n";
-
-$root = 3;
-@hop[150];
-
-for ($i = 0; $i < 150; $i++) {
-    @hop[$i] = 0;
-}
-
-@hop[$root] = 1;
-$max_hop = 0;
-$change = 0;
-
-while ($change == 0) {
-    $change = 1;
-    for ($i = 0; $i < 150; $i++) {
-        if (@hop[$i] != 0) {
-            for ($j = 0; $j < $node[$i]; $j++) {
-                $new_hop = @hop[$i] + 1;
-                if ( (@hop[@neighbor[$i*14+$j]] == 0) || ($new_hop < @hop[@neighbor[$i*14+$j]]) ) {
-                    @hop[@neighbor[$i*14+$j]] = $new_hop;
-                    @sender[@neighbor[$i*14+$j]] = $i;
-                    $change = 0;
-                }
-            }
-        }
-    }
-}
-
-for ($i = 0; $i < 150; $i++) {
-    if (@hop[$i] > $max_hop) {
-        $max_hop = @hop[$i];
-    }
-}
-
-for ($i = 1; $i <= $max_hop; $i++) {
-    printf "Hop $i:";
-    for ($j = 0; $j < 150; $j++) {
-        if (@hop[$j] == $i) {
-            printf " $j(@sender[$j])";
[…]

### 2020-06-14 impl&eva/Indriya/Tree-COFlood/exp2/delay_analysis_contiki.pl

@@ -1,296 +1,0 @@
-@delay[6000];
-@is_cal[6000];
-@rec[6000];
-@src[6000];
-@hop[6000];
-@time_rec[6000];
-@src_delay[6000];
-@tail[6000];
-@tree_sender[6000];
-@long_link_sender[6000];
-@shortcut_sender[6000];
-@mpd[6000];
-@parent_etd[6000];
-@local_etd[6000];
-@delta_etd[6000];
-
-@count[40];
-@avg_delay[40];
-@comp_time[40];
-@sender_number[40];
-@tree_sender_number[40];
-@long_link_sender_number[40];
-@shortcut_sender_number[40];
-
-@duty_cycle[150];
-@is_record[150];
-@base_radio_on_time[150];
-@base_time[150];
-
-for ($i = 0; $i < 150; $i++) {
-	@duty_cycle[$i] = 0;
-    @is_record[$i] = 0;
-}
-
-for ($i = 0; $i < 40; $i++) {
-	@delay[3*40+$i] = 0;
-	@time_rec[3*40+$i] = 0;
-	@is_cal[3*40+$i] = 1;
-	@rec[3*40+$i] = 1;
-	@hop[3*40+$i] = 0;
-}
-
-$log_file = "flood.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "seq_no") { next; }
-
-	$seq_no = @log[0];
-	if ($seq_no < 40) {
-		@rec[3*40+$seq_no] = 1;
-		$time_flood = @log[1] * 65536 + @log[2];
-		@time_rec[3*40+$seq_no] = $time_flood;
-	}
-}
-close fin;
-
-$log_file = "delay.log";
-open fin, "<$log_file" or "could not open file!\n";
-while (<fin>) {
-	chomp;
-	@log = split;
-
-	if (@log[0] eq "nodeid") { next; }
-
-	$nodeid = @log[0];
-	$seq_no = @log[1];
-	if ($seq_no < 40) {
-		@rec[$nodeid*40+$seq_no] = 1;
-        @src[$nodeid*40+$seq_no] = @log[2];
-        $tmp_time = @log[3] * 65536 + @log[4];
-        @time_rec[$nodeid*40+$seq_no] = $tmp_time;
-        $tmp_time = @log[5] * 65536 + @log[6];
[…]

### 2020-06-14 impl&eva/Lab/beacon number/5/coflood4/delay_analysis.pl

@@ -1,286 +1,0 @@
-@delay[1500];
-@is_cal[1500];
-@rec[1500];
-@src[1500];
-@time_rec[1500];
-@src_delay[1500];
-@tail_time[1500];
-@hop[1500];
-
-@count[30];
-@avg_delay[30];
-@com_time[30];
-@last_id[30];
-@max_tail_time[30];
-@max_tail_id[30];
-@avg_tail_time[30];
-
-@all_tail[1650];
-$tail_count;
-
-@duty_cyle[50];
-@tmp_tail_time[50];
-
-@ebw[50];
-@path_ebw[50];
-@elder_id[50];
-@delay[50];
-@children_num[50];
-@is_sender[50];
-
-$total_sender = 0;
-$root = 0;
-
-for ($i = 0; $i < 30; $i++) {
-	@delay[$root*30+$i] = 0;
-	@time_rec[$root*30+$i] = 0;
-	@is_cal[$root*30+$i] = 1;
-	@rec[$root*30+$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 30; $j++) {
-		@rec[$i*30+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      #if (@log[0] eq "Thread[Thread-1,5,main]") {
-      #	@log[0] = @log[1];
-      #	@log[1] = @log[2];
-      #	@log[2] = @log[3];
-      #}
-      if (@log[0] eq "Thread[Thread-1,5,main]tree") {
-        @log[0] = "tree";
-      }
-
-      if (@log[0] eq "tree") {
-        @ebw[$i] = @log[1];
-        @path_ebw[$i] = @log[2];
-        @elder_id[$i] = @log[3];
-        @delay[$i] = @log[4];
-        @children_number[$i] = @log[5];
-        @is_sender[$i] = @log[6];
-
-        if (@log[6] == 1) {
-          $total_sender++;
-        }
-      } elsif (@log[0] eq "radio") {
-      	$time_h = @log[1];
-      	$time_l = @log[2];
-        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
-      } elsif (@log[0] eq "delay") {
-        $seq_no = @log[1];
[…]

### 2020-06-14 impl&eva/Lab/ll-coflood/threshold-20_2/delay_analysis.pl

@@ -1,289 +1,0 @@
-@delay[1500];
-@is_cal[1500];
-@rec[1500];
-@src[1500];
-@time_rec[1500];
-@src_delay[1500];
-@tail_time[1500];
-@hop[1500];
-
-@count[30];
-@avg_delay[30];
-@com_time[30];
-@last_id[30];
-@max_tail_time[30];
-@max_tail_id[30];
-@avg_tail_time[30];
-
-@all_tail[1650];
-$tail_count;
-
-@duty_cyle[50];
-@tmp_tail_time[50];
-
-@ebw[50];
-@path_ebw[50];
-@elder_id[50];
-@delay[50];
-@children_num[50];
-@is_sender[50];
-
-$total_sender = 0;
-$root = 0;
-
-for ($i = 0; $i < 30; $i++) {
-	@delay[$root*30+$i] = 0;
-	@time_rec[$root*30+$i] = 0;
-	@is_cal[$root*30+$i] = 1;
-	@rec[$root*30+$i] = 1;
-}
-
-for ($i = 0; $i < 50; $i++) {
-	for ($j = 0; $j < 30; $j++) {
-		@rec[$i*30+$j] = 0;
-	}
-	$log_file = "$i.log";
-	open fin, "<$log_file" or die "could not open file!\n";
-	while (<fin>) {
-      chomp;
-      @log = split;
-      #if (@log[0] eq "Thread[Thread-1,5,main]") {
-      #	@log[0] = @log[1];
-      #	@log[1] = @log[2];
-      #	@log[2] = @log[3];
-      #}
-      if (@log[0] eq "Thread[Thread-1,5,main]tree") {
-        @log[0] = "tree";
-      }
-
-      if (@log[0] eq "tree") {
-        @ebw[$i] = @log[1];
-        @path_ebw[$i] = @log[2];
-        @elder_id[$i] = @log[3];
-        @delay[$i] = @log[4];
-        @children_number[$i] = @log[5];
-        @is_sender[$i] = @log[6];
-
-        if (@log[6] == 1) {
-          $total_sender++;
-        }
-      } elsif (@log[0] eq "radio") {
-      	$time_h = @log[1];
-      	$time_l = @log[2];
-        @tmp_tail_time[$i] = $time_h * 65536 + $time_l;
-      } elsif (@log[0] eq "delay") {
-        $seq_no = @log[1];
[…]

### 2020-06-14 impl&eva/beacon-number-result-plot.pl

@@ -1,34 +1,0 @@
-{
-	$gnufile = "beacon-number-result-plot.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-    #print gnuout "set tmargin 0\n";
-    #print gnuout "set bmargin 0\n";
-    #print gnuout "set lmargin 3\n";
-    #print gnuout "set rmargin 3\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	#print gnuout "set style data histograms\n";
-    #print gnuout "set style histogram rowstacked\n";
-    #print gnuout "set boxwidth 0.6 relative\n";
-    #print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-    #print gnuout "set multiplot layout 2,1\n";
-    print gnuout "set output 'beacon_number.eps'\n";
-	print gnuout "set xrange [0:6]\n";
-    #print gnuout "unset xtics\n";
-    #print gnuout "unset ytics\n";
-    print gnuout "set key top right\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
-	print gnuout "set xtics ('5' 1, '10' 2, '15' 3, '20' 4, '25' 5)\n";
-	print gnuout "set xlabel 'Number of Beacons'\n";
-    print gnuout "set ylabel 'Average Expected Broadcasts'\n";
-    print gnuout "set yrange [0:30]\n";
-    print gnuout "set ytics 0,5,30\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-    print gnuout "plot 'beacon-number-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'beacon-number-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
-    #print gnuout "unset multiplot\n";
-	close gnuout;
-
-	system "gnuplot beacon-number-result-plot.plt";
-}

### 2020-06-14 impl&eva/completion-time-result.pl

@@ -1,23 +1,0 @@
-{
-	$gnufile = "completion-time-result.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 24\n";
-	print gnuout "set output 'completion-time-result.eps'\n";
-	print gnuout "set style data histogram\n";
-	print gnuout "set style histogram cluster gap 2\n";
-	print gnuout "set style fill pattern 2 border\n";
-	print gnuout "set boxwidth 1\n";
-	print gnuout "set xlabel 'Testbed'\n";
-	print gnuout "set ylabel 'Completion Time (ms)'\n";
-	#print gnuout "set size ratio 0.25\n";
-	print gnuout "set yrange [0:2400]\n";
-	#print gnuout "set xrange [0:4]\n";
-	print gnuout "set ytics 0,400,2400\n";
-	#print gnuout "set boxwidth 0.25\n";
-	print gnuout "set key top left\n";
-	#print gnuout "set key bottom right\n";
-	print gnuout "plot 'completion-time-result.txt' using 2:xtic(1) ti col lt -1 lw 4, '' u 3 ti col lt -1 lw 4, '' u 4 ti col lt -1 lw 4, '' u 5 ti col lt -1 lw 4, '' u 6 ti col lt -1 lw 4";
-	close gnuout;
-	
-	system "gnuplot completion-time-result.plt";
-}

### 2020-06-14 impl&eva/duty-cycle-result.pl

@@ -1,23 +1,0 @@
-{
-	$gnufile = "duty-cycle-result.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 24\n";
-	print gnuout "set output 'duty-cycle-result.eps'\n";
-	print gnuout "set style data histogram\n";
-	print gnuout "set style histogram cluster gap 2\n";
-	print gnuout "set style fill pattern 2 border\n";
-	print gnuout "set boxwidth 1\n";
-	print gnuout "set xlabel 'Testbed'\n";
-	print gnuout "set ylabel 'Radio Duty Cycle (%)'\n";
-	#print gnuout "set size ratio 0.25\n";
-	print gnuout "set yrange [0:12]\n";
-	#print gnuout "set xrange [0:4]\n";
-	print gnuout "set ytics 0,3,12\n";
-	#print gnuout "set boxwidth 0.25\n";
-	print gnuout "set key top right\n";
-	#print gnuout "set key bottom right\n";
-	print gnuout "plot 'duty-cycle-result.txt' using 2:xtic(1) ti col lt -1 lw 4, '' u 3 ti col lt -1 lw 4, '' u 4 ti col lt -1 lw 4, '' u 5 ti col lt -1 lw 4, '' u 6 ti col lt -1 lw 4";
-	close gnuout;
-
-	system "gnuplot duty-cycle-result.plt";
-}

### 2020-06-14 impl&eva/ll-coflood-result-plot.pl

@@ -1,34 +1,0 @@
-{
-	$gnufile = "ll-coflood-result-plot.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-    #print gnuout "set tmargin 0\n";
-    #print gnuout "set bmargin 0\n";
-    #print gnuout "set lmargin 3\n";
-    #print gnuout "set rmargin 3\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	#print gnuout "set style data histograms\n";
-    #print gnuout "set style histogram rowstacked\n";
-    #print gnuout "set boxwidth 0.6 relative\n";
-    #print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-    #print gnuout "set multiplot layout 2,1\n";
-    print gnuout "set output 'll-coflood.eps'\n";
-	print gnuout "set xrange [0:6]\n";
-    #print gnuout "unset xtics\n";
-    #print gnuout "unset ytics\n";
-    print gnuout "set key top right\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
-	print gnuout "set xtics ('512' 1, '640' 2, '768' 3, '896' 4, '1024' 5)\n";
-	print gnuout "set xlabel 'Long Link Threshold (ms)'\n";
-    print gnuout "set ylabel 'Compeletion Time (ms)'\n";
-    print gnuout "set yrange [800:2400]\n";
-    print gnuout "set ytics 800,400,3000\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-    print gnuout "plot 'll-coflood-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'll-coflood-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
-    #print gnuout "unset multiplot\n";
-	close gnuout;
-
-	system "gnuplot ll-coflood-result-plot.plt";
-}

### 2020-06-14 impl&eva/sp-coflood-result-plot.pl

@@ -1,34 +1,0 @@
-{
-	$gnufile = "sp-coflood-result-plot.plt";
-	open gnuout, ">$gnufile" or die "could not open $gnufile!\n";
-    #print gnuout "set tmargin 0\n";
-    #print gnuout "set bmargin 0\n";
-    #print gnuout "set lmargin 3\n";
-    #print gnuout "set rmargin 3\n";
-	print gnuout "set term post eps color solid enh 'ArialMT' 26\n";
-	#print gnuout "set style data histograms\n";
-    #print gnuout "set style histogram rowstacked\n";
-    #print gnuout "set boxwidth 0.6 relative\n";
-    #print gnuout "set style fill pattern 2 border -1\n";
-    #print gnuout "set style line 2 lt 1 lw 7\n";
-    #print gnuout "set multiplot layout 2,1\n";
-    print gnuout "set output 'sp-coflood.eps'\n";
-	print gnuout "set xrange [0:8]\n";
-    #print gnuout "unset xtics\n";
-    #print gnuout "unset ytics\n";
-    print gnuout "set key top right\n";
-	print gnuout "set key samplen 2 spacing 2 font ',22'\n";
-	print gnuout "set xtics ('64' 1, '128' 2, '192' 3, '256' 4, '320' 5, '384' 6, '448' 7)\n";
-	print gnuout "set xlabel 'Shortcut Path Threshold (ms)'\n";
-    print gnuout "set ylabel 'Completion Time (ms)'\n";
-    print gnuout "set yrange [800:2400]\n";
-    print gnuout "set ytics 800,400,2400\n";
-    #print gnuout "set key off\n";
-	#print gnuout "set size ratio 0.25\n";
-	#print gnuout "set key bottom right\n";
-    print gnuout "plot 'sp-coflood-result.txt' using 2:4 with linespoints t 'Lab Testbed' lt 7 lw 4 lc rgb 'black' ps 2 pt 4, 'sp-coflood-result.txt' using 2:3 with linespoints t 'Indriya Testbed' lt 4 lw 4 lc rgb 'red' ps 2 pt 8\n";
-    #print gnuout "unset multiplot\n";
-	close gnuout;
-
-	system "gnuplot sp-coflood-result-plot.plt";
-}

### 2020-06-14 implementation.tex
removed irrelevant files

@@
      \subfigure[input from same environment]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1}
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
          \label{fig-train-single-1}
@@
      \subfigure[output of (a)]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2}
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
          \label{fig-train-single-2}
@@
      \subfigure[input from different environment]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5}
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
          \label{fig-train-single-3}
@@
      \subfigure[output of (c)]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4}
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
          \label{fig-train-single-4}
@@
      \subfigure[ground truth]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3}
+         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
          \label{fig-train-single-5}

### 2020-06-14 design.tex
removed irrelevant files
modified design

@@
 \label{sec-design}
-We designed an end-to-end network architecture consisting of several identical layers in which:
+As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together.
+The merged data will be stacked with the feature maps of each single image before we perform the next layer of convolution on them.
+Each convolutional layer uses the same set of parameters for all the images, so that the same set of features are extracted from the images, and thus can be merged.
+The merging layers consists of simple calculations extracting either the most significant, or the mutual features of the images, the former preserving interesting findings while the latter filters out credible features from the redundancy of the input.
+The network pipeline consists of alternate layers of convolution and merging, and after each merging layer, the reliable information accumulates and more complex features can be extracted with their support.
+Furthermore, we frequently insert the original input images in each level of our pipeline, creating an unevenness in depth and reducing network complexity, because we discovered that this process guides the model to be loyal to the inputs, generating more truthful results and less artifacts.
+
+The details of our network architecture is as follows:
 	Each input image (or each lane from the output of the previous layer) is assigned to its own lane and processed by several convolutional layers.
@@
  \centering
-    \includegraphics[width=0.375\textwidth]{./pic/system}
+    \includegraphics[width=0.5\textwidth]{./pic/design.pdf}
     \caption{Network Architecture of SRPeek.}

### 2020-06-14 conclusion.tex
conclusion

\section{Conclusion}
\label{sec-conclusion}
In this work we designed a holistic system for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency. We proved that this threat towards screen privacy is imminent and can cause damage while undetected. It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps. Although this system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user. One of these defenses is displaying a dynamic background behind the characters, with a small protion of patterns colored similar to the texts. The constant changes will confuse most of the multi-frame SR algorithms, as they are often designed based on the assumption that all input images are reflections of the same scene. Other defence methods include active scanning for suspicious individuals, encrypted keyboards at password entry phases, etc.

### 2020-06-21 design.tex
add eval

@@
-\section{System Design}
+\section{Design}
 \label{sec-design}
+
+\subsection{network design}
+
 As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together.
@@
 \end{figure}
+
+\subsection{system design}
+
+We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps: 
+\begin{enumerate}
+
+\item Input.
+Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
+Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
+This way information on the images will be more compact and easier to comprehend by neural networks.
+
+\item Alignment.
+The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
+The images are also spun to make the text horizontal in the process.
+The screen is cropped out and the rest of the image abandoned.
+
+\item Adjustment.
+The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
+The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
+
+\item Processing.
+As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo.
+For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see fig.~\ref{fig-patches}.
+After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
+The input is RGB colored, while the output, as we are not interested in color, is black and white.
+When all patches are processed, their outputs are merged together.
+The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
+In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.
+
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/patches.jpg}
+    \caption{Illustration of overlapping patches the network process photos.}
+    \label{fig-patches}
+\end{figure}
+
+\end{enumerate}
+
+These steps are repeatedly executed to enable the attacker to monitor the victim.
+The workflow of our system is shown in fig.~\ref{fig-workflow}.
+The training data for the network is also gathered in this way.
+Different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone with training images captured from it.
+When using smartphones with optical zoom, the images will shift slightly over time even if we keep them completely still, so the aligning phases are still needed.
+To reduce calculation and better align the images with the ground truth, we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-workflow}), but our system works perfectly without it.
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
+    \caption{Illustration of the workflow of our shoulder-surfing system.}
+    \label{fig-workflow}
+\end{figure}

### 2020-06-21 evaluation.tex
add eval

@@
+ 
 \section{Model Evaluation}
 We evaluate the ability of the network model, testing its performance in different training and testing conditions.
+We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments.
 \subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control}).
+We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control} and Fig.~\ref{fig-control}).
 Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
-On average the model achieves 96.5\% OCR accuracy.
-Considering the complexity of Chinese characters, and the assist of context when read by a human being, we believe this result proves that this model is highly functional when ignoring the environmental parameters.
+The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
+Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
+In the optical zoom group the accuracy of the model dropped drastically at 7m distance.
+Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.).
+It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.
 
@@
 
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
+    \caption{Performance in Controlled Environment(optical zoom lenses)}
+    \label{fig-control}
+\end{figure}
 \subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random}). The model achieves 93.5\% accuracy.
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random} and Fig.~\ref{fig-random}).
+The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
 
@@
 \end{tabular} 
-\caption{Performance in Random Environment}
+\caption{Performance in Random Environment(traditional lenses)}
 \label{table-random}
@@
 
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
+    \caption{Performance in Random Environment(optical zoom lenses)}
+    \label{fig-random}
+\end{figure}
 We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability.
-Also, the model performs better at closer distances, but this difference is trivial.
+Also, the model performs better at closer distances.
+As the model is trained initially on the 5m group data, it performs expecially well at this distance, while the accuracy at other distances experience certain levels of decrease.
+Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplist characters can escape from being flooded by noize.
 
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-The results are shown in Table~\ref{table-adapt}.
+The results are shown in Table~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
 
@@
 However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results.
-We used the relatively easys 'daytime 1.2m-distance direct' group of data for testing.
+We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing.
 The results are shown in Table~\ref{table-comp}.
@@
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
+As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range.
 We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model.

### 2020-06-21 implementation.tex
add eval

@@
 As a result of these observations, we have to collect images in varied environments.
-Our experiment consists of 2 smartphones at a distance between 1 and 2 meters, one for the attacker and one the victim.
+Our experiment consists of 2 smartphones, one for the attacker and one the victim.
+Their distance is between 1 and 2 meters for traditional lenses(for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming.
+Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation.
 An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos.

### 2020-06-25 abstract.tex
cl for abs and intro

--- 2020-05-21 abstract.tex
@@
 \label{abstract}
-We use smartphones everywhere and concerns have arisen about ‘shoulder surfing’, or the act of strangers peeking at our phone in public areas.
+We use smartphones everywhere and privacy concerns have arisen for ``shoulder surfing'', where strangers peek at our phone in public areas.
 This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms.
-We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR.
-We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment’s circumstances) and is robust in different environments.
-Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
+With the development of smartphones and super resolution (SR) technique, we believe that this threat is underestimated as a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms.
+To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing, including an unique multi-image SR neural network architecture designed for commercial smartphones.
+Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images.
+And it outperforms other known SR algorithms and fills the blank space of multi-image SR for shoulder surfing attack.
 \end{abstract}

### 2020-06-25 introduction.tex
removed irrelevant files
cl for abs and intro

--- 2020-05-17 introduction.tex
@@
 As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
-As a result, some concerns of privacy have arisen about nearby parties peeking at our screen, or ‘shoulder surfing’.
-Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet.
+As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing".
+Assuming that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes.
+And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages.
+% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm.
+The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games.
+Besides, specially designed equipment are not a necessity for the shoulder surfing attack.
 
-On the other hand, many works in this area are built on a threat model of an attacker observing with his/hers naked eye, as they assume that the attacker is not malicious and merely take several peeks out of curiosity.
-However, it is the rare but malicious and prepared attacker that can do the most harm, and leave aside special equipment, if we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim.
-For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
-Moreover, smartphone cameras have seen great improvement these years, and as a highly-accessible ‘extension of the eye’, it is possible that ‘shoulder surfers’ peek at others’ screen through their smartphone lenses to obtain critical information like passwords or private e-mails.
-What’s more, recent developments in the field of super resolution (SR) pose a greater threat to smartphone privacy.
-Attackers can take multiple snapshots of the victim’s screen and process them with multiple image super resolution algorithms in real time, making them able to see clearly while keeping a longer distance.
-However, most SR methods are designed for and trained on naturally taken images \cite{nasrollahi2020deep} \cite{lyn2020image}; few works have focused on reconstructing blurry snapshots taken at extreme distances, and a new architecture needs to be designed.
+The privacy threat however has been exacerbated with smartphones improved significantly these years.
+Given the commercial smartphone, the attacker can not only reduce suspicion by acquiring sensitive information from a long distance, but also record the information for propagating, rendering greater damage to the victim.
+For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
+Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second.
+And more images means more recorded information of the victim.
+To gain vital data stealthily from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be employed by the attacker, delivering a more threatening shoulder surfing model.
 
-To explore this rarely studied privacy threat of the attacker looking through a smartphone camera, we have developed a holistic system for shoulder surfing.
-The fictional attacker captures multiple images of the victim’s screen in burst mode from his smartphone, and enhances its resolution with our multi-frame super resolution neural network.
-The network is designed and trained for this purpose, targeting several blurry images taken in quick succession of a screen at a distance.
-As the information of interest is mostly displayed on screen in the form of text (e.g.
-passwords or e-mails), our network focuses on reconstructing text, specifically, Chinese characters, English letters, and numbers.
-The system is deployed on a smartphone for demonstration, capturing and processing images at real time.
-Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition of video clips.
+% In this present era where the leakage of a password and the disclosure of correspondence of public figures can cause great damage to the victim, we believe that it's imminent to recall attention on this new privacy threat and propose the corresponding standard of screen protection based on modern circumstances.
 
-\subsection{Difficulties}
-There are several difficulties unique to this SR application.
-The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses.
+To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}.
+All of these methods however require additional cost and/or effort \cite{Chun2019Keep} and are not widely deployed yet on the critical privacy stages (e.g., password entry) of most everyday apps.
+And none of existing work can deal with the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
+Given that the leakage of a password and the disclosure of correspondence of public figures can cause great damage to the victim, we believe that it's imminent to recall attention on this new privacy threat and propose the corresponding standard of screen protection based on modern circumstances.
+
+\vspace{1mm}
+\noindent
+\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial.
+And we achieve \textsf{SRPeek} by overcoming three key challenges.
+
+\begin{itemize}[leftmargin=*]
+  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses.
 Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
-
-Another difficulty unique to our task is the subject—mainly, Chinese characters.
+  \item \textbf{Processing with multi-frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time.
+However, we discover that there is no existing SR algorithm suitable for this scenario.
+On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}.
+Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances.
+On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images.
+The reason has two folds.
+First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
+Second, they lack an emphasis on the process of horizontal comparison(??) by relying heavily on the information extracted from each single image, resulting in an inefficient merge of information from multiple frames.
+  \item \textbf{Compatibility with various characters.} Another difficulty unique to our task is the subject—mainly, Chinese characters.
 Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g.
@@
 And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.
+\end{itemize}
 
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/zeros}
-    \caption{ Fig 1.
-4 photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera.
-Note how they exhibit different blurriness and display no consistency between neighboring frames.}
+	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
+    \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera.
+All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
 	\label{fig-zeros}
@@
 
-\subsection{Network Architecture} 
+\cl{The following part can correspond to challenges above.}
+In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones.
+To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN).
+With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone.
+Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring.
+As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios.
+Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.
+
+To deal with massive frames of blurred images with limited computational resources on smartphones, we design an unique merging layer and place it between convolutional layers in the SR pipeline.
+Thus information can be extracted first from input images independently and then merged together, serving as a reference for the following convolutions.
+
 As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach.
@@
 
-The details of our architecture will be discussed in section 4.
-
+% The details of our architecture will be discussed in section 4.
 This paper makes the following contributions:
-
 \begin{itemize}
-  \item	We propose SRPeek, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images.
+  \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images.
 This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
   \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera.
-To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shouler surfing senarios.
+To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
   \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.

### 2020-06-25 design.tex
modify tables

@@
 
-These steps are repeatedly executed to enable the attacker to monitor the victim.
+These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.
+At critical times requiring continuous monitoring so as not to miss transient display, e.g.
+password entering, the system can simply lengthen the input phase across that period and process the data afterwards.
 The workflow of our system is shown in fig.~\ref{fig-workflow}.
-The training data for the network is also gathered in this way.
-Different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone with training images captured from it.
-When using smartphones with optical zoom, the images will shift slightly over time even if we keep them completely still, so the aligning phases are still needed.
-To reduce calculation and better align the images with the ground truth, we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-workflow}), but our system works perfectly without it.
 \begin{figure}

### 2020-06-25 evaluation.tex
modify tables

@@
 \subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control} and Fig.~\ref{fig-control}).
+We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Fig~\ref{fig-control} and Fig.~\ref{fig-control2}).
 Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
@@
 
-\begin{table}  
-\begin{tabular}{c|c|c|c|c} 
-Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
-PSNR(db) & 14.64 & 12.39 & 10.728 & 10.259 \\ \hline
-OCR Accuracy(\%) & 100 & 97 & 95 & 94 \\
-\end{tabular} 
-\caption{Performance in Controlled Environment}
-\label{table-control}
-\end{table}
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
+    \caption{Performance in Controlled Environment(Traditional Lenses)}
+    \label{fig-control}
+\end{figure}
 
@@
     \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
-    \caption{Performance in Controlled Environment(optical zoom lenses)}
-    \label{fig-control}
+    \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
+    \label{fig-control2}
 \end{figure}
 \subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random} and Fig.~\ref{fig-random}).
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Fig.~\ref{fig-random} and Fig.~\ref{fig-random2}).
 The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
 
-\begin{table}  
-\begin{tabular}{c|c|c|c|c} 
-Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
-PSNR(db) & 13.32 & 11.17 & 9.744 & 9.558 \\ \hline
-OCR Accuracy(\%) & 100 & 97 & 92 & 85 \\
-\end{tabular} 
-\caption{Performance in Random Environment(traditional lenses)}
-\label{table-random}
-\end{table}
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
+    \caption{Performance in Random Environment(Traditional Lenses)}
+    \label{fig-random}
+\end{figure}
 
@@
     \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
-    \caption{Performance in Random Environment(optical zoom lenses)}
-    \label{fig-random}
+    \caption{Performance in Random Environment(Optical Zoom Lenses)}
+    \label{fig-random2}
 \end{figure}
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-The results are shown in Table~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
+The results are shown in Fig.~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
 
-\begin{table*}  
-\begin{tabular}{c|c|c|c|c} 
-Data & All Data & Night only & 1.2m distance only & Direct angle only \\ \hline
-PSNR(db) & 13.32 & 9.17 & 9.94 & 8.84\\ \hline
-OCR Accuracy & 100 & 73 & 80 & 52\\
-\end{tabular} 
-\caption{Adapting Ability}
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
+    \caption{Adapting Ability(Traditional Lenses)}
     \label{table-adapt}
-\end{table*}
+\end{figure}
 
@@
 We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing.
-The results are shown in Table~\ref{table-comp}.
+The results are shown in Fig.~\ref{table-comp}.
 
-\begin{table}  
-\begin{tabular}{c|c|c|c} 
-Model & Ours & SRCNN & VideoSR \\ \hline
-PSNR(db) & 13.32 & 7.690 & 8.403 \\ \hline
-OCR Accuracy(\%) & 100 & 10 & 23 \\
-\end{tabular} 
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
     \caption{Comparison with other architectures}
     \label{table-comp}
-\end{table}
+\end{figure}
 
@@
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-The results are shown in Table~\ref{table-accuracy}.
+The results are shown in Fig.~\ref{table-accuracy}.
 
-\begin{table*}  
-\begin{tabular}{c|c|c|c} 
-Scenario & Home & Transport & Theater\\ \hline
-Valid images & 20 & 20 & 20\\ \hline
-OCR Accuracy(\%) & 95 & 80 & 65\\ \hline
-Human Recognition Accuracy(raw data)(\%) & 5 & 0 & 0\\ \hline
-Human Recognition Accuracy(processed image)(\%) & 95 & 85 & 70 \\
-\end{tabular} 
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
     \caption{Accuracy in different real-life scenarios}
 	\label{table-accuracy}
-\end{table*}
+\end{figure}
 
@@
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Table~\ref{table-tremor}.
-\begin{table*}  
-\begin{tabular}{c|c|c|c|c} 
-Scenario &Stationary & Handheld camera & Handheld target & Handheld camera and target\\ \hline
-Valid images & 20 & 19 & 20 & 18\\ \hline
-OCR Accuracy(\%) & 95 & 85 & 80 & 80\\ \hline
-Human Recognition Accuracy(raw data)(\%) & 5 & 0 & 5 & 5\\ \hline
-Human Recognition Accuracy(processed image)(\%) & 95 & 85 & 80 & 85
-\end{tabular} 
+We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Fig.~\ref{table-tremor}.
+
+\begin{figure}
+ \centering
+    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
 \caption{Influence of hand tremors}
 \label{table-tremor}
-\end{table*}
+\end{figure}
 
@@
 For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric.
+In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible.
+Less photos will be avaliable for each character but decifering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same nerual network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
 The results are shown in Table~\ref{table-task}.
 
-\begin{table*}  
-\begin{tabular}{c|c|c|c|c} 
-Scenario & Read text & Type text & Enter PIN & Enter complex password\\ \hline
-Human Recognition Accuracy(raw image) & 5 & 0 & 0 & 0\\ \hline
-Accuracy & 100 & 100 & - & -\\ \hline
-Accuracy per character& - & - & 100 & 80\\ 
+\begin{table}[] 
+\centering
+\begin{tabular}{@{}lllll@{}}
+	\toprule
+Scenario & Read text & Type text & Enter PIN & Enter password\\ \midrule
+\begin{tabular}[c]{@{}l@{}}Human\\ Recognition\\ Accuracy\\(raw image)\end{tabular} & 5 & 0 & 0 & 0\\ \\
+Accuracy & 100 & 100 & - & -\\ \\
+\begin{tabular}[c]{@{}l@{}}Accuracy\\ per character\end{tabular}& - & - & 100 & 80\\ \bottomrule
 \end{tabular}
+
 \caption{Success rate in different tasks}
 \label{table-task}
-\end{table*}
+\end{table}
 
@@
 \subsection{Image Capturing Ability}
-Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in models 3~4 years old.
+Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old.
 Heavily used phones also performs less than ideal when capturing images in burst mode.

### 2020-06-25 implementation.tex
modify tables

@@
 We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset.
+Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model with a set of training images captured from it.
+When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours).
+There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data.
+%To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-training}), but our system works perfectly without it.
  Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.

### 2020-06-25 introduction.tex
cl for abs and intro

@@
 
+\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
 \vspace{1mm}
@@
 
-\cl{The following part can correspond to challenges above.}
+\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
 In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones.
@@
 
-% The details of our architecture will be discussed in section 4.
-This paper makes the following contributions:
-\begin{itemize}
+\cl{Evaluations can be summarized here (performance and comparison with existing works).}
+
+\vspace{1mm}
+\noindent
+\textbf{Summary of Evaluation Results.}
+
+\vspace{1mm}
+\noindent
+\textbf{Contributions.} This paper makes the following contributions:
+\begin{itemize}[leftmargin=*]
   \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images.

### 2020-06-28 design.tex
intro and design

@@
 
-As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together.
-The merged data will be stacked with the feature maps of each single image before we perform the next layer of convolution on them.
-Each convolutional layer uses the same set of parameters for all the images, so that the same set of features are extracted from the images, and thus can be merged.
-The merging layers consists of simple calculations extracting either the most significant, or the mutual features of the images, the former preserving interesting findings while the latter filters out credible features from the redundancy of the input.
-The network pipeline consists of alternate layers of convolution and merging, and after each merging layer, the reliable information accumulates and more complex features can be extracted with their support.
-Furthermore, we frequently insert the original input images in each level of our pipeline, creating an unevenness in depth and reducing network complexity, because we discovered that this process guides the model to be loyal to the inputs, generating more truthful results and less artifacts.
+The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output.
+The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer.
+As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.
+We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer.
+Till now the model is not different from traditional SR models:
 
-The details of our network architecture is as follows:
-	Each input image (or each lane from the output of the previous layer) is assigned to its own lane and processed by several convolutional layers.
-These layers share parameters across channels; however, each image is processed individually and do not interact with each other in this stage.
-Each channel will present a feature map of n channels.
-	The features extracted from all layers are merged broadwise with the following function:
+$$x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N$$
 
-    $${x'_k=\sum x_ie^{kx_i}/\sum e^{kx_i}}$$
+\cl{function above cannot express merging between x1 x2 ... xN?}
 
-Where k varies from -1 to 1.
-Apparently, k=0 leads to averaging, k=${+\infty}$ leads to a process similar to max operator and k=${-\infty}$ leads to min operator.
-This process merges information from every lane into one.
-The output is n channels for each value of k.
-	The original input images are accessed again.
-These images are also processed separately by several convolutional layers (sharing parameters across lanes) to extract features.
-The output of these images (m channels each) are stacked with the n channels from step 2) as m+n channels each lane.
-Some more convolution and an upscaling layer may follow, merging the data more thoroughly.
-These will be the input for the next layer.
-The above 3 steps are stacked as one layer.
-The functional network often consists of 5 to 8 layers to achieve 4x super resolution.
-The network ends with a merging process similar to the 2) step and a few more layers of convolution.
+Additionally, we introduce the initial images $x_i^{(0)}$ as an input for all the layers:
+
+$$x_i^{(l)} = H_l(x_i^{(l-1)},x_i^{(0)}), i=1,2,...N$$
+
+The last layer is exceptional, it yields a single image $y$ as output.
+
+Presently, in these layers nothing is done to raise the resolution of the images, so that the resolution of $x_i^{(0)}$ to $x_i^{(l-1)}$ and $y$ remains the same.
+To increase resolution we insert several 2$\times$ nearest upsampling layers $U$ evenly throughout the architecture between the layers:
+
+$$x_i^{(l)} \leftarrow U(x_i^{(l)}), x_i^{(0)} \leftarrow U(x_i^{(0)}), i=1,2,...N$$
+
+we upsample the input images $x_i^{(0)}$ simultaneously to keep the two inputs of the following layers $H_l(x_i^{(l-1)},x_i^{(0)})$ unanimous in resolution.
+For example, in a 4$\times$ SR network with five layers, we may insert 2 2$\times$ nearest upsampling layers behind the 2nd and 4th layer.
+
+Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$, distributed as follows:
+
+\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
+
+\begin{enumerate}
+\item The first input parameter of this layer, $x_i^{(l-1)}$, is passed through a convolution layer to extract features.
+Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):
+
+$$ a_i^{(l)} = Conv_{1l}(x_i^{(l-1)},Param_{1l}), i=1,2,...N$$
+
+\item The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps.
+Suppose the results of $Conv_{1l}$ consists of $R$ channels:
+
+$$ a_i^{(l)} = \{a_{i1}^{(l)},a_{i2}^{(l)},...,a_{iR}^{(l)}\}, i=1,2,...N$$
+
+The data in each channel will be merged separately in the merging layer. The output is $T\times R$ channels, denoted as $b_{tr}^{(l)}(t=1,2,...T, r=1,2,...R)$:
+
+$$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$
+$$ p=1,2,...P, q=1,2,...Q, t=1,2,...T, r=1,2,...R $$
+
+$P,Q$ denotes the height and width of the current images, (p,q) represent the pixel located at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process.
+Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator.
+We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min).
+these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.
+
+\item Separately, we pass the initial input images, $$x_i^{(0)}$$, or the second input parameter of $H_l$ into a convolutional layer$Conv_{2l}$, which is similar to $Conv_{1l}$ and process each image separately, also generating $N$ outputs with $R$ channels per output, denoted as $$c_ir^{(l)}, i=1,2,...N, r=1,2,...R$$:
+
+$$ c_i^{(l)} = Conv_{2l}(x_i^{(0)},Param_{2l}), i=1,2,...N$$
+
+$$ c_i^{(l)} = \{c_{i1}^{(l)},c_{i2}^{(l)},...,c_{iR}^{(l)}\}, i=1,2,...N$$
+
+\item The data from step (2) and (3) are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$.
+There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:
+
+$$ d_i^{(l)} = Conv_{3l}(Stack(c_i^{(l)},b^{(l)}),Param_{3l}), i=1,2,...N $$
+
+\item If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$.
+Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$.
+The merging layer is identical to the previous $Merge_l$, merging the N outputs $d_i^{(l)}$ into $T\times R$ channels $e_{tr}^{(l)}$, and a convolutional layer processes this $e_{tr}^{(l)}$ to generate a single channel of output $y$.
+
+$$ \{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\} = Merge`_{L}(\{d_i^{(L)},i\in (1,N)\})$$
+
+$$ y = Conv`_{L}(\{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\})$$
+
+\end{enumerate}
+
 The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.

### 2020-06-28 introduction.tex
intro and design

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{pic/intro.png}
+    \caption{Overview of the proposed shoulder surfing threat model.}
+	\label{fig-zeros}
+\end{figure}
 % introduce LPL asynchronous duty cycle media access
@@
 And we achieve \textsf{SRPeek} by overcoming three key challenges.
-
-\begin{itemize}[leftmargin=*]
-  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
-  \item \textbf{Processing with multi-frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time.
-However, we discover that there is no existing SR algorithm suitable for this scenario.
-On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}.
-Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances.
-On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images.
-The reason has two folds.
-First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
-Second, they lack an emphasis on the process of horizontal comparison(??) by relying heavily on the information extracted from each single image, resulting in an inefficient merge of information from multiple frames.
-  \item \textbf{Compatibility with various characters.} Another difficulty unique to our task is the subject—mainly, Chinese characters.
-Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g.
-faces and natural objects.
-In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings.
-And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.
-\end{itemize}
-
 \begin{figure}
@@
 \end{figure}
+\begin{itemize}[leftmargin=*]
+  \item \textbf{Blurriness of input images.} \cl{need revising.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses.
+Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
+\cl{However, such blurry input means less information, and a greater possibility of reconstructing the wrong character.
+In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.
+As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
+Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Fig.~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others.
+If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.}
+  \item \textbf{Processing with multiple frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time.
+However, we discover that there is no existing SR algorithm suitable for this scenario.
+On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}.
+Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 10 snapshots per second in burst mode, and these photos are taken from extreme distances.
+On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images.
+The reason has two folds.
+First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
+\cl{Second, most models rely heavily on the information extracted from each single image, however, the images in our application are so blurry and distorted that we cannot tell if, for example, it is one stroke or two parrallel strokes that is shown in these two darker pixels on this photo---unless we consult pixels at the same location in other input photos.
+The nature of our task requires this kind of consultation of pixels with same coordinates on different images throughout our construction process, and this mechanism needs to be designed into the network architecture.}
+  \item \textbf{Model complexity and variable input.} \cl{To achieve real-time monitoring, we need to perform our calculations locally on the smartphone, instead of sending the data to a server and process them remotely, because 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith.
+However, to get ideal results we need 10 to 20 images which will consume 1 to 2 seconds to capture, and this time period is the minimum interval between each output frame, with the processing phase working in parrallel.
+This way the time allowed for calculation is 1 to 2 seconds, with limited calculation power and RAM.
+In cases where the display on the target screen changes more frequently, less images will be avaliable for each scene, and the attacker requires more frequent feedback which means less time for each processing task.
+These not only require a smaller and simpler network model, but also a model that can function with variable input, efficiently utilizing the data from either 3 or 20 images and provide results to the best of its efforts.}
+  \item \textbf{Complexities of characters.} As the information of interest in shoulder surfing scenarios is mostly in the form of text (e.g., passwords or e-mails), we will focus on reconstructing text, specifically, Chinese characters, English letters, and numbers, in our system.\cl{declare this beforehand?} The task of reconstructing text, instead of scenary or objects, poses unique challenges.
+Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g.
+faces and natural objects.
+In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings.
+And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data.
+Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters.
+On the other hand, however, the focus on characters can also aid us.
+As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}
+\end{itemize}
 
@@
 In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones.
-To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN).
-With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone.
-Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring.
-As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios.
-Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.
-
-To deal with massive frames of blurred images with limited computational resources on smartphones, we design an unique merging layer and place it between convolutional layers in the SR pipeline.
-Thus information can be extracted first from input images independently and then merged together, serving as a reference for the following convolutions.
-
-As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach.
-Most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
-Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Figure~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others.
-If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.
-
-Considering the unique challenges of our application, we believe that if these images are processed iteratively, alternating between the following two processes, our network will be able to solve this ‘jigsaw puzzle’:
-
-\begin{enumerate}
-  \item Every single image of the input collection will be processed solely (by several layers of CNN), with access of the output of step (2) of the last iteration;
-  \item The processed results will be merged (with weighted averaging methods) and distributed to each photo for the next iteration.
-\end{enumerate}
-
-This architecture is beneficial to our task.
-On one hand, the deep learning part is assigned to each single image, reducing computational complexity and parameter growth, while receiving a global view of all the images, renewed at each layer, thanks to the merging process; on the other hand, information can be shared horizontally with weighted averaging methods, meaning no consideration of sequential order and no reliance of consistency between neighboring frames.
-Thus, this architecture solves the dilemma mentioned above, and proves perfectly functional in our application.
+Deployed on a smartphone, this system will take snapshots of the target screen in burst mode of the attacker's screen, which are aligned, cropped, and then processed by our multi-frame SR neural network to generate a high-res image of the victim's screen.
+The core of this system, the nerual network, is specifically designed and trained for this task, aimed to counter the four challenges mentioned above.
+The outline of this network is as follows:
+\begin{itemize}[leftmargin=*]
+  \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
+The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image.
+Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
+  \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images.
+As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently.
+This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution.
+In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer.
+In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase.
+At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
+  \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
+This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters.
+In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps.
+This process functions with any number of input images.
+As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input.
+On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Fig.~\ref{fig-zeros}.
+  \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results.
+The frequent introduction of input images is designed to mitigate this challenge.
+Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images.
+We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data.
+The loss functions in training is also redesigned.
+The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
+Our solution is putting a weight on each pixel before applying weighted MSE.
+Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights.
+This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests.
+\end{itemize}
 

### 2020-06-28 abstract.tex
abs+parial intro

@@
 \label{abstract}
-We use smartphones everywhere and privacy concerns have arisen for ``shoulder surfing'', where strangers peek at our phone in public areas.
-This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technique, we believe that this threat is underestimated as a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms.
-To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing, including an unique multi-image SR neural network architecture designed for commercial smartphones.
-Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images.
-And it outperforms other known SR algorithms and fills the blank space of multi-image SR for shoulder surfing attack.
+We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas.
+To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye.
+With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms, rendering the underestimated threat model.
+To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including an unique deep neural network (DNN) architecture for multi-image SR.
+Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the multiple types of contents off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images.
+And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
 \end{abstract}

### 2020-06-28 design.tex
abs+parial intro

@@
-\section{Design}
+\section{System Design}
 \label{sec-design}
@@
 \subsection{network design}
-
 The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output.
@@
 
-The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.
+The full structure of a 3 layer network is shown in Figure~\ref{fig-system}.
 
@@
 As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo.
-For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see fig.~\ref{fig-patches}.
+For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see Figure~\ref{fig-patches}.
 After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
@@
 password entering, the system can simply lengthen the input phase across that period and process the data afterwards.
-The workflow of our system is shown in fig.~\ref{fig-workflow}.
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
-    \caption{Illustration of the workflow of our shoulder-surfing system.}
-    \label{fig-workflow}
-\end{figure}
+The workflow of our system is shown in Figure~\ref{fig-workflow}.

### 2020-06-28 evaluation.tex
abs+parial intro

@@
 \subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Fig~\ref{fig-control} and Fig.~\ref{fig-control2}).
+We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control} and Figure~\ref{fig-control2}).
 Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
@@
 \subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Fig.~\ref{fig-random} and Fig.~\ref{fig-random2}).
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random2}).
 The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-The results are shown in Fig.~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
+The results are shown in Figure~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
 
@@
 We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing.
-The results are shown in Fig.~\ref{table-comp}.
+The results are shown in Figure~\ref{table-comp}.
 
@@
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-The results are shown in Fig.~\ref{table-accuracy}.
+The results are shown in Figure~\ref{table-accuracy}.
 
@@
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Fig.~\ref{table-tremor}.
+We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Figure~\ref{table-tremor}.
 
@@
 We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.
-\section{Limitations}
-\subsection{Image Capturing Ability}
-Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old.
-Heavily used phones also performs less than ideal when capturing images in burst mode.
-Also, when capturing images the user need to hold their phone as still as possible to avoid motion blur and assist image alignment.
-The user also has to keep a sharp focus on the target phone.
-\subsection{Processing Ability}
-To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time.
-As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
-\subsection{Motion and Tremors}
-In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often.
-However some users may tilt their phones during interactions—especially when typing with one hand.
-Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.

### 2020-06-28 implementation.tex
abs+parial intro

@@
 There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data.
-%To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-training}), but our system works perfectly without it.
- Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.
-However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
+%To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
+ Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.
+However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
  \begin{figure}

### 2020-06-28 introduction.tex
abs+parial intro

--- 2020-06-25 introduction.tex
@@
 As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing".
-Assuming that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes.
+Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes.
 And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages.
@@
 
-The privacy threat however has been exacerbated with smartphones improved significantly these years.
-Given the commercial smartphone, the attacker can not only reduce suspicion by acquiring sensitive information from a long distance, but also record the information for propagating, rendering greater damage to the victim.
-For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
+The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years.
+Given the commercial smartphone, the attacker cannot acquire sensitive information from a long distance to reduce suspicion, but also recognize the information accurately for propagating, making existing defense work ineffective.
+For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
+Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
 Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second.
-And more images means more recorded information of the victim.
-To gain vital data stealthily from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be employed by the attacker, delivering a more threatening shoulder surfing model.
+And more images mean more recorded information of the victim.
+To gain vital data stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.
 
@@
 To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}.
-All of these methods however require additional cost and/or effort \cite{Chun2019Keep} and are not widely deployed yet on the critical privacy stages (e.g., password entry) of most everyday apps.
-And none of existing work can deal with the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
-Given that the leakage of a password and the disclosure of correspondence of public figures can cause great damage to the victim, we believe that it's imminent to recall attention on this new privacy threat and propose the corresponding standard of screen protection based on modern circumstances.
+All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios.
+Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios.
+Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
 
-\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
-\vspace{1mm}
-\noindent
-\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial.
-And we achieve \textsf{SRPeek} by overcoming three key challenges.
-
-\begin{itemize}[leftmargin=*]
-  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
-  \item \textbf{Processing with multi-frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time.
-However, we discover that there is no existing SR algorithm suitable for this scenario.
-On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}.
-Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances.
-On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images.
-The reason has two folds.
-First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
-Second, they lack an emphasis on the process of horizontal comparison(??) by relying heavily on the information extracted from each single image, resulting in an inefficient merge of information from multiple frames.
-  \item \textbf{Compatibility with various characters.} Another difficulty unique to our task is the subject—mainly, Chinese characters.
-Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g.
-faces and natural objects.
-In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings.
-And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.
-\end{itemize}
+In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm.
+Deployed on commercial smartphones, it can take multiple snapshots of the target screen continuously and stealthily from a long range, illustrated in Figure~\ref{illustration_of_system}.
+Benefited from our multi-frame SR neural network, those blurred images can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim.
 
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
-    \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera.
-All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
-	\label{fig-zeros}
+	\includegraphics[width=0.48\textwidth]{pic/intro.png}
+    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.
+\cl{supplement elements for long range, blurred input and the recognized results.}}
+	\label{illustration_of_system}
 \end{figure}
 
-\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
-In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones.
-To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN).
-With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone.
-Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring.
-As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios.
-Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.
+\vspace{1mm}
+\noindent
+\textbf{Challenges.} Creating a high-resolution shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time.
+And we achieve \textsf{SRPeek} by overcoming four key challenges.
 
-To deal with massive frames of blurred images with limited computational resources on smartphones, we design an unique merging layer and place it between convolutional layers in the SR pipeline.
-Thus information can be extracted first from input images independently and then merged together, serving as a reference for the following convolutions.
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
+%     \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera.
+All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
+% 	\label{illustration_of_system}
+% \end{figure}
 
-As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach.
-Most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
-Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Figure~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others.
-If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.
-
-Considering the unique challenges of our application, we believe that if these images are processed iteratively, alternating between the following two processes, our network will be able to solve this ‘jigsaw puzzle’:
-
-\begin{enumerate}
-  \item Every single image of the input collection will be processed solely (by several layers of CNN), with access of the output of step (2) of the last iteration;
-  \item The processed results will be merged (with weighted averaging methods) and distributed to each photo for the next iteration.
-\end{enumerate}
-
-This architecture is beneficial to our task.
-On one hand, the deep learning part is assigned to each single image, reducing computational complexity and parameter growth, while receiving a global view of all the images, renewed at each layer, thanks to the merging process; on the other hand, information can be shared horizontally with weighted averaging methods, meaning no consideration of sequential order and no reliance of consistency between neighboring frames.
-Thus, this architecture solves the dilemma mentioned above, and proves perfectly functional in our application.
+\begin{itemize}[leftmargin=*]
+  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without much room for focusing.
+It can be further exacerbated by straining the magnification of the smartphone lenses.
+Unlike most SR applications and datasets working with ``normally" captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction" than ``interpolation"".
+Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
+  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.
+As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
+  On one hand, each photo is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel.
+Thus they cannot be processed as a video clip due to the lacking consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}; on the other hand, because of the low concentration of information, blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information.
+  % and the only chance of recovering the ground truth is to compare each photo against others. 
+  Few useful information can be extracted separately and merged directly to produce satisfactory results if processed by common procedures to enhance the resolution of a series of snapshots\cl{citation?}.
+  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents.
+However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred photos as input.
+Since smartphones can capture 10 snapshots per second in burst mode.
+Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cl{citation?}.
+The reason has two folds.
+First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
+Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process.
+Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this photo.
+  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on comercial smartphones in a real-time manner rather than remotely in cloud server.
+Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith.
+Given the required 10 to 20 images to process for ideal contennt recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM.
+In cases where the display on the target screen changes more frequently, less images and processing time are avaliable for each scene.
+Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dyanmic inputs efficiently, either 3 or 20 images.
+  \item \textbf{Complexities of characters.} To make our threat model more applicable for real-life scenarios (e.g., passwords or e-mails), we aim for reconstructing multi-type texts, including Chinese characters, English letters, and numbers.
+And it poses unique challenges compared with scene or object reconstruction.
+Composed of multiple strokes, characters are distributed discretely in image space, not known to other entities, e.g.
+faces and natural objects.
+In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings.
+And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data.
+Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters.
+On the other hand, however, the focus on characters can also aid us.
+As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}
+\end{itemize}
 

### 2020-06-28 limitation_and_discussion.tex
abs+parial intro

\section{Limitations}
\subsection{Image Capturing Ability}
Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old. Heavily used phones also performs less than ideal when capturing images in burst mode. Also, when capturing images the user need to hold their phone as still as possible to avoid motion blur and assist image alignment. The user also has to keep a sharp focus on the target phone.
\subsection{Processing Ability}
To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time. As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
\subsection{Motion and Tremors}
In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often. However some users may tilt their phones during interactions—especially when typing with one hand. Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.

### 2020-06-28 system_overview.tex
abs+parial intro

\section{System Overview}
\label{sec-system-overview} 
\begin{figure}
    \centering
       \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
       \caption{Illustration of the workflow of our shoulder-surfing system.}
       \label{fig-workflow}
\end{figure}

The outline of this network is as follows:
\begin{itemize}[leftmargin=*]
  \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers. The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image. Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
  \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images. As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently. This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution. In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer. In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
  \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power. This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters. In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps. This process functions with any number of input images. As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input. On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
  \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images. We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data. The loss functions in training is also redesigned. The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels. Our solution is putting a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
\end{itemize}

### 2020-06-28 threat_model.tex
abs+parial intro

@@
 \label{sec-threat-model} 
-The objective of the attacker is to acquire the information on the smartphone screen of the victim, reading the numbers and English/Chinese characters on screen, with the help of his smartphone’s camera equipped with the SR network we designed.
+Given the smartphone’s camera equipped with the SR network, the objective of the attacker is to acquire the multi-type of contents accurately on the smartphone screen of the victim from a long range, covering numbers, English and Chinese characters on screen.
 To reduce suspicion, the attacker will probably position himself at about 1.5 meters from the target screen, at an angle within 30 degrees.
-At this distance few people will be on guard of strangers even when viewing sensitive data or entering passwords.
+Since few people can be on guard of strangers at this distance even when viewing sensitive data or entering passwords.
 The attacker may raise his phone (one of the latest models with powerful lenses and computational abilities), pretending to be interacting with it, while pointing his camera at the victim.

### 2020-06-29 introduction.tex
revision by cl

@@
 Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
-
-In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm.
-Deployed on commercial smartphones, it can take multiple snapshots of the target screen continuously and stealthily from a long range, illustrated in Figure~\ref{illustration_of_system}.
-Benefited from our multi-frame SR neural network, those blurred images can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim.
-
 \begin{figure}
@@
 \end{figure}
+
+\vspace{1mm}
+\noindent
+\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
+Assuming the victim is scanning messages in life, the attacker can raise his commercial smartphone with powerful lenses and our SR network to the victim stealthily, even from a long range (e.g., 1.5 meters far away within the visual angle of 30$^{\circ}$).
+As the camera zooms in, he can take 20 to 30 snapshots continuously in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames.
+This process can take about 2 seconds with the consistent content and position for the screen of the victim.
+Benefited from our multi-frame SR neural network, those blurred snapshots can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim in real time.
+Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters.
+The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.
 
@@
 Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this photo.
-  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on comercial smartphones in a real-time manner rather than remotely in cloud server.
-Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith.
-Given the required 10 to 20 images to process for ideal contennt recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM.
-In cases where the display on the target screen changes more frequently, less images and processing time are avaliable for each scene.
-Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dyanmic inputs efficiently, either 3 or 20 images.
-  \item \textbf{Complexities of characters.} To make our threat model more applicable for real-life scenarios (e.g., passwords or e-mails), we aim for reconstructing multi-type texts, including Chinese characters, English letters, and numbers.
-And it poses unique challenges compared with scene or object reconstruction.
-Composed of multiple strokes, characters are distributed discretely in image space, not known to other entities, e.g.
-faces and natural objects.
-In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings.
-And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data.
-Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters.
-On the other hand, however, the focus on characters can also aid us.
-As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}
+  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server.
+Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwidth.
+Given the required 10 to 20 images to process for ideal content recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM.
+In cases where the display on the target screen changes more frequently, less images and processing time are available for each scene.
+Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 images.
+  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct multi-type texts, including Chinese characters, English letters, and numbers.
+Composed of multiple strokes, characters are distributed discretely in the pixel-wise image and different with other entities (e.g., faces and natural objects), rendering unique challenges.
+In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings.
+Unlike most SR applications working on similarity between their output and the ground truth, our network architecture and training process must be engineered to recover readable contents.
+Another challenge is the imbalanced element for words.
+Since we know certain stroke or alphabet of Chinese and English characters can occur more frequently, results in lower prediction accuracy over the less common, unconventionality shaped characters.
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*]
-  \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images.
-This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
-  \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera.
+  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range.
 To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
-  \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.
+  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots.
+It can be further extended to other text-recognition applications on commercial smartphones.
+  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
 \end{itemize}
-
 % describe the organization of the paper
 The rest of the paper is organized as follows.
-Section 2 describes the threat model of our  carefully studies the performance of state-of-the-art concurrent flooding.
-The detailed design of COFlood protocol is shown in Section~\ref{sec-design}.
-We show the implementation details and evaluation results in Section~\ref{sec-implementation-and-evaluation}.
-The related work is introduced in Section~\ref{sec-related-work}.
-Finally, we conclude our work in Section~\ref{sec-conclusion}.
+Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing attack.
+We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}, respectively.
+We further wrap up this paper by presenting the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}.
+And the conclusion is show in Section~\ref{sec-conclusion}.

### 2020-06-29 related_work.tex
revision by cl

@@
 \label{sec-related-work}
+\begin{table*}[t]
+    \caption{A comparison of state-of-the-art works on Wi-Fi Imaging.}
+    \vspace{2mm}
+    \begin{center}
+    \begin{tabular}{ccccc}
+    \hline
+     Reference  & Principle &  RF Platform & Method & \#(Tx,Rx) Ant$^{\mathrm{a}}$\\ 
+    \hline
+    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
+    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
+    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
+    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
+    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
+    \hline
+    \textbf{\textsf{WiHolo-2D}} & Intensity \& Polarization & COTS Wi-Fi & 2D IFFT \& GAN &(1,6) \\
+    \hline
+    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning. $^{\mathrm{b}} $The receive beam sweeps from $+90^{\circ}$ to $-90^{\circ}$ for one}\\
+    \multicolumn{5}{l}{transmit beam angle between $+90^{\circ}$ and $-90^{\circ}$. $^{\mathrm{c}}$The RX drone measures the RSSI every 2 cm for the 3m$\times$3m area.}\\
+    \multicolumn{5}{l}{$^{\mathrm{d}}$Achieve a resolution of 4.0 cm $\times$ 7.2 cm for the 2m$\times$3m area.}\\
+    \end{tabular}
+    \label{comparison}
+    \end{center}
+\end{table*}
+
+\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
 \subsection{Shoulder Surfing}

### 2020-06-29 system_overview.tex
revision by cl

@@
 
-The outline of this network is as follows:
+To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
+\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
 \begin{itemize}[leftmargin=*]

### 2020-06-30 conclusion.tex
修改

@@
+\section{Discussion}
+\label{sec-discussion}
+Although our shoulder surfing system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
+
+\vspace{1mm}
+\noindent
+\textbf{Dynamic background.} Most multi-frame SR algorithms are designed based on the assumption that all input images are reflections of the same scene, and ours is not an exception.
+By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influencial elements cannot be easily removed.
+These dots do not need to be distinct or colored same as the the texts, as multi-frame SR algorithms function with tiny,pixel level differences between frames, making them especially sensitive to microscopic changes.
+
+\textbf{Active scanning.} There are several works providing an active countermeasure against shoulder surfing threats with the naked eye.
+With front-facing cameras and face detection algorithms, the smartphone can constantly scan the surrounding passers-by and detect their gaze direction, and give a warning to the user when that gaze points at the screen.
+However, to the extent of our knowledge none of these works have included cameras into their detection scope, but we believe it's practical to implement such features.
+
+\textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network.
+These methods fools the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
+Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remains to be implemented in our future work.
+
 \section{Conclusion}
 \label{sec-conclusion}
-In this work we designed a holistic system for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
-We proved that this threat towards screen privacy is imminent and can cause damage while undetected.
+In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
+We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection.
 It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps.
-Although this system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
-One of these defenses is displaying a dynamic background behind the characters, with a small protion of patterns colored similar to the texts.
-The constant changes will confuse most of the multi-frame SR algorithms, as they are often designed based on the assumption that all input images are reflections of the same scene.
-Other defence methods include active scanning for suspicious individuals, encrypted keyboards at password entry phases, etc.
+
+The core of SRPeek is a specially designed multi-frame SR network.
+With its innovative architecture this network outperforms other algorithms of the same field in our application.
+The design ideology enables this network to process higher levels of data integration ability while keeping a low calculation profile, and we believe the elements of this design can be used in other applications with large amounts of data, such as natural language processing or anomaly detection.
+Our model can also be used in OCR tasks when multiple images are avaliable, functioning as a preprocessor to improve the quality of the images and increase accuracy.

### 2020-06-30 design.tex
修改

@@
 
-Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$, distributed as follows:
+Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$.
 
@@
 
-\begin{enumerate}
-\item The first input parameter of this layer, $x_i^{(l-1)}$, is passed through a convolution layer to extract features.
+\vspace{1mm}
+\noindent
+\textbf{Conv1.} The first convolutional layer, $Conv1$, accepts the layer's first input parameter $x_i^{(l-1)}$ as input.
 Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):
@@
 
-\item The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps.
+\vspace{1mm}
+\noindent
+\textbf{Merge.} The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps.
 Suppose the results of $Conv_{1l}$ consists of $R$ channels:
@@
 $$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$
-$$ p=1,2,...P, q=1,2,...Q, t=1,2,...T, r=1,2,...R $$
 
-$P,Q$ denotes the height and width of the current images, (p,q) represent the pixel located at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process.
+where (p,q) represent the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process.
 Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator.
@@
 
-\item Separately, we pass the initial input images, $$x_i^{(0)}$$, or the second input parameter of $H_l$ into a convolutional layer$Conv_{2l}$, which is similar to $Conv_{1l}$ and process each image separately, also generating $N$ outputs with $R$ channels per output, denoted as $$c_ir^{(l)}, i=1,2,...N, r=1,2,...R$$:
+\vspace{1mm}
+\noindent
+\textbf{Conv2.} $Conv2$ is a replica of $Conv1$, processing the layer's second input parameter $x_i^{(0)}$, also generating $N$ outputs with $R$ channels per output, denoted as $c_ir^{(l)}, i=1,2,...N, r=1,2,...R$:
 
@@
 
-\item The data from step (2) and (3) are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$.
+\vspace{1mm}
+\noindent
+\textbf{Conv3.}The data from $Merge$ and $Conv2$ are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$.
 There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:
@@
 
-\item If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$.
+\vspace{1mm}
+\noindent
+\textbf{Output.}If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$.
 Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$.
@@
 
-$$ \{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\} = Merge`_{L}(\{d_i^{(L)},i\in (1,N)\})$$
+$$ \{e_{tr}^{(L)},t\le T,r\le R\} = Merge'_{L}(\{d_i^{(L)},i\le N\})$$
 
-$$ y = Conv`_{L}(\{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\})$$
-
-\end{enumerate}
+$$ y = Conv'_{L}(\{e_{tr}^{(L)},t\le T,r\le R\} )$$
 
@@
 We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
-\begin{enumerate}
 
-\item Input.
-Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
+\vspace{1mm}
+\noindent
+\textbf{Input.} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
 Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
@@
 
-\item Alignment.
-The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+\vspace{1mm}
+\noindent
+\textbf{Alignment.} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 
-\item Adjustment.
-The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
+\vspace{1mm}
+\noindent
+\textbf{Adjustment.} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
 The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
 
-\item Processing.
-As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo.
-For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see Figure~\ref{fig-patches}.
+\vspace{1mm}
+\noindent
+\textbf{Processing.} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
 After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
@@
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/patches.jpg}
-    \caption{Illustration of overlapping patches the network process photos.}
-    \label{fig-patches}
-\end{figure}
-
-\end{enumerate}
-
 These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.

### 2020-06-30 implementation.tex
revision by cl
修改

@@
 
-\subsection{Experiment Setting}
+\subsection{Data Collection}
 \label{sec-experiment-setting}
+
 In our experiment, we are forced to collect the training dataset on our own instead of using public datasets.
@@
 However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke.
-Noise and details are not the main issue here, as we need only the facts, deeming it a victory if the neural network returns a noised, wrapped, but readable image.
 These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets.
@@
 The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network.
-We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset.
-Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model with a set of training images captured from it.
+We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them.
+Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model.
 When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours).
@@
 %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
+
 Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.
@@
 
+\subsection{Experiment Setting}
 As a result of these observations, we have to collect images in varied environments.
@@
 As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters.
+
 As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker.
@@
 We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter.
-The position of the phones is also a crucial factor in this parameter, and we avoid having the sunlight directly shone on the camera of the attacker or the screen of the victim, as it is extremely difficult to see anything in these extreme circumstances.
-We also draw a box around the characters on the victim's screen for alignment purposes, as although in production our system can detect the edges of the screen for alignment, this method provides more accurate results and possibly accelerates training.
-After collecting the images, we crop them along these boxes, retaining only the characters.
-In the training phase we randomly crop out squares of 9x9 pixels at the corresponding position on the training dataset and ground truth, and feed them into the neural network.
+The position of the phones is also a crucial factor in this parameter, and we avoid extreme settings, e.g.
+having the sunlight directly shining on the screen.
 We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels).

### 2020-06-30 introduction.tex
修改

--- 2020-06-28 introduction.tex
@@
 
-\cl{Evaluations can be summarized here (performance and comparison with existing works).}
-
 \vspace{1mm}
@@
 \textbf{Summary of Evaluation Results.}
+Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings.
+The system is able to capture photos and produce high-res images constantly with about 2 seconds interval.
+Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.
 

### 2020-06-30 related_work.tex
修改

--- 2020-05-17 related_work.tex
@@
 multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip.
-Although they picture the same scene and are mostly identical to each other, those low-res pictures can be viewed as replicas of a certain high-res scene with random pixels blurred and removed, and multiple image super-resolution algorithms reconstruct the high-res scene by merging these incomplete information sources, often exhibiting better performance than single image super-resolution.
-
-As mentioned above, multiple image super-resolution algorithms are based on the assumption that all input images are reflections of the same scene.
-It can be assumed that there exists a high-res image H, and each input low-res image Li is a version of an aliased, blurred, downsampled and noised H.
-By modelling the alias, blur and noise effects, and comparing these low-res inputs, we can grasp an estimation of those degrading effects and neutralize them, and the output of our super-resolution algorithm will be a high-res image H’ with the most possibility to single-handedly generate all the input images Li via the aliasing, blurring, downsampling and noising processes.
+These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single image super-resolution.
 
 Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem.
-Early works focus on the analysis of the images on frequency or special domains, focusing on their pixel level differences and merging their information.
-Spatial domain methods mostly work on the interpolation approach, trying to insert new pixels between pixels of the low-res images.
-One of the well-known methods in the spatial domain is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images with gradient decent methods.
-On the other hand, frequency domain approaches focus on the Fourier transform of the images, and reconstruct high-res images based on patterns of the images in the frequency domain.
-Downsampling processes remove high-frequency components of the images, preserving low-frequency components; Noises often exists in a certain frequency band and can thus be identified and removed.
-By assuming that the high-res scene is band-limited, with CFT and DFT transformations, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time.
+Early works focus on the analysis of the images on spatial or frequency domains.
+One of the widely known spatial domain methods is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images.
+On the other hand, frequency domain approaches focus on the Fourier transform of the images.
+By assuming that the high-res scene is band-limited, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time.
 A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc.
@@
 This work focuses on single image super-resolution, as the neural network accepts a single image as input.
-As Generative Adversarial Networks (GAN) were proposed, the network good at constructing images pleasant to the human eye was also introduced into the domain of super resolution \cite{ledig2017photo}.
-These networks generate photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene.
-Note that super resolution is an ill-posed problem, that is, we do not have a ‘ground truth’ to begin with, and traditional evaluation methods, e.g.
-mean square error (MSE) might not be suitable according to the application.
-Although SRGAN might score slightly lower on MSE, it can reconstruct more high-frequency and realistic details and score much higher on the mean opinion score (MOS).
-However, when published, the above works were limited to single input images.
-Because of increasing complexity and training difficulty, we cannot directly modify these super resolution neural networks to accept multiple images as input.
-There are also various works adapting neural networks to perform multi-image SR tasks.
-The most common variation is video SR\cite{shi2016real, kappeler2016video}, accepting complete video clips as input, and functioning on the similarity between frames.
+Generative Adversarial Networks (GAN) were also used in this era\cite{ledig2017photo}, generating photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene.
+When published, the above works were limited to single input images, and most multi-image SR tasks are variations of them.
+The most common variation is video SR\cite{shi2016real, kappeler2016video}, with a structure similar to SRCNN, accepting complete video clips as input, and functioning on the similarity between frames.
 The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily.
@@
 These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.
-
-However, the methods mentioned above are not suitable for our application and we need a novel approach.
-The blurriness of our photos exceeds the processing ability of non-learning methods; furthermore, these photos are extremely blurred, defocused and full of noise so that few information can be extracted from them via single image SR methods; The adjacent frames display drastically different blurring patterns so that they lack consistency between adjacent frames.
-Only from an overall view of all the images can we distinguish noise from facts, and we need a network that can comprehend the similarities and differences between each frame to recover the buried information, and indeed, building an end-to-end multi-image SR network without assuming sequential consistency between frames is still a very much underexplored field of study, and our work aims at filling that gap.
+However, because of the extreme blurriness of the photos and the lack of consistency between frames, the methods mentioned above are not suitable for our application and we need a novel approach.

### 2020-06-30 introduction.tex
intro_cl_063016pm

@@
 % introduce LPL asynchronous duty cycle media access
-As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
+Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
 As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing".
-Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes.
-And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages.
+Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}.
+For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment.
 % It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm.
@@
 The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years.
-Given the commercial smartphone, the attacker cannot acquire sensitive information from a long distance to reduce suspicion, but also recognize the information accurately for propagating, making existing defense work ineffective.
-For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
 Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
@@
 And more images mean more recorded information of the victim.
-To gain vital data stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.
+Given the commercial smartphone, the attacker can record the information reliably for propagating.
+For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
+To gain vital data more stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.
 
@@
 
-To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}.
+Unfortunately, none of existing work can mitigate the new threat model.
+Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}.
 All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios.
@@
 \begin{itemize}[leftmargin=*]
-  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without much room for focusing.
+  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing.
 It can be further exacerbated by straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ``normally" captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction" than ``interpolation"".
+Unlike most SR applications and datasets working with ``normally" captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction" than ``interpolation".
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
@@
 As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
-  On one hand, each photo is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel.
-Thus they cannot be processed as a video clip due to the lacking consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}; on the other hand, because of the low concentration of information, blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information.
+  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}.
+Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle.
   % and the only chance of recovering the ground truth is to compare each photo against others. 
-  Few useful information can be extracted separately and merged directly to produce satisfactory results if processed by common procedures to enhance the resolution of a series of snapshots\cl{citation?}.
+  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}. 
   \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents.
-However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred photos as input.
+However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input.
 Since smartphones can capture 10 snapshots per second in burst mode.
@@
 Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process.
-Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this photo.
+Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.
   \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server.
@@
 Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings.
-The system is able to capture photos and produce high-res images constantly with about 2 seconds interval.
+The system is able to capture snapshots and produce high-res images constantly with about 2 seconds interval.
 Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.

### 2020-06-30 abstract.tex
abstract + introduction

@@
 To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms, rendering the underestimated threat model.
-To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including an unique deep neural network (DNN) architecture for multi-image SR.
-Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the multiple types of contents off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images.
+With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
+To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.
+We implement SPPeek in Android.
+The experimental results demonstrate its efficiency and robustness, allowing a human to read 95\% text contents when the distance between the camera and screen is as long as 1.5m in different scenarios.
 And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.

### 2020-06-30 introduction.tex
abstract + introduction

--- 2020-06-30 introduction.tex
@@
 As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
-As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing".
+As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing''.
 Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes.
@@
 Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios.
-Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
+Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
 \begin{figure}
@@
 Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters.
-The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.
+The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim's screen.
 
@@
 It can be further exacerbated by straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ``normally" captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction" than ``interpolation"".
+Unlike most SR applications and datasets working with ``normall'' captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction'' than ``interpolation''.
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
@@
 Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings.
-The system is able to capture photos and produce high-res images constantly with about 2 seconds interval.
+The system is able to capture photos and produce high-resolution images constantly with about 2 seconds interval.
 Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.

### 2020-06-30 introduction.tex

--- 2020-06-30 introduction.tex
@@
 Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
-As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing".
+As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing''.
 Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}.
 For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment.
+
 % It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm.
@@
 Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios.
-Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
+Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
+
 \begin{figure}
@@
 It can be further exacerbated by straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ``normally" captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction" than ``interpolation".
+Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''.
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
+
   % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.

### 2020-06-30 related_work.tex
intro_cl_063016pm
related work

@@
-\section{Related Work}
-\label{sec-related-work}
 \begin{table*}[t]
-    \caption{A comparison of state-of-the-art works on Wi-Fi Imaging.}
+    \caption{A comparison of state-of-the-art works on shoulder surfing.}
     \vspace{2mm}
@@
     \hline
-     Reference  & Principle &  RF Platform & Method & \#(Tx,Rx) Ant$^{\mathrm{a}}$\\ 
+     Reference & Subject & Range$^{\mathrm{a}}$ & Deployment & Performance\\ 
     \hline
@@
     \hline
-    \textbf{\textsf{WiHolo-2D}} & Intensity \& Polarization & COTS Wi-Fi & 2D IFFT \& GAN &(1,6) \\
+    \textbf{\textsf{SRPeek}} & Multi-type Characters & 1.5m \& 30$^\circ$ & COTS smartphones & Recovery 95\% Contents in Real Time \\
     \hline
-    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning. $^{\mathrm{b}} $The receive beam sweeps from $+90^{\circ}$ to $-90^{\circ}$ for one}\\
-    \multicolumn{5}{l}{transmit beam angle between $+90^{\circ}$ and $-90^{\circ}$. $^{\mathrm{c}}$The RX drone measures the RSSI every 2 cm for the 3m$\times$3m area.}\\
-    \multicolumn{5}{l}{$^{\mathrm{d}}$Achieve a resolution of 4.0 cm $\times$ 7.2 cm for the 2m$\times$3m area.}\\
+    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning.}\\
     \end{tabular}
@@
 
+\section{Related Work}
+\label{sec-related-work}
+
 \cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
@@
 With the arrival of the information era, privacy issues are becoming increasingly prominent.
-Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily in recent years.
-Surveys of shoulder surfing provides evidence of this behavior in real world \cite{eiband2017understanding} \cite{goucher2011look}, often more efficient than expected\cite{kwon2013covert}.
-Various techniques and systems have been designed to mitigate this threat.
-Some systems sense malicious passers-by and hide information \cite{brudy2014anyone} or warn the user\cite{saad2018communicating}; others modify the user interfaces to create honeypots (for passwords)\cite{chakraborty2014tag}, confuse unauthorized parties\cite{wiedenbeck2006design}, or making the interactions invisible\cite{kumar2007reducing} or unreadable from a distance\cite{Chun2019Keep}.
-Most of the works designing defenses against shoulder surfing assume that the attacker is a casual passer-by, taking occasional peeks with his/hers naked eye, as is the case most of the time\cite{eiband2017understanding}.
-However, it is the malicious ones, although few, that can utilize the information (passwords, business correspondence, etc.) they obtained to do real harm.
-On the other hand, the threat model of tool-assisted shoulder surfing is also studied.
-Schaub, et, al.
-observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}.
-Maggi, et al.
-designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}, but without the help of SR techniques, this method can only function when the attacker is standing at close range, which is a barely practical scenario.
-With the development of smartphone camera, processing ability, and SR technology over the years, we propose a stronger shoulder surfing system in which attackers can successfully obtain information while keeping a distance to avoid suspicion, and prove that this threat is eminent in our daily life.
+Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}.
+To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
+Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}.
+Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
+To deal with the threat model of tool-assisted shoulder surfing\cl{more citations?},
+% Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
+Maggi et al.
+designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}.
+It can however only function when the attacker is standing at close range, which is a barely practical scenario.
+By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can successfully obtain information for a longer range to reduce suspicion.
+Evaluations demonstrate its feasibility and privacy concerns in our daily life.
 

### 2020-07-01 introduction.tex
change temp
revise by cl

@@
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
-
   % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing attack.
-We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}, respectively.
-We further wrap up this paper by presenting the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}.
-And the conclusion is show in Section~\ref{sec-conclusion}.
+Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing and SR techniques.
+We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}.
+We further wrap up this paper by delivering the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}.
+And the conclusion is shown in Section~\ref{sec-conclusion}.

### 2020-07-01 related_work.tex
change temp
revise by cl

@@
     \hline
-     Reference & Subject & Range$^{\mathrm{a}}$ & Deployment & Performance\\ 
+     Reference & Deployment & Range$^{\mathrm{a}}$ & Subject & Performance\\ 
     \hline
@@
     \hline
-    \textbf{\textsf{SRPeek}} & Multi-type Characters & 1.5m \& 30$^\circ$ & COTS smartphones & Recovery 95\% Contents in Real Time \\
+    \textbf{\textsf{SRPeek}} & COTS smartphones & 1.5m \& 30$^\circ$ & Multi-type Characters & Real-time Monitoring with 95\% Contents\\
     \hline
-    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning.}\\
+    \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance and observing view angle to the victim's screen.}\\
     \end{tabular}
-    \label{comparison}
+    \label{tbl:comparison}
     \end{center}
@@
 \label{sec-related-work}
-
-\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
 \subsection{Shoulder Surfing}
@@
 To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
-Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}.
+Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}\cl{more citation and table 1 row-1}.
 Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
-To deal with the threat model of tool-assisted shoulder surfing\cl{more citations?},
+To deal with the threat model of tool-assisted shoulder surfing\cl{more citation and table 1 row-2},
 % Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
 Maggi et al.
-designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}.
+designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}.
 It can however only function when the attacker is standing at close range, which is a barely practical scenario.
-By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can successfully obtain information for a longer range to reduce suspicion.
+By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.5m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
 Evaluations demonstrate its feasibility and privacy concerns in our daily life.
@@
 \subsection{Super Resolution}
-Image super-resolution is the process of reconstructing an image with a higher spatial resolution.
-Single image super-resolution techniques accept a single low-res image as input, and based on its structural pattern, self-similarity \cite{suetake2008image}, or previous knowledge of the genre of the image, deduces missing information and reconstructs the missing pixels to form a sharp, high-res image.
-On the other hand, multiple image super-resolution techniques work on a set of pictures on the same scene, e.g.
-multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip.
-These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single image super-resolution.
+Image SR is the process of reconstructing an image with a higher spatial resolution.
+Based on the structural pattern, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
+Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip.
+These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms.
+And a variety of techniques have been proposed for the multi-image SR problem.
+And early works focus on the analysis of images in spatial or frequency domains.
+For example, the Shift-Add algorithm~\cite{farsiu2003robust} analyzes the spatial information by maximizing the pixel-wise possibility of high-resolution image from low-resolution images.
+Besides, approaches for the frequency domain rely on the Fourier transform of images.
+Assuming that the high-resolution scene is band-limited, these algorithms reconstruct high-frequency components from patterns of low-frequency components, removing bands of noise and blur effects simultaneously.
+Unfortunately, all SR techniques  however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics\cl{more citation and table 1 row-3}.
+While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.
 
-Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem.
-Early works focus on the analysis of the images on spatial or frequency domains.
-One of the widely known spatial domain methods is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images.
-On the other hand, frequency domain approaches focus on the Fourier transform of the images.
-By assuming that the high-res scene is band-limited, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time.
-A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc.
-and achieve best performance only in their own field.
-
-More recent works of Super Resolution are often based on deep learning approaches.
-In 2016, SRCNN \cite{dong2015image} was developed from CNN replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches.
-This work focuses on single image super-resolution, as the neural network accepts a single image as input.
-Generative Adversarial Networks (GAN) were also used in this era\cite{ledig2017photo}, generating photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene.
-When published, the above works were limited to single input images, and most multi-image SR tasks are variations of them.
-The most common variation is video SR\cite{shi2016real, kappeler2016video}, with a structure similar to SRCNN, accepting complete video clips as input, and functioning on the similarity between frames.
-The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily.
-Other works face image groups without consistency or sequential information, e.g.
-satellite images.
-To achieve appreciable results, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures.
-They commonly function by merging the results of single image SR algorithms to efficiently utilize input information\cite{kawulok2019deep}, or building a multi-image network to create a course view and support it with single image SR networks\cite{8834937}.
-These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.
-However, because of the extreme blurriness of the photos and the lack of consistency between frames, the methods mentioned above are not suitable for our application and we need a novel approach.
+Deep learning approaches can also be adopted for Super Resolution.
+For example, SRCNN~\cite{dong2015image} was designed using CNN by replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches.
+It however only focuses on single image SR, as the neural network accepts a single image as input\cl{table 1 row-4}.
+Besides, Generative Adversarial Networks (GAN) were also used to generate photo-realistic images~\cite{ledig2017photo}, with less artifacts and more genuine-looking details perceptible to the human eye.
+To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input.
+Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
+% modifying the 2d convolution layers to 3d convolution~\cite{caballero2017real}, 
+we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}\cl{table 1 row-5}..
+For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures.
+They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}\cl{table 1 row-6}.
+Due of the extreme blurriness of snapshots, these methods can not deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.
+And they achieve limited performance, shown in Table~\ref{tbl:comparison}.
+% These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.

### 2020-07-01 conclusion.tex
revise by cl

--- 2020-06-14 conclusion.tex
@@
 \label{sec-conclusion}
-In this work we designed a holistic system for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
-We proved that this threat towards screen privacy is imminent and can cause damage while undetected.
+In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
+We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection.
 It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps.
-Although this system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
-One of these defenses is displaying a dynamic background behind the characters, with a small protion of patterns colored similar to the texts.
-The constant changes will confuse most of the multi-frame SR algorithms, as they are often designed based on the assumption that all input images are reflections of the same scene.
-Other defence methods include active scanning for suspicious individuals, encrypted keyboards at password entry phases, etc.
+
+The core of SRPeek is a specially designed multi-frame SR network.
+With its innovative architecture this network outperforms other algorithms of the same field in our application.
+The design ideology enables this network to process higher levels of data integration ability while keeping a low calculation profile, and we believe the elements of this design can be used in other applications with large amounts of data, such as natural language processing or anomaly detection.
+Our model can also be used in OCR tasks when multiple images are avaliable, functioning as a preprocessor to improve the quality of the images and increase accuracy.

### 2020-07-01 design.tex
revise by cl

@@
 Till now the model is not different from traditional SR models:
-
-$$x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N$$
+\begin{equation}\label{eq:1}
+    \begin{split}
+x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N
+\end{split}
+\end{equation}
 
@@
 Additionally, we introduce the initial images $x_i^{(0)}$ as an input for all the layers:
-
-$$x_i^{(l)} = H_l(x_i^{(l-1)},x_i^{(0)}), i=1,2,...N$$
+\begin{equation}\label{eq:2}
+    \begin{split}
+        x_i^{(l)} = H_l(x_i^{(l-1)},x_i^{(0)}), i=1,2,...N
+\end{split}
+\end{equation}
 
@@
 To increase resolution we insert several 2$\times$ nearest upsampling layers $U$ evenly throughout the architecture between the layers:
-
-$$x_i^{(l)} \leftarrow U(x_i^{(l)}), x_i^{(0)} \leftarrow U(x_i^{(0)}), i=1,2,...N$$
+\begin{equation}\label{eq:3}
+    \begin{split}
+        x_i^{(l)} \leftarrow U(x_i^{(l)}), x_i^{(0)} \leftarrow U(x_i^{(0)}), i=1,2,...N
+\end{split}
+\end{equation}
 
@@
 \cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
+\begin{figure}
+    \centering
+       \includegraphics[width=0.5\textwidth]{./pic/network.pdf}
+       \caption{Network Architecture of SRPeek.}
+       \label{fig-system}
+   \end{figure}
 
@@
 \noindent
-\textbf{Conv1.} The first convolutional layer, $Conv1$, accepts the layer's first input parameter $x_i^{(l-1)}$ as input.
+\textbf{Conv1:} The first convolutional layer, $Conv1$, accepts the layer's first input parameter $x_i^{(l-1)}$ as input.
 Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):
-
-$$ a_i^{(l)} = Conv_{1l}(x_i^{(l-1)},Param_{1l}), i=1,2,...N$$
+\begin{equation}\label{eq:4}
+    \begin{split}
+        a_i^{(l)} = Conv_{1l}(x_i^{(l-1)},Param_{1l}), i=1,2,...N
+\end{split}
+\end{equation}
 
@@
 \noindent
-\textbf{Merge.} The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps.
+\textbf{Merge:} The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps.
 Suppose the results of $Conv_{1l}$ consists of $R$ channels:
-
-$$ a_i^{(l)} = \{a_{i1}^{(l)},a_{i2}^{(l)},...,a_{iR}^{(l)}\}, i=1,2,...N$$
+\begin{equation}\label{eq:5}
+    \begin{split}
+        a_i^{(l)} = \{a_{i1}^{(l)},a_{i2}^{(l)},...,a_{iR}^{(l)}\}, i=1,2,...N
+\end{split}
+\end{equation}
 
@@
 
-$$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$
+\begin{equation}\label{eq:6}
+    \begin{split}
+        b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}}
+\end{split}
+\end{equation}
 
@@
 \noindent
-\textbf{Conv2.} $Conv2$ is a replica of $Conv1$, processing the layer's second input parameter $x_i^{(0)}$, also generating $N$ outputs with $R$ channels per output, denoted as $c_ir^{(l)}, i=1,2,...N, r=1,2,...R$:
-
-$$ c_i^{(l)} = Conv_{2l}(x_i^{(0)},Param_{2l}), i=1,2,...N$$
-
-$$ c_i^{(l)} = \{c_{i1}^{(l)},c_{i2}^{(l)},...,c_{iR}^{(l)}\}, i=1,2,...N$$
+\textbf{Conv2:} $Conv2$ is a replica of $Conv1$, processing the layer's second input parameter $x_i^{(0)}$, also generating $N$ outputs with $R$ channels per output, denoted as $c_ir^{(l)}, i=1,2,...N, r=1,2,...R$:
+\begin{equation}\label{eq:7}
+    \begin{split}
+        c_i^{(l)} &= Conv_{2l}(x_i^{(0)},Param_{2l}), i=1,2,...N\\
+        c_i^{(l)} &= \{c_{i1}^{(l)},c_{i2}^{(l)},...,c_{iR}^{(l)}\}, i=1,2,...N\\
+\end{split}
+\end{equation}
 
@@
 \noindent
-\textbf{Conv3.}The data from $Merge$ and $Conv2$ are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$.
+\textbf{Conv3:} The data from $Merge$ and $Conv2$ are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$.
 There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:
-
-$$ d_i^{(l)} = Conv_{3l}(Stack(c_i^{(l)},b^{(l)}),Param_{3l}), i=1,2,...N $$
+\begin{equation}\label{eq:8}
+    \begin{split}
+        d_i^{(l)} = Conv_{3l}(Stack(c_i^{(l)},b^{(l)}),Param_{3l}), i=1,2,...N 
+\end{split}
+\end{equation}
 
@@
 \noindent
-\textbf{Output.}If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$.
+\textbf{Output:} If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$.
 Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$.
 The merging layer is identical to the previous $Merge_l$, merging the N outputs $d_i^{(l)}$ into $T\times R$ channels $e_{tr}^{(l)}$, and a convolutional layer processes this $e_{tr}^{(l)}$ to generate a single channel of output $y$.
-
-$$ \{e_{tr}^{(L)},t\le T,r\le R\} = Merge'_{L}(\{d_i^{(L)},i\le N\})$$
-
-$$ y = Conv'_{L}(\{e_{tr}^{(L)},t\le T,r\le R\} )$$
+\begin{equation}\label{eq:7}
+    \begin{split}
+        \{e_{tr}^{(L)},t\le T,r\le R\} &= Merge'_{L}(\{d_i^{(L)},i\le N\})\\
+        y &= Conv'_{L}(\{e_{tr}^{(L)},t\le T,r\le R\} )\\
+\end{split}
+\end{equation}
 
@@
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/design.pdf}
-    \caption{Network Architecture of SRPeek.}
-    \label{fig-system}
-\end{figure}
-
 \subsection{system design}
-
 We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
@@
 \noindent
-\textbf{Input.} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
+\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
 Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
@@
 \noindent
-\textbf{Alignment.} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 \noindent
-\textbf{Adjustment.} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
+\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
 The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
@@
 \noindent
-\textbf{Processing.} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
+\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
 After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).

### 2020-07-01 introduction.tex
revise by cl

@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/intro.png}
-    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.
-\cl{supplement elements for long range, blurred input and the recognized results.}}
+	\includegraphics[width=0.5\textwidth]{pic/illustration.pdf}
+    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
 	\label{illustration_of_system}
@@
 % describe the organization of the paper
+
 The rest of the paper is organized as follows.

### 2020-07-01 limitation_and_discussion.tex
revise by cl

@@
-\section{Limitations}
-\subsection{Image Capturing Ability}
+\section{Limitations \& Discussions}
+\label{sec-limitations-and-discussions}
+
+\vspace{1mm}
+\noindent
+\textbf{Image Capturing Ability}
 Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old.
@@
 The user also has to keep a sharp focus on the target phone.
-\subsection{Processing Ability}
+
+\vspace{1mm}
+\noindent
+\textbf{Processing Ability}
 To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time.
 As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
-\subsection{Motion and Tremors}
+
+\vspace{1mm}
+\noindent
+\textbf{Motion and Tremors}
 In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often.
@@
 Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.
+
+Although our shoulder surfing system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
+
+\vspace{1mm}
+\noindent
+\textbf{Dynamic background.} Most multi-frame SR algorithms are designed based on the assumption that all input images are reflections of the same scene, and ours is not an exception.
+By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influencial elements cannot be easily removed.
+These dots do not need to be distinct or colored same as the the texts, as multi-frame SR algorithms function with tiny,pixel level differences between frames, making them especially sensitive to microscopic changes.
+
+\textbf{Active scanning.} There are several works providing an active countermeasure against shoulder surfing threats with the naked eye.
+With front-facing cameras and face detection algorithms, the smartphone can constantly scan the surrounding passers-by and detect their gaze direction, and give a warning to the user when that gaze points at the screen.
+However, to the extent of our knowledge none of these works have included cameras into their detection scope, but we believe it's practical to implement such features.
+
+\textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network.
+These methods fools the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
+Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remains to be implemented in our future work.

### 2020-07-01 system_overview.tex
revise by cl

--- 2020-06-28 system_overview.tex
@@
 \label{sec-system-overview} 
-\begin{figure}
-    \centering
-       \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
-       \caption{Illustration of the workflow of our shoulder-surfing system.}
-       \label{fig-workflow}
-\end{figure}
+To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
+\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
 
-The outline of this network is as follows:
 \begin{itemize}[leftmargin=*]
@@
 At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
+  \begin{figure}
+    \centering
+       \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
+       \caption{Illustration of the workflow of our shoulder-surfing system.}
+       \label{fig-workflow}
+  \end{figure}
   \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.

### 2020-07-01 design.tex
revise by cl

@@
 
-\subsection{network design}
+\subsection{Design Principal}
+To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
+\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
+
+\begin{itemize}[leftmargin=*]
+    \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
+The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image.
+Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
+    \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images.
+As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently.
+This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution.
+In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer.
+In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase.
+At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
+    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
+This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters.
+In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps.
+This process functions with any number of input images.
+As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input.
+On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
+    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results.
+The frequent introduction of input images is designed to mitigate this challenge.
+Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images.
+We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data.
+The loss functions in training is also redesigned.
+The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
+Our solution is putting a weight on each pixel before applying weighted MSE.
+Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights.
+This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests.
+  \end{itemize}
+
+\subsection{Network Design}
 The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output.
@@
 
-\subsection{system design}
-We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
+% \subsection{Design Principal}
+% To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
+% \cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
 
-\vspace{1mm}
-\noindent
-\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
+% \subsection{system design}
+% We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
+
+% \vspace{1mm}
+% \noindent
+% \textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
 Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
@@
 
-\vspace{1mm}
-\noindent
-\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+% \vspace{1mm}
+% \noindent
+% \textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 
-\vspace{1mm}
-\noindent
-\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
+% \vspace{1mm}
+% \noindent
+% \textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
 The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
 
-\vspace{1mm}
-\noindent
-\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
+% \vspace{1mm}
+% \noindent
+% \textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
 After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
@@
 
-These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.
+% These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.
 At critical times requiring continuous monitoring so as not to miss transient display, e.g.

### 2020-07-01 system_overview.tex
revise by cl

--- 2020-06-28 system_overview.tex
@@
 \label{sec-system-overview} 
+We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
+
+\vspace{1mm}
+\noindent
+\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
+Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
+This way information on the images will be more compact and easier to comprehend by neural networks.
+
+\vspace{1mm}
+\noindent
+\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
+The images are also spun to make the text horizontal in the process.
+The screen is cropped out and the rest of the image abandoned.
+
+\vspace{1mm}
+\noindent
+\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
+The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
+
+\vspace{1mm}
+\noindent
+\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
+After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
+The input is RGB colored, while the output, as we are not interested in color, is black and white.
+When all patches are processed, their outputs are merged together.
+The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
+In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.
+
+These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.
+At critical times requiring continuous monitoring so as not to miss transient display, e.g.
+password entering, the system can simply lengthen the input phase across that period and process the data afterwards.
+The workflow of our system is shown in Figure~\ref{fig-workflow}.
 \begin{figure}
@@
 \end{figure}
-
-The outline of this network is as follows:
-\begin{itemize}[leftmargin=*]
-  \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
-The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image.
-Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
-  \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images.
-As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently.
-This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution.
-In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer.
-In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase.
-At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
-  \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
-This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters.
-In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps.
-This process functions with any number of input images.
-As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input.
-On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
-  \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results.
-The frequent introduction of input images is designed to mitigate this challenge.
-Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images.
-We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data.
-The loss functions in training is also redesigned.
-The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
-Our solution is putting a weight on each pixel before applying weighted MSE.
-Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights.
-This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests.
-\end{itemize}

### 2020-07-01 limitation_and_discussion.tex
revise by cl
fig

@@
 \textbf{Dynamic background.} Most multi-frame SR algorithms are designed based on the assumption that all input images are reflections of the same scene, and ours is not an exception.
-By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influencial elements cannot be easily removed.
+By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influential elements cannot be easily removed.
 These dots do not need to be distinct or colored same as the the texts, as multi-frame SR algorithms function with tiny,pixel level differences between frames, making them especially sensitive to microscopic changes.
 
+\vspace{1mm}
+\noindent
 \textbf{Active scanning.} There are several works providing an active countermeasure against shoulder surfing threats with the naked eye.
@@
 
+\vspace{1mm}
+\noindent
 \textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network.

### 2020-07-01 abstract.tex
修改“

@@
 We implement SPPeek in Android.
-The experimental results demonstrate its efficiency and robustness, allowing a human to read 95\% text contents when the distance between the camera and screen is as long as 1.5m in different scenarios.
+The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses.
 And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.

### 2020-07-01 design.tex
修改“

@@
 To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
-\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
+%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
 
@@
     \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
-The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image.
+All input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
 Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
-    \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images.
-As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently.
-This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution.
-In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer.
-In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase.
+    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution.
 At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
-    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
-This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters.
-In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps.
-This process functions with any number of input images.
-As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input.
+    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
+This trait also enables the  the same network to adapt any number of input images.
 On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
@@
 The frequent introduction of input images is designed to mitigate this challenge.
-Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images.
+Also, our model can learn correlations between certain features and strokes from the training data, decomposing the SR problem and making it a lot less challenging.
 We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data.
@@
 
-\cl{function above cannot express merging between x1 x2 ... xN?}
+%\cl{function above cannot express merging between x1 x2 ... xN?}
 
@@
 
-\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
+%\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}
 \begin{figure}

### 2020-07-01 evaluation.tex
修改“

@@
+\section{Evaluation \& Case Study}
+\label{sec-evaluation}
 
-\section{Model Evaluation}
 We evaluate the ability of the network model, testing its performance in different training and testing conditions.
@@
 
-\section{System Evaluation}
+% \section{System Evaluation}
 \subsection{Accuracy}
@@
 \centering
-\begin{tabular}{@{}lllll@{}}
+\begin{tabular}{@{}ccccc@{}}
 	\toprule
-Scenario & Read text & Type text & Enter PIN & Enter password\\ \midrule
-\begin{tabular}[c]{@{}l@{}}Human\\ Recognition\\ Accuracy\\(raw image)\end{tabular} & 5 & 0 & 0 & 0\\ \\
-Accuracy & 100 & 100 & - & -\\ \\
-\begin{tabular}[c]{@{}l@{}}Accuracy\\ per character\end{tabular}& - & - & 100 & 80\\ \bottomrule
+Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
+raw image & 5 & 0 & 0 & 0\\ \\
+SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
 \end{tabular}
 
-\caption{Success rate in different tasks}
+\caption{Success rate in different tasks.}
 \label{table-task}

### 2020-07-01 implementation.tex
修改“

@@
-\section{Implementation and Training}
-
-\label{sec-implementation-and-evaluation}
+\section{Implementation \& Training}
+\label{sec-implementation-and-training}
 
@@
          }
-     \subfigure[ground truth]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
-         \label{fig-train-single-5}
-         }
+    % \subfigure[ground truth]{
+     %    \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
+      %   \label{fig-train-single-5}
+       %  }
         \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
@@
 Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
-
+\begin{figure}
+  \centering
+     \centering
+     \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
+         \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
+         \label{fig-exp1}
+         }
+   \subfigure[screenshot from attacker's phone(SRPeek system).]{
+         \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
+         \label{fig-exp2}
+         }
+   \subfigure[screenshot from victim's phone.]{
+         \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
+         \label{fig-exp3}
+         }
+     \caption{Illustration of our experimental setting.}
+     \label{fig-experiment}
+\end{figure}
 The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.).

### 2020-07-01 introduction.tex
修改“

@@
 \textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
-Assuming the victim is scanning messages in life, the attacker can raise his commercial smartphone with powerful lenses and our SR network to the victim stealthily, even from a long range (e.g., 1.5 meters far away within the visual angle of 30$^{\circ}$).
-As the camera zooms in, he can take 20 to 30 snapshots continuously in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames.
-This process can take about 2 seconds with the consistent content and position for the screen of the victim.
-Benefited from our multi-frame SR neural network, those blurred snapshots can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim in real time.
-Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters.
-The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim's screen.
+While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone, zooms in on the victim's screen, takes 10 to 20 snapshots rapidly in burst mode(about 10 frames per second), and process them with a multi-frame SR system to generate a high-res result.
+The whole process takes only a few seconds and can even be repeated at a 2 second interval to give the attacker a continuous surveillance over the victim's screen, not missing any detail, while at the same time, few people would suspect a stranger holding his smartphone at 1.8 meters behind them.
+With the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can be raised to a staggering 6 meters, posing a silent but deadly threat to screen privacy.
 
@@
 \noindent
-\textbf{Challenges.} Creating a high-resolution shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time.
+\textbf{Challenges.} Creating a powerful SR based shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time.
 And we achieve \textsf{SRPeek} by overcoming four key challenges.
@@
 As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
-  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}.
-Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle.
+  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames, shown in Figure~\ref{illustration_of_system}.
+Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for interigation abilities of the SR algorithms than most other SR applications.
   % and the only chance of recovering the ground truth is to compare each photo against others. 
-  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}. 
+%  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}.
   \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents.
@@
 Since smartphones can capture 10 snapshots per second in burst mode.
-Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cl{citation?}.
+Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cite{lucas2019generative} \cite{kappeler2016video}.
 The reason has two folds.

### 2020-07-01 related_work.tex
revise by cl
修改“

@@
     \hline
-     Reference & Deployment & Range$^{\mathrm{a}}$ & Subject & Performance\\ 
+     Reference & Equipment & Training & distance$^{\mathrm{a}}$ \\
     \hline
-    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
-    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
-    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
-    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
-    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
+    Eiband~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
+    Kwon~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
+Schaub~\cite{schaub2012password} & naked eye & untrained & Intimate\\
+    Maggi~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
     \hline
-    \textbf{\textsf{SRPeek}} & COTS smartphones & 1.5m \& 30$^\circ$ & Multi-type Characters & Real-time Monitoring with 95\% Contents\\
+    \hline
+    \textbf{\textsf{SRPeek}} & COTS smartphones & trained  & 1.8m(traditional)\\
+  & & &6m(optical zoom)\\
     \hline
     \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance and observing view angle to the victim's screen.}\\
+
+    \multicolumn{5}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
     \end{tabular}
@@
 To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
-Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}\cl{more citation and table 1 row-1}.
+Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding} ~\cite{wiedenbeck2006design}.
 Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
-To deal with the threat model of tool-assisted shoulder surfing\cl{more citation and table 1 row-2},
+To deal with the threat model of tool-assisted shoulder surfing,%\cl{more citation and table 1 row-2},
 % Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
@@
 Assuming that the high-resolution scene is band-limited, these algorithms reconstruct high-frequency components from patterns of low-frequency components, removing bands of noise and blur effects simultaneously.
-Unfortunately, all SR techniques  however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics\cl{more citation and table 1 row-3}.
-While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.
+Unfortunately, all SR techniques  however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics~\cite{Youm2016Image}
+%\cl{more citation and table 1 row-3}
+. While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.
 
@@
 For example, SRCNN~\cite{dong2015image} was designed using CNN by replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches.
-It however only focuses on single image SR, as the neural network accepts a single image as input\cl{table 1 row-4}.
+It however only focuses on single image SR, as the neural network accepts a single image as input.
 Besides, Generative Adversarial Networks (GAN) were also used to generate photo-realistic images~\cite{ledig2017photo}, with less artifacts and more genuine-looking details perceptible to the human eye.
@@
 % modifying the 2d convolution layers to 3d convolution~\cite{caballero2017real}, 
-we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}\cl{table 1 row-5}..
+we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
 For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures.
-They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}\cl{table 1 row-6}.
+They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}.
 Due of the extreme blurriness of snapshots, these methods can not deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.

### 2020-07-01 evaluation.tex
fig

@@
 
-\begin{figure}
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
-    \caption{Performance in Controlled Environment(Traditional Lenses)}
-    \label{fig-control}
-\end{figure}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \hfill
+    \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
+    \label{fig-performance-1}
+\end{figure*}
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
-    \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
-    \label{fig-control2}
-\end{figure}
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
+%     \caption{Performance in Controlled Environment(Traditional Lenses)}
+%     \label{fig-control}
+% \end{figure}
+
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
+%     \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
+%     \label{fig-control2}
+% \end{figure}
 \subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random2}).
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random-2}).
 The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
-    \caption{Performance in Random Environment(Traditional Lenses)}
-    \label{fig-random}
-\end{figure}
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
+%     \caption{Performance in Random Environment(Traditional Lenses)}
+%     \label{fig-random}
+% \end{figure}
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
-    \caption{Performance in Random Environment(Optical Zoom Lenses)}
-    \label{fig-random2}
-\end{figure}
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
+%     \caption{Performance in Random Environment(Optical Zoom Lenses)}
+%     \label{fig-random-2}
+% \end{figure}
 We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability.
 Also, the model performs better at closer distances.
-As the model is trained initially on the 5m group data, it performs expecially well at this distance, while the accuracy at other distances experience certain levels of decrease.
-Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplist characters can escape from being flooded by noize.
+As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease.
+Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.
+
+\begin{figure*}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \hfill
+    \caption{Performance for Adapting Ability and various processing images.}
+    \label{fig:adapting}
+\end{figure*}
 
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-The results are shown in Figure~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
+The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
 
-\begin{figure}
- \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
-    \caption{Adapting Ability(Traditional Lenses)}
-    \label{table-adapt}
-\end{figure}
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
+%     \caption{Adapting Ability(Traditional Lenses)}
+%     \label{table-adapt}
+% \end{figure}
 
@@
 
-\begin{figure}
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
+%     \caption{Comparison with other architectures}
+%     \label{table-comp}
+% \end{figure}
+
+\begin{table}[!t]
     \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
-    \caption{Comparison with other architectures}
+    \begin{tabular}{@{}cccc@{}}
+        \toprule
+    System & SRPeek & SRCNN & VideoSR \\ \midrule
+    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
+    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
+    \end{tabular}
+    \caption{Comparison with existing systems.}
     \label{table-comp}
-\end{figure}
+\end{table}
 
@@
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-The results are shown in Figure~\ref{table-accuracy}.
+The results are shown in Figure~\ref{table-scenarios}.
 
-\begin{figure}
+\begin{table}[!t]
     \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
-    \caption{Accuracy in different real-life scenarios}
-	\label{table-accuracy}
-\end{figure}
+    \begin{tabular}{@{}cccc@{}}
+        \toprule
+    System & Home & Transport & Theater \\ \midrule
+    Baseline & 5 & 0 & 0\\ 
+    \midrule
+    OCR & 100 & 10 & 23\\ 
+    Human & 95 & 85 & 70\\ \bottomrule
+    \end{tabular}
+    \caption{Recognition accuracy in various scenarios.}
+    \label{table-scenarios}
+\end{table}
+
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
+%     \caption{Accuracy in different real-life scenarios}
+% 	\label{table-accuracy}
+% \end{figure}
 
@@
 
-\begin{figure}
+\begin{table}[!t] 
     \centering
-    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
-\caption{Influence of hand tremors}
+    \begin{tabular}{ccccc}
+        \toprule
+    System & None & Camera & Target & Both  \\
+    \midrule
+    Baseline & 5 & 0 & 5& 5\\ 
+    \midrule
+    OCR & 95 & 85 & 80 & 80\\ 
+    Human & 95 & 85 & 80 & 85\\ \bottomrule
+    \end{tabular}
+    \caption{Impact of hand tremors while holding various items.}
     \label{table-tremor}
-\end{figure}
+\end{table}
+
+% \begin{figure}
+%  \centering
+%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
+% \caption{Influence of hand tremors}
+% \label{table-tremor}
+% \end{figure}
 
@@
 
-\begin{table}[] 
+\begin{table}[!t]
 \centering
@@
 Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
-raw image & 5 & 0 & 0 & 0\\ \\
+Raw Image & 5 & 0 & 0 & 0\\
 SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
 \end{tabular}
-
 \caption{Success rate in different tasks.}

### 2020-07-01 related_work.tex
fig

@@
-\begin{table*}[t]
+\section{Related Work}
+\label{sec-related-work}
+\begin{table}[t]
   \caption{A comparison of state-of-the-art works on shoulder surfing.}
@@
   \begin{center}
-    \begin{tabular}{ccccc}
+  \begin{tabular}{cccc}
   \hline
@@
   \hline
-    \textbf{\textsf{SRPeek}} & COTS smartphones & trained  & 1.8m(traditional)\\
-  & & &6m(optical zoom)\\
+  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 6 meter\\
   \hline
-    \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance and observing view angle to the victim's screen.}\\
+  \multicolumn{4}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\
 
-    \multicolumn{5}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
+  \multicolumn{4}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
   \end{tabular}
@@
   \end{center}
-\end{table*}
+\end{table}
 
-\section{Related Work}
-\label{sec-related-work}
 \subsection{Shoulder Surfing}

### 2020-07-01 evaluation.tex
fig

@@
 \label{sec-evaluation}
-
+% \begin{figure*}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+%     \hfill
+%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
+%     \label{fig-performance-1}
+% \end{figure*}
 We evaluate the ability of the network model, testing its performance in different training and testing conditions.
@@
 \subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control} and Figure~\ref{fig-control2}).
+We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}).
 Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
@@
 Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
+\begin{figure}[!t]
+    \centering
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+    \hfill
+    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
+    \label{fig:control}
+\end{figure}
+
 In the optical zoom group the accuracy of the model dropped drastically at 7m distance.
@@
 
-\begin{figure*}[!t]
+\subsection{Performance In Random Environment}
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}).
+The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
+\begin{figure}[!t]
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control2}}
-    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
     \hfill
-    \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
-    \label{fig-performance-1}
-\end{figure*}
+    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
+    \label{fig:control}
+\end{figure}
 
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
-%     \caption{Performance in Controlled Environment(Traditional Lenses)}
-%     \label{fig-control}
-% \end{figure}
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
-%     \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
-%     \label{fig-control2}
-% \end{figure}
-\subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random-2}).
-The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
-%     \caption{Performance in Random Environment(Traditional Lenses)}
-%     \label{fig-random}
-% \end{figure}
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
-%     \caption{Performance in Random Environment(Optical Zoom Lenses)}
-%     \label{fig-random-2}
-% \end{figure}
 We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability.
@@
 
-\begin{figure*}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
-    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
-    \hfill
-    \caption{Performance for Adapting Ability and various processing images.}
-    \label{fig:adapting}
-\end{figure*}
+% \begin{figure*}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+%     \hfill
+%     \caption{Performance for Adapting Ability and various processing images.}
+%     \label{fig:adapting}
+% \end{figure*}
 
@@
 The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
-%     \caption{Adapting Ability(Traditional Lenses)}
-%     \label{table-adapt}
-% \end{figure}
+\begin{figure}[!t]
+    \centering
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+    \hfill
+    \caption{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
+    \label{fig:adapting}
+\end{figure}
 
@@
 The results are shown in Figure~\ref{table-comp}.
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
-%     \caption{Comparison with other architectures}
-%     \label{table-comp}
-% \end{figure}
-
 \begin{table}[!t]
@@
         \toprule
-    System & Home & Transport & Theater \\ \midrule
+    Scenarios & Home & Transport & Theater \\ \midrule
     Baseline & 5 & 0 & 0\\ 
@@
 \end{table}
-
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
-%     \caption{Accuracy in different real-life scenarios}
-% 	\label{table-accuracy}
-% \end{figure}
 
@@
         \toprule
-    System & None & Camera & Target & Both  \\
+    Items & None & Camera & Target & Both  \\
     \midrule
@@
 
-% \begin{figure}
-%  \centering
-%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
-% \caption{Influence of hand tremors}
-% \label{table-tremor}
-% \end{figure}
-
 We conclude from the results that hand tremors can impact the performance of our system.
 Although the edges of the phone are notable marks for image alignment, small shifts in the sub-pixel level will cause blurriness in the results of the networks, lowering the readability of the outputs.
+
+\begin{figure}[!t]
+    \centering
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \hfill
+    \caption{Performance with various processing images using Traditional Lens and Optical Lens.}
+    \label{fig:adapting}
+\end{figure}
 

### 2020-07-01 abstract.tex
evaluation

@@
 With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
-To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.
-We implement SPPeek in Android.
+To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.
+We implement \textsf{SPPeek} in Android.
 The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses.

### 2020-07-01 abstract.tex
intro

--- 2020-07-01 abstract.tex
@@
 To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
-To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.
-We implement SPPeek in Android.
-The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses.
+With the development of smartphones and super resolution (SR) techniques, a malicious attacker can peek from further away with the assist of the smartphone camera and SR algorithms, rendering the underestimated shoulder surfing threat model.
+To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) for multi-image SR.
+We implement SPPeek in Android and conduct comprehensive experiments in controlled and real life scenarios.
+Evaluations demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses.
 And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.

### 2020-07-01 introduction.tex
intro

@@
 
-The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years.
+The privacy concerns however have been exacerbated with the rapidly developed mobile camera module these years.
 Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
 Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second.
+Given the commercial smartphone, the attacker can record the information reliably for propagating.
 And more images mean more recorded information of the victim.
-Given the commercial smartphone, the attacker can record the information reliably for propagating.
 For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
@@
 
-Unfortunately, none of existing work can mitigate the new threat model.
-Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}.
-All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios.
+Unfortunately, none of existing work can mitigate this new threat model.
+Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}.
+All of these methods however require the additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios.
 Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios.
-Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
+Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new threat model and propose corresponding countermeasure for modern circumstances.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{pic/illustration.pdf}
+	\includegraphics[width=0.48\textwidth]{pic/illustration.pdf}
     \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
@@
 \textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
-While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone, zooms in on the victim's screen, takes 10 to 20 snapshots rapidly in burst mode(about 10 frames per second), and process them with a multi-frame SR system to generate a high-res result.
-The whole process takes only a few seconds and can even be repeated at a 2 second interval to give the attacker a continuous surveillance over the victim's screen, not missing any detail, while at the same time, few people would suspect a stranger holding his smartphone at 1.8 meters behind them.
-With the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can be raised to a staggering 6 meters, posing a silent but deadly threat to screen privacy.
+While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone and zooms in on the victim's screen.
+Then he can take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and process them with a multi-frame SR technique to generate a high-resolution result.
+The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously, not missing any detail.
+Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them.
+Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.
 
@@
 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
-%     \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera.
-All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
-% 	\label{illustration_of_system}
-% \end{figure}
-
 \begin{itemize}[leftmargin=*]
@@
 It can be further exacerbated by straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''.
+Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts as Figure~\ref{illustration_of_system} shows, requiring a reliable ``reconstruction'' than ``interpolation''.
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
-  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.
+  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-resolution images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects.
 As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two.
-  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames, shown in Figure~\ref{illustration_of_system}.
-Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for interigation abilities of the SR algorithms than most other SR applications.
+  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames.
+Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle.
+Thus it poses a greater demand for integration abilities of the SR algorithms than most other SR applications.
   % and the only chance of recovering the ground truth is to compare each photo against others. 
 %  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}.
-  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents.
+  \item \textbf{Super resolution with multiple snapshots.} To resolve the blurriness of input snapshots, a SR algorithm on a smartphone is required to recover the blurred contents.
 However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input.
 Since smartphones can capture 10 snapshots per second in burst mode.
-Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cite{lucas2019generative} \cite{kappeler2016video}.
+Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms~\cite{lucas2019generative,kappeler2016video}.
 The reason has two folds.
-First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment.
-Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process.
+First, massive input leads to the increase in model complexity, making it unsuitable for mobile deployment.
+Second, the nature of our task requires to do pixel-wise correlation and comparison in the same coordinate with consecutive snapshots throughout our construction process.
 Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.
   \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server.
-Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwidth.
-Given the required 10 to 20 images to process for ideal content recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM.
-In cases where the display on the target screen changes more frequently, less images and processing time are available for each scene.
-Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 images.
-  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct multi-type texts, including Chinese characters, English letters, and numbers.
-Composed of multiple strokes, characters are distributed discretely in the pixel-wise image and different with other entities (e.g., faces and natural objects), rendering unique challenges.
+Since 1) the latter requires a stable internet access, and 2) sending multiple snapshots across the Internet will consume time and bandwidth.
+Given the required 10 to 20 snapshots to be processed for the ideal content recovery, we have 1-2 seconds as the minimum interval between each output frame, rendering a limited period for calculation with the restricted power and RAM.
+In case where the display on the target screen changes more frequently, fewer snapshots and less processing time are available for each scene.
+Consequently, it cannot only require a more precise network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 snapshots.
+  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct complex characters with multiple strokes, such as Chinese characters shown in Figure~\ref{illustration_of_system}.
+Composed of multiple strokes, characters are distributed discretely in the pixel-wise snapshot and different with other entities (e.g., faces and natural objects), rendering unique challenges.
 In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings.
@@
 \textbf{Summary of Evaluation Results.}
-Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings.
-The system is able to capture snapshots and produce high-res images constantly with about 2 seconds interval.
-Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.
+Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming, or 6m on a phone with optical zooming in our experimental settings.
+\textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval.
+Our experiments in real life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.
 
@@
 \begin{itemize}[leftmargin=*]
-  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range.
+  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones.
 To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
-  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots.
-It can be further extended to other text-recognition applications on commercial smartphones.
-  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
+  \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
+  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
 \end{itemize}

### 2020-07-01 abstract.tex

--- 2020-07-01 abstract.tex
@@
 To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
+With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
 To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.

### 2020-07-01 evaluation.tex

@@
-\section{Evaluation \& Case Study}
+\section{Evaluation and Case Study}
 \label{sec-evaluation}
@@
 % \end{figure*}
-We evaluate the ability of the network model, testing its performance in different training and testing conditions.
-We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments.
-\subsection{Performance In Controlled Environment}
-We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}).
-Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
-The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms.
-The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
-Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
+We evaluate the performance of the network model in different training and testing conditions.
+We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
+The telephoto camera possesss up to 5x optical zooming ability which we will utilize fully in our experiments.
+
 \begin{figure}[!t]
     \centering
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
     \hfill
@@
 
-In the optical zoom group the accuracy of the model dropped drastically at 7m distance.
-Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.).
-It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.
+\subsection{Performance In Controlled Environment}
+In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images.
+The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}.
+Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
+The model with traditional lenses (without optical zoom) is trained and tested at 1-2 meters range, while the one with optical zoom at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+
+From Figure~\ref{fig-control-1}, we can see the model can achieve an OCR accuracy above 90\% at 1.8m with traditional lenses in both day and night time.
+The PSNR is higher than 10 as well.
+The OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs.
+For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical zooming lenses.
+The performance is relatively consistent in both day and night time.
+Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
+
+In the optical zoom group, the accuracy of the model dropped drastically at 7m distance.
+Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes, etc.).
+It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.
 
 \subsection{Performance In Random Environment}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}).
-The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.
+We train the model with data captured in different environments, as mentioned before, and test its ability in other environments.
+The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}.
+For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lenses.
+From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical zooming lenses.
+This verifies the efficiency of our model for environment adaption.
+
 \begin{figure}[!t]
     \centering
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
     \hfill
@@
 \subsection{Adapting Ability}
-We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
-The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
+We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments.
+The results are shown in Figure~\ref{fig-adapt-tranditional}.
+Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
 \begin{figure}[!t]

### 2020-07-01 related_work.tex
intro

@@
 \begin{table}[t]
-  \caption{A comparison of state-of-the-art works on shoulder surfing.}
+  \caption{A comparison of the state-of-the-arts on shoulder surfing.}
   \vspace{2mm}
@@
   \hline
-   Reference & Equipment & Training & distance$^{\mathrm{a}}$ \\
+   Reference & Scenarios & Training & distance$^{\mathrm{a}}$ \\
   \hline
-  Eiband~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
-  Kwon~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
-Schaub~\cite{schaub2012password} & naked eye & untrained & Intimate\\
-  Maggi~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
+  Eiband et al.~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
+  Kwon et al.~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
+Schaub et al.~\cite{schaub2012password} & naked eye & untrained & Intimate\\
+  Maggi et al.~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
   \hline
   \hline
-  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 6 meter\\
+  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 1.8 / 6 meter\\
   \hline
@@
 It can however only function when the attacker is standing at close range, which is a barely practical scenario.
-By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.5m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
+By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
 Evaluations demonstrate its feasibility and privacy concerns in our daily life.

### 2020-07-01 evaluation.tex
intro

@@
 
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
-    \hfill
-    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
-    \label{fig:control}
-\end{figure}
-
-\subsection{Performance In Controlled Environment}
+\subsection{Performance In Controlled Environments}
 In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images.
@@
 Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+    \hfill
+    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
+    \label{fig:control}
+\end{figure}
 
@@
 
-\subsection{Performance In Random Environment}
+\subsection{Performance In Random Environments}
 We train the model with data captured in different environments, as mentioned before, and test its ability in other environments.

### 2020-07-01 evaluation.tex
evaluation

--- 2020-07-01 evaluation.tex
@@
 We train and test other commonly used architectures with the same sets of data and evaluate their results.
-We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing.
+We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average.
 We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR).
-However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results.
+However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results.
 We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing.
-The results are shown in Figure~\ref{table-comp}.
+The results are shown in Table~\ref{table-comp}.
 \begin{table}[!t]
     \centering
+    \caption{Comparison with existing systems.}
     \begin{tabular}{@{}cccc@{}}
@@
     \end{tabular}
-    \caption{Comparison with existing systems.}
     \label{table-comp}
 \end{table}
+
+We can see that the PSNR of SRPeek is 13.32dB which 73.2\% and 58.6\% larger than that of SRCNN and VideoSR.
+For the OCR accuracy, SRPeek can recognize all characters, but SRCNN and VideoSR can only recognize 10\% and 23\% of them.
+The results show the efficiency of our SR model in comparison with existing models.
 
@@
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
-As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range.
+As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1-2m range.
 We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model.
 No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty.
-The results are shown in Figure~\ref{table-scenarios}.
+The results are shown in Table~\ref{table-scenarios}.
+
+The results show that Human can read 95\%, 85\% and 70\% contents in home, transport and theater while the OCR accuracy is 100\%, 10\% and 23\%.
+That verifies human can obtain the most parts of informations from the peeking in various environments.
+In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads lower accuracy in transport and theater.
 
@@
     \centering
+    \caption{Recognition accuracy in various scenarios.}
     \begin{tabular}{@{}cccc@{}}
@@
     \end{tabular}
-    \caption{Recognition accuracy in various scenarios.}
     \label{table-scenarios}
@@
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Figure~\ref{table-tremor}.
+We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Table~\ref{table-tremor}.
 
@@
     \centering
+    \caption{Impact of hand tremors while holding various items.}
     \begin{tabular}{ccccc}
@@
     \end{tabular}
-    \caption{Impact of hand tremors while holding various items.}
     \label{table-tremor}
@@
 
+We can see when tremors happen, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human.
 We conclude from the results that hand tremors can impact the performance of our system.
@@
     \centering
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
     \hfill

### 2020-07-01 evaluation.tex
evaluation

@@
 The results are shown in Figure~\ref{fig-adapt-tranditional}.
-Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.
+
 \begin{figure}[!t]
     \centering
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
     \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
     \hfill
-    \caption{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
+    \caption[Optical Lens]{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
     \label{fig:adapting}
@@
 The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone.
-For the first two tasks,we ask the observing participant several questions to test if he/she have collected the vital information(e.g.
+For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information(e.g.
 the name or the location mentioned in the text).
@@
 In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible.
-Less photos will be avaliable for each character but decifering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same nerual network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
+Less photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
 The results are shown in Table~\ref{table-task}.

### 2020-07-01 evaluation.tex
后两部分

@@
-\section{Evaluation and Case Study}
+\section{Model Evaluation}
 \label{sec-evaluation}
@@
 Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
-The model with traditional lenses (without optical zoom) is trained and tested at 1-2 meters range, while the one with optical zoom at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+The model with traditional lens without optical zoom(hereafter refered as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom(hereafter refered as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+The PSNR and OCR results are shown in Fig.
+~\ref{fig-control-1}.
 
-From Figure~\ref{fig-control-1}, we can see the model can achieve an OCR accuracy above 90\% at 1.8m with traditional lenses in both day and night time.
+This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens in both day and night time.
 The PSNR is higher than 10 as well.
-The OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs.
-For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical zooming lenses.
+OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs.
+For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical lens.
 The performance is relatively consistent in both day and night time.
@@
 The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}.
-For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lenses.
-From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical zooming lenses.
+For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens.
+From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens.
 This verifies the efficiency of our model for environment adaption.
@@
 
+\subsection{Performance with fewer avaliable images}
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \hfill
+    \caption{Performance with fewer avaliable images using Traditional Lens and Optical Lens.}
+    \label{fig:number}
+\end{figure}
+As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene.
+This design is requisite because in certain scenraios the data displayed on the victim's screen is transient and ever-changing, e.g.
+password entry, where only the last character of the password is visible.
+We evaluated the impact of fewer avaliable images to the performance of the SR model.
+The results are shown in fig.~\ref{fig:number}.
+We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.
+
+In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is avaliable to rule out all possibilities of the displayed characters.
+The optical lens group displayed a steady decent of accuracy when fewer images are avaliable, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
+
 \subsection{Adapting Ability}
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments.
-The results are shown in Figure~\ref{fig-adapt-tranditional}.
+The results are shown in Figure~\ref{fig:adapting}.
 
@@
 However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results.
-We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing.
+We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing.
 The results are shown in Table~\ref{table-comp}.
@@
 % \section{System Evaluation}
+\section{Case Study}
 \subsection{Accuracy}
@@
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
-As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1-2m range.
+As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range.
 We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model.
@@
     \centering
-    \caption{Impact of hand tremors while holding various items.}
+    \caption{Impact of hand tremors when the camera(attacker phone) and/or target(victim phone) is handheld.}
     \begin{tabular}{ccccc}
@@
 
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
-    \hfill
-    \caption{Performance with various processing images using Traditional Lens and Optical Lens.}
-    \label{fig:adapting}
-\end{figure}
-
 \subsection{Success rate in different tasks}
@@
 In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible.
-Less photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
+Fewer photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
 The results are shown in Table~\ref{table-task}.
@@
 \centering
+\caption{Success rate in different tasks.}
+\label{table-task}
 \begin{tabular}{@{}ccccc@{}}
@@
 \end{tabular}
-\caption{Success rate in different tasks.}
-\label{table-task}
+
 \end{table}
@@
 We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario.
-The attacker will be sitting or standing behind the participant at 1.5m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.
+The attacker will be sitting or standing behind the participant at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.
 None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing.

### 2020-07-01 implementation.tex
fig
后两部分

--- 2020-06-30 implementation.tex
@@
 Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{pic/setup.pdf}
+    \caption{Illustration of our experimental setting (Distance between phones are shortened for demonstration).}
+	\label{illustration_of_system}
+\end{figure}
+% \begin{figure}
+%   \centering
+%      \centering
+%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
+%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
+%          \label{fig-exp1}
+%          }
+%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
+%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
+%          \label{fig-exp2}
+%          }
+%    \subfigure[screenshot from victim's phone.]{
+%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
+%          \label{fig-exp3}
+%          }
+%      \caption{Illustration of our experimental setting.}
+%      \label{fig-experiment}
+% \end{figure}
 
@@
 This phenomenon can be mitigated with dropout and normalization layers.
-As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 2.0m and 1.5m range in the training process, the model fits 1.75m photos easily.
+As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 1.8m and 1.2m range in the training process, the model fits 1.5m photos easily.
 After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.

### 2020-07-02 evaluation.tex
添加reallife image

@@
 We observed that variations in light and angle parameter in training data is crucial to a robust model.
-Variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
+In the tradition lens group, variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
 Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size.
 However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process.
+The optical lens group yields similar results except the distance group.
+As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
 
@@
 \section{Case Study}
+\label{case-study}
 \subsection{Accuracy}
-We build the system on smartphone and evaluate its performance in real-life environments.
+
+We build the system on smartphone and evaluate its performance in real-life environments(shown in Fig.~\ref{fig-reallife}).
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
@@
 The results are shown in Table~\ref{table-scenarios}.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{pic/reallife.jpg}
+    \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
+	\label{fig-reallife}
+\end{figure}
 

### 2020-07-02 implementation.tex
添加reallife image

@@
 Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
+An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
 \begin{figure}
@@
 	\includegraphics[width=0.48\textwidth]{pic/setup.pdf}
-    \caption{Illustration of our experimental setting (Distance between phones are shortened for demonstration).}
+    \caption{Illustration of our experimental setting (Distance between phones is shortened for demonstration).}
 	\label{illustration_of_system}

### 2020-07-02 introduction.tex
intro
添加reallife image

@@
   \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
-  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
+  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for content recognition, calling for the new privacy concern.
 \end{itemize}
@@
 
+\vspace{1mm}
 The rest of the paper is organized as follows.
 Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing and SR techniques.
-We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}.
+We present the system and network design in Section ~\ref{sec-system-overview} and ~\ref{sec-design}, followed by the implementation in Section~\ref{sec-implementation-and-training} and evaluation in Section ~\ref{sec-evaluation} and ~\ref{case-study}.
 We further wrap up this paper by delivering the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}.

### 2020-07-02 system_overview.tex
fig
添加reallife image

@@
 \textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
-Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
+Note that zooming is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
 This way information on the images will be more compact and easier to comprehend by neural networks.
@@
 \textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
-The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).
+The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of the camera lens in the Input phase will be adjusted accordingly).
 
@@
 \noindent
-\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together.
-After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling).
+\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo with our multi-frame super resolution network to generate 36x36 images (4x upscaling).
 The input is RGB colored, while the output, as we are not interested in color, is black and white.
-When all patches are processed, their outputs are merged together.
+In this way, we generate upscaled image segments of all the characters on the target screen.
+The three calculation process(Alignment, Adjustment, Processing) runs parallel to the input process, so that once a batch of input images is avaliable, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
+
+\vspace{1mm}
+\noindent
+\textbf{Output:} The outputs of our SR network, the 36x36 patches, are then merged into a whole.
 The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
-In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.
+As we only carve out the texts on the phone and process them, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker(An illustration can be found in Fig.~\ref{illustration_of_system}).
 
@@
   \centering
-     \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
-     \caption{Illustration of the workflow of our shoulder-surfing system.}
+     \includegraphics[width=0.48\textwidth]{./pic/workflow_cl.pdf}
+     \caption{Illustration of the workflow of \textsf{SRPeek}.}
      \label{fig-workflow}

### 2020-07-02 conclusion.tex
fix typos

@@
 We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection.
-It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps.
+It is our wish that this work can stir discussion in the field of screen privacy protection and propagate defense mechanisms across critical mobile apps.
 
@@
 The design ideology enables this network to process higher levels of data integration ability while keeping a low calculation profile, and we believe the elements of this design can be used in other applications with large amounts of data, such as natural language processing or anomaly detection.
-Our model can also be used in OCR tasks when multiple images are avaliable, functioning as a preprocessor to improve the quality of the images and increase accuracy.
+Our model can also be used in OCR tasks when multiple images are available, functioning as a preprocessor to improve the quality of the images and increase accuracy.

### 2020-07-02 design.tex
fix typos

@@
 All input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
-Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
+Another important feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
     \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution.
 At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
-    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
-This trait also enables the  the same network to adapt any number of input images.
-On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
-    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results.
+    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are performed individually for each image (or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
+This trait also enables the same network to adapt any number of input images.
+On one hand, this gives our model the ability to adapt to the uncertainty of the number of available images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
+    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results.
 The frequent introduction of input images is designed to mitigate this challenge.
 Also, our model can learn correlations between certain features and strokes from the training data, decomposing the SR problem and making it a lot less challenging.
-We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data.
+We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalances of data.
 The loss functions in training is also redesigned.
-The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
+The mean square error (MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
 Our solution is putting a weight on each pixel before applying weighted MSE.
-Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights.
+Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights.
 This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests.
@@
 Presently, in these layers nothing is done to raise the resolution of the images, so that the resolution of $x_i^{(0)}$ to $x_i^{(l-1)}$ and $y$ remains the same.
-To increase resolution we insert several 2$\times$ nearest upsampling layers $U$ evenly throughout the architecture between the layers:
+To increase resolution, we insert several 2$\times$ nearest upsampling layers $U$ evenly throughout the architecture between the layers:
 \begin{equation}\label{eq:3}
@@
 \textbf{Conv1:} The first convolutional layer, $Conv1$, accepts the layer's first input parameter $x_i^{(l-1)}$ as input.
-Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):
+Note that all three convolutional layers accept a single image (or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):
 \begin{equation}\label{eq:4}
@@
 
-The full structure of a 3 layer network is shown in Figure~\ref{fig-system}.
+The full structure of a 3-layer network is shown in Figure~\ref{fig-system}.
 
@@
 % \textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
-Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
+Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if available, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
 This way information on the images will be more compact and easier to comprehend by neural networks.
@@
 % \noindent
-% \textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+% \textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will occasionally shift slightly across time due to the movements of its inner mechanism.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
-In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.
+In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images (roughly upscaled to encompass them, just for reference) and displayed to the attacker.
 

### 2020-07-02 evaluation.tex
fix typos

@@
 We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
-The telephoto camera possesss up to 5x optical zooming ability which we will utilize fully in our experiments.
+The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.
 
@@
 The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}.
-Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy.
-The model with traditional lens without optical zoom(hereafter refered as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom(hereafter refered as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition (OCR) services to evaluate the accuracy.
+The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
 The PSNR and OCR results are shown in Fig.
@@
 In the optical zoom group, the accuracy of the model dropped drastically at 7m distance.
-Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes, etc.).
+Increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.).
 It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.
@@
 
-\subsection{Performance with fewer avaliable images}
+\subsection{Performance with fewer available images}
 \begin{figure}[!t]
@@
     \hfill
-    \caption{Performance with fewer avaliable images using Traditional Lens and Optical Lens.}
+    \caption{Performance with fewer available images using Traditional Lens and Optical Lens.}
     \label{fig:number}
@@
 As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene.
-This design is requisite because in certain scenraios the data displayed on the victim's screen is transient and ever-changing, e.g.
+This design is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g.
 password entry, where only the last character of the password is visible.
-We evaluated the impact of fewer avaliable images to the performance of the SR model.
+We evaluated the impact of fewer available images to the performance of the SR model.
 The results are shown in fig.~\ref{fig:number}.
@@
 
-In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is avaliable to rule out all possibilities of the displayed characters.
-The optical lens group displayed a steady decent of accuracy when fewer images are avaliable, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
+In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is available to rule out all possibilities of the displayed characters.
+The optical lens group displayed a steady decent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
 
@@
 We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average.
-We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR).
+We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR).
 However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results.
@@
 
-We build the system on smartphone and evaluate its performance in real-life environments(shown in Fig.~\ref{fig-reallife}).
+We build the system on smartphone and evaluate its performance in real-life environments (shown in Fig.~\ref{fig-reallife}).
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
@@
 The results show that Human can read 95\%, 85\% and 70\% contents in home, transport and theater while the OCR accuracy is 100\%, 10\% and 23\%.
-That verifies human can obtain the most parts of informations from the peeking in various environments.
+That verifies human can obtain the most parts of information from the peeking in various environments.
 In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads lower accuracy in transport and theater.
@@
 \subsection{Influence of hand tremors}
-We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort(Handheld camera).
+We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort (Handheld camera).
 We process these images and let them read the results.
 We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
-We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions(Handheld target).
+We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions (Handheld target).
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Table~\ref{table-tremor}.
+We capture images of the phone at the same time to see how our system deal with a moving target screen.
+The results are shown in Table~\ref{table-tremor}.
 
@@
 
-We can see when tremors happen, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human.
+We can see that with the existence of tremors, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human.
 We conclude from the results that hand tremors can impact the performance of our system.
@@
 \subsection{Success rate in different tasks}
-We test the success rate of obtaining crucial information when the observed participant perform several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters.
+We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters.
 The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone.
-For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information(e.g.
+For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information (e.g.
 the name or the location mentioned in the text).
@@
 In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible.
-Fewer photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario).
+Fewer photos will be available for each character but deciphering English characters is also easier than Chinese characters, and we trained a model specifically for each task (with the same neural network architecture), the training images containing only English characters and numbers (or only numbers for the PIN entry scenario).
 The results are shown in Table~\ref{table-task}.
@@
 \subsection{Perceived shoulder surfing susceptibility}
-We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario.
+We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenarios.
 The attacker will be sitting or standing behind the participant at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.

### 2020-07-02 implementation.tex
fix typos

@@
 When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours).
-There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data.
+There is no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data.
 %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
@@
 Our experiment consists of 2 smartphones, one for the attacker and one the victim.
-Their distance is between 1 and 2 meters for traditional lenses(for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming.
+Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming.
 Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation.

### 2020-07-02 introduction.tex
fix typos

@@
   On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames.
-Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle.
-Thus it poses a greater demand for integration abilities of the SR algorithms than most other SR applications.
+Thus, it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for integration abilities of the SR algorithms than most other SR applications.
   % and the only chance of recovering the ground truth is to compare each photo against others. 

### 2020-07-02 limitation_and_discussion.tex
后两部分
fix typos

@@
 \label{sec-limitations-and-discussions}
-
+There are certain limitations of this work.
+We require a certain degree of image capturing and processing abilities of the attacker's phone, and we also expect the victim not to exert too much disturbance to the target phone.
 \vspace{1mm}
@@
 Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old.
-Heavily used phones also performs less than ideal when capturing images in burst mode.
-Also, when capturing images the user need to hold their phone as still as possible to avoid motion blur and assist image alignment.
+Heavily used phones also perform less than ideal when capturing images in burst mode.
+Also, when capturing images, the user needs to hold their phone as still as possible to avoid motion blur and assist image alignment.
 The user also has to keep a sharp focus on the target phone.
@@
 In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often.
-However some users may tilt their phones during interactions—especially when typing with one hand.
+However, some users may tilt their phones during interactions---especially when typing with one hand.
 Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.
@@
 By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influential elements cannot be easily removed.
-These dots do not need to be distinct or colored same as the the texts, as multi-frame SR algorithms function with tiny,pixel level differences between frames, making them especially sensitive to microscopic changes.
+These dots do not need to be distinct or colored same as the texts, as multi-frame SR algorithms function with tiny, pixel level differences between frames, making them especially sensitive to microscopic changes.
 
@@
 \textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network.
-These methods fools the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
+These methods fool the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
 Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remains to be implemented in our future work.

### 2020-07-02 related_work.tex
fix typos

@@
 To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input.
-Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
+Then the sequentially and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
 % modifying the 2d convolution layers to 3d convolution~\cite{caballero2017real}, 
@@
 They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}.
-Due of the extreme blurriness of snapshots, these methods can not deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.
+Due of the extreme blurriness of snapshots, these methods cannot deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.
 And they achieve limited performance, shown in Table~\ref{tbl:comparison}.

### 2020-07-02 system_overview.tex
fix typos

@@
 \textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
-Note that zooming is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
+Note that zooming is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if available, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
 This way information on the images will be more compact and easier to comprehend by neural networks.
@@
 \noindent
-\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism.
+\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will occasionally shift slightly across time due to the movements of its inner mechanism.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 \textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
-The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of the camera lens in the Input phase will be adjusted accordingly).
+The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size (and the zooming of the camera lens in the Input phase will be adjusted accordingly).
 
@@
 In this way, we generate upscaled image segments of all the characters on the target screen.
-The three calculation process(Alignment, Adjustment, Processing) runs parallel to the input process, so that once a batch of input images is avaliable, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
+The three calculation processes (Alignment, Adjustment, Processing) runs parallel to the input process, so that once a batch of input images is available, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
 
@@
 The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
-As we only carve out the texts on the phone and process them, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker(An illustration can be found in Fig.~\ref{illustration_of_system}).
+As we only carve out the texts on the phone and process them, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration can be found in Fig.~\ref{illustration_of_system}).
 

### 2020-07-02 related_work.tex
temp

@@
   \begin{center}
-  \begin{tabular}{cccc}
+  \begin{tabular}{ccccc}
   \hline
-   Reference & Scenarios & Training & distance$^{\mathrm{a}}$ \\
+   Reference & Scenarios   & Accuracy & \begin{tabular}[c]{@{}l@{}}Quantitative \\ Model\end{tabular}& Distance$^{\mathrm{a}}$ \\
   \hline
-  Eiband et al.~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
-  Kwon et al.~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
-Schaub et al.~\cite{schaub2012password} & naked eye & untrained & Intimate\\
-  Maggi et al.~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
+  Eiband et al.~\cite{eiband2017understanding}  & naked eye & no & no & 1 meter \\
+  Kwon et al.~\cite{kwon2013covert}  & naked eye & no & no &-$^{\mathrm{b}}$\\
+Schaub et al.~\cite{schaub2012password} & naked eye & no & no & -\\
+  Maggi et al.~\cite{maggi2011poster}  & camera & yes  & no &- \\
   \hline
   \hline
-  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 1.8 / 6 meter\\
+  \textbf{\textsf{SRPeek}} & COTS phones & yes & yes  & 1.8 / 6 meter\\
   \hline
-  \multicolumn{4}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\
+  \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\
 
-  \multicolumn{4}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
+  \multicolumn{5}{l}{$^{\mathrm{b}}$Distance is uncontrolled; The attacker stands next to or behind the victim.}\\
   \end{tabular}

### 2020-07-02 evaluation.tex
change reallife fig

@@
     System & SRPeek & SRCNN & VideoSR \\ \midrule
-    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
-    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
+    PSNR & 13.32db & 7.69db & 8.403db\\ 
+    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
     \end{tabular}
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/reallife.jpg}
+	\includegraphics[width=0.46\textwidth]{pic/reallife.pdf}
     \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
@@
     Scenarios & Home & Transport & Theater \\ \midrule
-    Baseline & 5 & 0 & 0\\ 
+    Baseline & 5\% & 0 & 0\\ 
     \midrule
-    OCR & 100 & 10 & 23\\ 
-    Human & 95 & 85 & 70\\ \bottomrule
+    OCR & 100\% & 10\% & 23\%\\ 
+    Human & 95\% & 85\% & 70\%\\ \bottomrule
     \end{tabular}
@@
     \centering
-    \caption{Impact of hand tremors when the camera(attacker phone) and/or target(victim phone) is handheld.}
+    \caption{Impact of hand tremors when the camera (attacker phone) and/or target (victim phone) is handheld.}
     \begin{tabular}{ccccc}
         \toprule
-    Items & None & Camera & Target & Both  \\
+    Accuracy & None & Camera & Target & Both  \\
     \midrule
-    Baseline & 5 & 0 & 5& 5\\ 
+    Baseline & 5\% & 0 & 5\% & 5\%\\ 
     \midrule
-    OCR & 95 & 85 & 80 & 80\\ 
-    Human & 95 & 85 & 80 & 85\\ \bottomrule
+    OCR & 95\% & 85\% & 80\% & 80\%\\ 
+    Human & 95\% & 85\% & 80\% & 85\%\\ \bottomrule
     \end{tabular}
@@
 Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
-Raw Image & 5 & 0 & 0 & 0\\
-SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
+Raw Image & 5\% & 0 & 0 & 0\\
+SRPeek & 100\% & 100\% & 100\% & 80\%\\ \bottomrule
 \end{tabular}

### 2020-07-02 evaluation.tex
table 1

@@
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
     \hfill
@@
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
     \hfill
@@
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
-    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+    \subfigure{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
     \hfill

### 2020-07-02 related_work.tex
table 1

--- 2020-07-02 related_work.tex
@@
   \begin{center}
-  \begin{tabular}{cccc}
+  \begin{tabular}{ccccc}
   \hline
-   Reference & Scenarios & Training & distance$^{\mathrm{a}}$ \\
+   Reference & Scenarios   & Metric & \begin{tabular}[c]{@{}l@{}}Quantitative \\ Model\end{tabular}& Distance$^{\mathrm{a}}$ \\
   \hline
-  Eiband et al.~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
-  Kwon et al.~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
-Schaub et al.~\cite{schaub2012password} & naked eye & untrained & Intimate\\
-  Maggi et al.~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
+  Eiband~\cite{eiband2017understanding}  & Naked eye & $\times$ & $\times$ & 1m \\
+  Kwon~\cite{kwon2013covert}  & Naked eye & $\times$ & $\times$ &-$^{\mathrm{b}}$\\
+Schaub~\cite{schaub2012password} & Naked eye & \cmark & $\times$ & -\\
+  Maggi~\cite{maggi2011poster}  & Camera & \cmark  & $\times$ &- \\
   \hline
   \hline
-  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 1.8 / 6 meter\\
+  \textbf{\textsf{SRPeek}} & COTS phones & \cmark & \cmark  & 1.8 / 6m\\
   \hline
-  \multicolumn{4}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\
+  \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen. $^{\mathrm{b}}$The attacker stands}\\
 
-  \multicolumn{4}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
+  \multicolumn{5}{l}{next to the victim without the maximum effective distance.}\\
   \end{tabular}

### 2020-07-02 design.tex
change reallife fig
cl

@@
 
-\begin{itemize}[leftmargin=*]
+\begin{itemize}
     \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
@@
 
-Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$.
+Illustrated in Figure~\ref{fig-system}, inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$.
 
@@
        \includegraphics[width=0.5\textwidth]{./pic/network.pdf}
-       \caption{Network Architecture of SRPeek.}
+       \caption{Core network architecture of SRPeek.}
        \label{fig-system}
@@
 
-The full structure of a 3-layer network is shown in Figure~\ref{fig-system}.
-
 % \subsection{Design Principal}

### 2020-07-02 evaluation.tex
cl

@@
 \subsection{Performance In Controlled Environments}
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+    \hfill
+    \caption{Performance in the controlled environment using traditional lens and optical lens.}
+    \label{fig:control}
+\end{figure}
+
 In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images.
@@
 Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
-    \hfill
-    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
-    \label{fig:control}
-\end{figure}
 
@@
 \subsection{Performance In Random Environments}
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \hfill
+    \caption{Performance in the random environment using traditional lens and optical Lens.}
+    \label{fig:control}
+\end{figure}
+
 We train the model with data captured in different environments, as mentioned before, and test its ability in other environments.
@@
 This verifies the efficiency of our model for environment adaption.
-
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
-    \hfill
-    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
-    \label{fig:control}
-\end{figure}
 
@@
     \hfill
-    \caption{Performance with fewer available images using Traditional Lens and Optical Lens.}
+    \caption{Performance with fewer available images using traditional lens and optical lens.}
     \label{fig:number}
@@
     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
-    \subfigure{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
     \hfill
-    \caption[Optical Lens]{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
+    \caption{Performance for the adapting ability using traditional lens and optical lens.}
     \label{fig:adapting}

### 2020-07-02 related_work.tex
related work

@@
   \hline
-  Eiband~\cite{eiband2017understanding}  & Naked eye & $\times$ & $\times$ & 1m \\
-  Kwon~\cite{kwon2013covert}  & Naked eye & $\times$ & $\times$ &-$^{\mathrm{b}}$\\
-Schaub~\cite{schaub2012password} & Naked eye & \cmark & $\times$ & -\\
-  Maggi~\cite{maggi2011poster}  & Camera & \cmark  & $\times$ &- \\
+  Eiband~\cite{eiband2017understanding}  & Naked eye & $\times$ & $\times$ & - \\
+  Kwon~\cite{kwon2013covert}  & Naked eye & \cmark & $\times$ &1m \\
+Schaub~\cite{schaub2012password} & Naked eye & \cmark & $\times$ & -$^{\mathrm{b}}$\\
+  Maggi~\cite{maggi2011poster}  & Camera & \cmark  & $\times$ &-$^{\mathrm{b}}$ \\
   \hline
@@
 Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
-To deal with the threat model of tool-assisted shoulder surfing,%\cl{more citation and table 1 row-2},
-% Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password} 
-Maggi et al.
+
+However, compared to the various works focusing on defenses against shoulder surfing, the works studying and modelling this threat is sparse and outdated.
+Most of these works focus on scenarios where the attacker peeks at the phone with his/hers naked eye, performing experiments or conducting surveys to research this threat.
+Eiband et al.~\cite{eiband2017understanding} conducted a user survey to investigate stories of shoulder surfing; Kwon et al.~\cite{kwon2013covert} designed a shoulder surfing approach called covert attentional shoulder surfing, and evaluated its success rates against PIN entry scenarios, presenting a powerful shoulder surfing threat model with the naked eye; and Schaub et al.~\cite{schaub2012password} evaluated shoulder surfing susceptibility, using Levenshtein distances and 7-point Likert scales to evaluate the accuracy and difficulties of shoulder surfing on different virtual keyboards.
+These works, however, lack quantitive modelling of this privacy threat, such as controlling the distances, illumination, angle, etc.
+to evaluate the vulnerability of screen privacy in different scenarios; and these works all focus on the unequipped attacker, so that their attack range is within 1 meter or even closer (where the attacker stands right behind or next to the victim), which is a barely practical scenario.
+
+To deal with the threat model of tool-assisted shoulder surfing, Maggi et al.
 designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}.
-It can however only function when the attacker is standing at close range, which is a barely practical scenario.
+However, the system contains only recognition algorithms, lacking SR processors to enhance the quality of the image, so that it can only function when the attacker is standing at close range.
 By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
 Evaluations demonstrate its feasibility and privacy concerns in our daily life.
+We also performed thorough evaluations of our threat model, measuring its abilities with various environment parameters.
+To the best of our knowledge, we are the first work to design and model the new form of shoulder surfing attack with the assistance of smartphones and multi-frame SR algorithms.
 

### 2020-07-02 evaluation.tex
cl

@@
 \subsection{Performance In Random Environments}
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
-    \hfill
-    \caption{Performance in the random environment using traditional lens and optical Lens.}
-    \label{fig:control}
-\end{figure}
-
 We train the model with data captured in different environments, as mentioned before, and test its ability in other environments.
@@
 Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \hfill
+    \caption{Performance in the random environment using traditional lens and optical Lens.}
+    \label{fig:control}
+\end{figure}
 
@@
 \subsection{Performance with fewer available images}
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
-    \hfill
-    \caption{Performance with fewer available images using traditional lens and optical lens.}
-    \label{fig:number}
-\end{figure}
 As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene.
@@
 The optical lens group displayed a steady decent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
+\begin{figure}[!t]
+    \centering
+    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \hfill
+    \caption{Performance with fewer available images using traditional lens and optical lens.}
+    \label{fig:number}
+\end{figure}
 
@@
 
+We observed that variations in light and angle parameter in training data is crucial to a robust model.
+In the tradition lens group, variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
+Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size.
+However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process.
+The optical lens group yields similar results except the distance group.
+As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
 \begin{figure}[!t]
@@
 \end{figure}
-
-We observed that variations in light and angle parameter in training data is crucial to a robust model.
-In the tradition lens group, variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
-Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size.
-However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process.
-The optical lens group yields similar results except the distance group.
-As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
 

### 2020-08-15 design.tex
10.5pages

@@
 
-\subsection{Design Principal}
+\subsection{Design Principle}
 To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
@@
 \begin{itemize}
-    \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers.
-All input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
-Another important feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
+    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
+The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
     \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution.
 At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
-    \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are performed individually for each image (or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power.
-This trait also enables the same network to adapt any number of input images.
-On one hand, this gives our model the ability to adapt to the uncertainty of the number of available images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Figure~\ref{illustration_of_system}.
+    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters.
+This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames.
+Furthermore, this allows variations in the number of input images.
     \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results.
 The frequent introduction of input images is designed to mitigate this challenge.
-Also, our model can learn correlations between certain features and strokes from the training data, decomposing the SR problem and making it a lot less challenging.
-We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalances of data.
-The loss functions in training is also redesigned.
-The mean square error (MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels.
-Our solution is putting a weight on each pixel before applying weighted MSE.
+Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE.
 Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights.

### 2020-08-15 evaluation.tex
10.5pages

@@
 We evaluate the performance of the network model in different training and testing conditions.
-We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
+We perform the following experiments with two Custom Off-The-Shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
 The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.
@@
 
-In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images.
+In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images.
 The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}.
-Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition (OCR) services to evaluate the accuracy.
+Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy.
 The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
@@
 
-This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens in both day and night time.
-The PSNR is higher than 10 as well.
-OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs.
-For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical lens.
-The performance is relatively consistent in both day and night time.
-Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
-
-In the optical zoom group, the accuracy of the model dropped drastically at 7m distance.
-Increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.).
+This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens and at 6m with optical lens.
+Performances are relatively consistent in both day and night time, while increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.).
 It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.
@@
 The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}.
+We can observe that the model performs best in daytime and at closer distances.
 For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens.
@@
 
-We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability.
-Also, the model performs better at closer distances.
-As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease.
-Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.
 \begin{figure}[!t]

### 2020-08-15 implementation.tex
change reallife fig
cl
10.5pages

@@
 
-\subsection{Data Collection}
-\label{sec-experiment-setting}
-
-In our experiment, we are forced to collect the training dataset on our own instead of using public datasets.
-Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing.
-Modern network architectures work with naturally obtained images, e.g.
+In our experiment, we are forced to collect the training dataset on our own instead of using public datasets, as there is no publicly available image dataset built for shoulder-surfing to the best of our knowledge, and because of the uniqueness of our application, i.e.
+blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly avaliable substitudes.
+%Modern network architectures work with naturally obtained images, e.g.
 ordinary photos, satellite images, scanned documents, YouTube videos, etc.
@@
 
-The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network.
-We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them.
-Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model.
-When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours).
-There is no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data.
+%Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model.
  %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
 
-Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset.
-However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
- \begin{figure}
-     \centering
-     \subfigure[input from same environment]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
-         \label{fig-train-single-1}
-         }
-     \subfigure[output of (a)]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
-         \label{fig-train-single-2}
-         }
-     \subfigure[input from different environment]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
-         \label{fig-train-single-3}
-         }
-     \subfigure[output of (c)]{
-         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
-         \label{fig-train-single-4}
-         }
-    % \subfigure[ground truth]{
-     %    \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
-      %   \label{fig-train-single-5}
-       %  }
-        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
-        \label{fig-train-single}
-\end{figure}
-
 \subsection{Experiment Setting}
-As a result of these observations, we have to collect images in varied environments.
+\label{sec-experiment-setting}
 Our experiment consists of 2 smartphones, one for the attacker and one the victim.
 Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming.
-Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation.
-An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos.
-Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture.
-The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets.
+Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation.
+An app runs inside the attacker's phone, taking photos in burst mode repeatedly (20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors.
+The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets.
 As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters.
-
-As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker.
-We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones.
-The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees.
-We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection.
-Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
+Screenshots were taken in the victim's phone as ground truth for training and evaluation.
 An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/setup.pdf}
-    \caption{Illustration of our experimental setting (Distance between phones is shortened for demonstration).}
+	\includegraphics[width=0.46\textwidth]{pic/setup.pdf}
+    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
 	\label{illustration_of_system}
@@
 
-The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.).
-We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter.
-The position of the phones is also a crucial factor in this parameter, and we avoid extreme settings, e.g.
-having the sunlight directly shining on the screen.
-We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels).
+The data was collected at different times of the day and night, with different illumination and at different positions and angles(tilting no more than 30 degrees).
+We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels), modifying these environmental parameters every 2,000 images.
 This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.
@@
 Thus, the specifications of our model are only for reference and may not work when reproduced on another phone.
+Also, we may need to repeat the data collection and training phases when switching to another phone model.
 
@@
 As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9x9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.
-
-\subsection{Training Process}
-Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming.
-Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset.
-The model should be able to handle this task easily.
-After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters.
-We add a small percentage of image data from another similar experiment setting into the training data and resume training.
-When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections.
-Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result.
-This phenomenon can be mitigated with dropout and normalization layers.
-As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 1.8m and 1.2m range in the training process, the model fits 1.5m photos easily.
-After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.

### 2020-08-15 introduction.tex
change reallife fig
10.5pages

@@
 % introduce LPL asynchronous duty cycle media access
-Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day.
-As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing''.
-Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}.
-For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment.
+Smartphones have become a necessity in our lives, and privacy concerns have consequently arisen.
+We often worry about nearby parties peeking at our screen, namely ``shoulder surfing''.
+Massive efforts have been made to shield users against this threat~\cite{wiedenbeck2006design,papadopoulos2017illusionpin,kumar2007reducing}, but this threat itself is somewhat understudied in comparison.
+In our opinion, the common threat model of an attacker with his/her naked eye is outdated, as with the groundbreaking developments in smartphones and neural networks, we should have considered the possibility that the shoulder surfing attacker is looking through his smartphone's lenses and even equipped with super resolution (SR) algorithms, which is already in use in HUAWEI's phones.
+In our work we'll present an up-to-date threat model as a reference for future works of screen privacy protection.
 
-% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm.
-The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games.
-Besides, specially designed equipment are not a necessity for the shoulder surfing attack.
+\textbf{Motivation.} Although it's pointed out by Eiband~\cite{eiband2017understanding} that in most occations the shoulder surfer means no harm and merely takes several peeks out of curiosity, we argue that a mere stranger can hardly do any harm, and it is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can really utilize the stolen information and should be the primary object of our defenses.
+%The attacker can even be our children stealing electronic payment passwords and spending huge sums in their games~\cite{2017childsteal}. 
+The argument goes the same with smartphones---although uncommon, the utilization of this commonly avaliable equipment can deal much greater harm with longer attacking range and ability of preserving evidence.
+For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
+The privacy concerns have been exacerbated with the rapidly developed mobile camera module these years.
+Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
+Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second, enabling the usage of multi-frame super resolution (SR) algorithms to further improve the shoulder surfing range.
 
-The privacy concerns however have been exacerbated with the rapidly developed mobile camera module these years.
-Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
-Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second.
-Given the commercial smartphone, the attacker can record the information reliably for propagating.
-And more images mean more recorded information of the victim.
-For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
-To gain vital data more stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.
-
-% In this present era where the leakage of a password and the disclosure of correspondence of public figures can cause great damage to the victim, we believe that it's imminent to recall attention on this new privacy threat and propose the corresponding standard of screen protection based on modern circumstances.
-
-Unfortunately, none of existing work can mitigate this new threat model.
-Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}.
-All of these methods however require the additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios.
-Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios.
+Unfortunately, none of existing works on screen privacy protection have considered the presence of modern mobile phone cameras and SR algorithms.
+Neumerous defense mechanisms have been proposed, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}, but the additional deployment cost and interaction complexity keeps them from being widely deployed\cite{Chun2019Keep}.
 Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new threat model and propose corresponding countermeasure for modern circumstances.
@@
     \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
-	\label{illustration_of_system}
+	\label{overview}
 \end{figure}
@@
 \noindent
-\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
-While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone and zooms in on the victim's screen.
-Then he can take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and process them with a multi-frame SR technique to generate a high-resolution result.
+\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
+While the victim's reading private information in public, the attacker uses his commercial smartphone to take 10 to 20 snapshots rapidly of his screen in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
 The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously, not missing any detail.
@@
 
-\begin{itemize}[leftmargin=*]
+\begin{itemize}
   \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing.
 It can be further exacerbated by straining the magnification of the smartphone lenses.
-Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts as Figure~\ref{illustration_of_system} shows, requiring a reliable ``reconstruction'' than ``interpolation''.
+Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts as Figure~\ref{overview} shows, requiring a reliable ``reconstruction'' than ``interpolation''.
 Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
@@
 Consequently, it cannot only require a more precise network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 snapshots.
-  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct complex characters with multiple strokes, such as Chinese characters shown in Figure~\ref{illustration_of_system}.
+  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct complex characters with multiple strokes, such as Chinese characters shown in Figure~\ref{overview}.
 Composed of multiple strokes, characters are distributed discretely in the pixel-wise snapshot and different with other entities (e.g., faces and natural objects), rendering unique challenges.
@@
 \textbf{Contributions.} This paper makes the following contributions:
-\begin{itemize}[leftmargin=*]
+\begin{itemize}
   \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones.

### 2020-08-15 related_work.tex
cl
10.5pages

@@
 \label{sec-related-work}
+
+\subsection{Shoulder Surfing}
+With the arrival of the information era, privacy issues are becoming increasingly prominent.
+Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}.
+To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
+Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding} ~\cite{wiedenbeck2006design}.
+Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
+
+However, compared to the various works focusing on defenses against shoulder surfing, the works studying and modelling this threat is sparse and outdated.
+Most of these works focus on scenarios where the attacker peeks at the phone with his/her naked eye, performing experiments or conducting surveys to research this threat.
+Eiband et al.~\cite{eiband2017understanding} conducted a user survey to investigate stories of shoulder surfing; Kwon et al.~\cite{kwon2013covert} designed a shoulder surfing approach called covert attentional shoulder surfing, and evaluated its success rates against PIN entry scenarios, presenting a powerful shoulder surfing threat model with the naked eye; and Schaub et al.~\cite{schaub2012password} evaluated shoulder surfing susceptibility, using Levenshtein distances and 7-point Likert scales to evaluate the accuracy and difficulties of shoulder surfing on different virtual keyboards.
+These works, however, lack quantitive modelling of this privacy threat, such as controlling the distances, illumination, angle, etc.
+to evaluate the vulnerability of screen privacy in different scenarios; and these works all focus on the unequipped attacker, so that their attack range is within 1 meter or even closer (where the attacker stands right behind or next to the victim), which is a barely practical scenario.
+
+To deal with the threat model of tool-assisted shoulder surfing, Maggi et al.
+designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}.
+However, the system contains only recognition algorithms, lacking SR processors to enhance the quality of the image, so that it can only function when the attacker is standing at close range.
+By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
+Evaluations demonstrate its feasibility and privacy concerns in our daily life.
+We also performed thorough evaluations of our threat model, measuring its abilities with various environment parameters.
+To the best of our knowledge, we are the first work to design and model the new form of shoulder surfing attack with the assistance of smartphones and multi-frame SR algorithms.
 \begin{table}[t]
@@
 
-\subsection{Shoulder Surfing}
-With the arrival of the information era, privacy issues are becoming increasingly prominent.
-Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}.
-To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
-Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding} ~\cite{wiedenbeck2006design}.
-Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
-
-However, compared to the various works focusing on defenses against shoulder surfing, the works studying and modelling this threat is sparse and outdated.
-Most of these works focus on scenarios where the attacker peeks at the phone with his/hers naked eye, performing experiments or conducting surveys to research this threat.
-Eiband et al.~\cite{eiband2017understanding} conducted a user survey to investigate stories of shoulder surfing; Kwon et al.~\cite{kwon2013covert} designed a shoulder surfing approach called covert attentional shoulder surfing, and evaluated its success rates against PIN entry scenarios, presenting a powerful shoulder surfing threat model with the naked eye; and Schaub et al.~\cite{schaub2012password} evaluated shoulder surfing susceptibility, using Levenshtein distances and 7-point Likert scales to evaluate the accuracy and difficulties of shoulder surfing on different virtual keyboards.
-These works, however, lack quantitive modelling of this privacy threat, such as controlling the distances, illumination, angle, etc.
-to evaluate the vulnerability of screen privacy in different scenarios; and these works all focus on the unequipped attacker, so that their attack range is within 1 meter or even closer (where the attacker stands right behind or next to the victim), which is a barely practical scenario.
-
-To deal with the threat model of tool-assisted shoulder surfing, Maggi et al.
-designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}.
-However, the system contains only recognition algorithms, lacking SR processors to enhance the quality of the image, so that it can only function when the attacker is standing at close range.
-By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
-Evaluations demonstrate its feasibility and privacy concerns in our daily life.
-We also performed thorough evaluations of our threat model, measuring its abilities with various environment parameters.
-To the best of our knowledge, we are the first work to design and model the new form of shoulder surfing attack with the assistance of smartphones and multi-frame SR algorithms.
-
 \subsection{Super Resolution}
@@
 To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input.
-Then the sequentially and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
-% modifying the 2d convolution layers to 3d convolution~\cite{caballero2017real}, 
-we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
+Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
+we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
 For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures.
@@
 And they achieve limited performance, shown in Table~\ref{tbl:comparison}.
-% These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.

### 2020-08-15 system_overview.tex
10.5pages

@@
 In this way, we generate upscaled image segments of all the characters on the target screen.
-The three calculation processes (Alignment, Adjustment, Processing) runs parallel to the input process, so that once a batch of input images is available, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
+The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that once a batch of input images is available, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
 
@@
      \includegraphics[width=0.48\textwidth]{./pic/workflow_cl.pdf}
-     \caption{Illustration of the workflow of \textsf{SRPeek}.}
+     \caption{Workflow of the \textsf{SRPeek} system.}
      \label{fig-workflow}

### 2020-08-15 pic_making/parameter_analysis.m

@@ -1,302 +1,0 @@
-% MAIN
-% Version 30-Nov-2019
-% Help on http://liecn.github.com
-clear;
-% clc;
-close all;
-%% Set Parameters for Transceivers
-wave_length = 299792458 / 5.825e9;
-sample_rate=1000;
-n_receivers = 2;    % Receiver count
-n_antennas = 3;    % Antenna count for each receiver
-n_subcarriers=30;
-
-%% Set Parameters for Data Description
-total_user=12;
-total_gait = 1;
-total_track = 6;
-total_instance = 4;
-
-lineA=["-",":","--",'-.'];
-% lineB=[left_color,"b","m","g"];
-lineC=["*","s","o","^","+","s"];
-lineS=["-.r","--m",":b"];
-%% Set Parameters for Loading Data
-data_root = './';
-
-fig=figure;
-set(fig,'DefaultAxesFontSize',18);
-set(fig,'DefaultAxesFontWeight','bold');
-%tailor the pdf
-left_color = [0.929 0.262 0.564];
-right_color = [0.439, 0.188, 0.627];
-set(fig,'defaultAxesColorOrder',[left_color; right_color]);
-
-set(fig,'PaperSize',[7.5 3.8]);
-
-%% data_1
-% x=[1,2,3,4];
-% psnr=[14.64,12.39,10.728,10.259];
-% ocr_acc=[100,98,95,94];
-% 
-% yyaxis left
-% b=bar(x,psnr,'FaceColor',left_color);
-% % b.CData=lineB(1);
-% ylabel('PSNR(db)'); % y label
-% ylim([0 25])
-% 
-% yyaxis right
-% h=plot(x,ocr_acc);
-% h.LineStyle=lineA(2);
-% h.Color=right_color;
-% h.Marker=lineC(2);
-% h.LineWidth=2;
-% ylabel('OCR Accuracy(%)'); % y label
-% ylim([85 100])
-% 
-% % legend(['Toward (-1)'],['Static (0)'])
-% xlabel('Day/Night & Distance(m)'); % x label
-% xticklabels({'D, 1.4','D, 1.8','N, 1.4','N, 1.8'})
-% % xlim([0 5])
-% title('')
-% %adjust the ratio
-% set(gcf,'WindowStyle','normal','Position', [200,200,640,360]);
[…]

### 2020-08-15 evaluation.tex

@@
 \subsection{Performance In Controlled Environments}
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
-    \hfill
-    \caption{Performance in the controlled environment using traditional lens and optical lens.}
-    \label{fig:control}
-\end{figure}
+% \begin{figure}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+%     \hfill
+%     \caption{Performance in the controlled environment using traditional lens and optical lens.}
+%     \label{fig:control}
+% \end{figure}
 
@@
 
-\begin{figure}[!t]
+% \begin{figure}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+%     \hfill
+%     \caption{Performance in the random environment using traditional lens and optical Lens.}
+%     \label{fig:control}
+% \end{figure}
+
+\begin{figure*}[!t]
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
     \hfill
-    \caption{Performance in the random environment using traditional lens and optical Lens.}
-    \label{fig:control}
-\end{figure}
-
-% \begin{figure*}[!t]
-%     \centering
-%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
-%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
-%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
-%     \hfill
-%     \caption{Performance for Adapting Ability and various processing images.}
-%     \label{fig:adapting}
-% \end{figure*}
+    \caption{Performance in (a)(b). the random as well as (c)(d). the controlled environment using traditional lens and optical lens.}
+    \label{fig:control_random}
+\end{figure*}
 
@@
 We evaluated the impact of fewer available images to the performance of the SR model.
-The results are shown in fig.~\ref{fig:number}.
+The results are shown in fig.~\ref{fig:number_adapting}.
 We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.
@@
 The optical lens group displayed a steady decent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
-\begin{figure}[!t]
+\begin{figure*}[!t]
     \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
     \hfill
-    \caption{Performance with fewer available images using traditional lens and optical lens.}
-    \label{fig:number}
-\end{figure}
+    \caption{Performance (a)(b). with fewer available images and (c)(d). for the adapting ability via traditional lens and optical lens.}
+    \label{fig:number_adapting}
+\end{figure*}
+
+% \begin{figure}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
+%     \hfill
+%     \caption{Performance with fewer available images using traditional lens and optical lens.}
+%     \label{fig:number}
+% \end{figure}
 
@@
 We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments.
-The results are shown in Figure~\ref{fig:adapting}.
+The results are shown in Figure~\ref{fig:number_adapting}.
 
@@
 As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
-\begin{figure}[!t]
-    \centering
-    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
-    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
-    \hfill
-    \caption{Performance for the adapting ability using traditional lens and optical lens.}
-    \label{fig:adapting}
-\end{figure}
+% \begin{figure}[!t]
+%     \centering
+%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
+%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
+%     \hfill
+%     \caption{Performance for the adapting ability using traditional lens and optical lens.}
+%     \label{fig:adapting}
+% \end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.46\textwidth]{pic/reallife.pdf}
+	\includegraphics[width=0.80\linewidth]{pic/reallife.pdf}
     \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}

### 2020-08-16 evaluation.tex
9 pages

@@
 Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy.
-The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.
+The traditional lens group is trained and tested at 1-2 meters distance, while the optical lens, 5-7.5 meters, where less than 5\% of the characters can be read with the naked eye.
 The PSNR and OCR results are shown in Fig.
@@
 This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens and at 6m with optical lens.
-Performances are relatively consistent in both day and night time, while increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.).
+Performances are relatively consistent in both day and night time, while increased distances mean less data, causing more artifacts(missing or misplaced strokes, etc.).
 It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.
@@
 We observed that variations in light and angle parameter in training data is crucial to a robust model.
-In the tradition lens group, variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters.
-Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size.
-However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process.
-The optical lens group yields similar results except the distance group.
-As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
+In the tradition lens group, the variations within 1 and 2 meters may have a smaller impact to the size of the characters
+ so that features extracted at one distance might still exist at another.
+ However, tilts and angles cause rotations and deformations and severely disturb the feature extraction process.
+The optical lens group yields similar results except at variations in distance.
+At a range of 6 meters, increases in distance leads to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
 % \begin{figure}[!t]
@@
 \subsection{Comparison with other architectures}
-We train and test other commonly used architectures with the same sets of data and evaluate their results.
-We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average.
+We train and test other widely used networks with the same sets of data and evaluate their results.
+We chose SRCNN, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average.
 We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR).
@@
 
-We build the system on smartphone and evaluate its performance in real-life environments (shown in Fig.~\ref{fig-reallife}).
-We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim.
-As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range.
+We build the system on smartphone and evaluate its performance in real-life scenarios (shown in Fig.~\ref{fig-reallife}).
+We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels, no optical zooming) for the attacker and a HUAWEI Mate8 smartphone for the victim, with the former ``1.8m daytime'' setting.
 We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model.
@@
 We conclude from the results that hand tremors can impact the performance of our system.
-Although the edges of the phone are notable marks for image alignment, small shifts in the sub-pixel level will cause blurriness in the results of the networks, lowering the readability of the outputs.
+Hand tremors can cause motion blur and erratic shifts in the sub-pixel level(after image alignment phase) and impact performance.
 
 \subsection{Success rate in different tasks}
-We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters.
-The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone.
-For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information (e.g.
-the name or the location mentioned in the text).
-For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric.
-In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible.
-Fewer photos will be available for each character but deciphering English characters is also easier than Chinese characters, and we trained a model specifically for each task (with the same neural network architecture), the training images containing only English characters and numbers (or only numbers for the PIN entry scenario).
+We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second).
+We use accuracy per character as evaluation metric.
+In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with same structure and different training data).
 The results are shown in Table~\ref{table-task}.
@@
 
-We prove from this experiment that our system functions normally in everyday scenarios and poses a threat to screen privacy.
+We conclude that \textsf{SRPeek} functions normally in everyday scenarios and poses a threat to screen privacy.
 
 \subsection{Perceived shoulder surfing susceptibility}
-We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenarios.
-The attacker will be sitting or standing behind the participant at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.
-None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing.
+We ask the participants to rate the perceived shoulder-surfing susceptibility after the experiment.
+The attacker sits or stands at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP.
+None of the participants reported suspicion of shoulder-surfing.
 We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

### 2020-08-16 introduction.tex
minor
cl
9 pages

@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{pic/illustration.pdf}
+	\includegraphics[width=0.80\linewidth]{pic/illustration.pdf}
     \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
@@
 
-\begin{itemize}
+\begin{itemize}[leftmargin=*]
   \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing.
@@
 \textbf{Summary of Evaluation Results.}
-Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming, or 6m on a phone with optical zooming in our experimental settings.
+Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming(hereafter referred as traditional lens), or 6m on a phone with optical zooming(hereafter referred as optical lens) in our experimental settings.
 \textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval.
@@
 \textbf{Contributions.} This paper makes the following contributions:
-\begin{itemize}
+\begin{itemize}[leftmargin=*]
   \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones.

### 2020-08-16 limitation_and_discussion.tex
cl
10.5pages
9 pages

@@
 We require a certain degree of image capturing and processing abilities of the attacker's phone, and we also expect the victim not to exert too much disturbance to the target phone.
+
 \vspace{1mm}
@@
 Heavily used phones also perform less than ideal when capturing images in burst mode.
-Also, when capturing images, the user needs to hold their phone as still as possible to avoid motion blur and assist image alignment.
-The user also has to keep a sharp focus on the target phone.
 
@@
 \textbf{Motion and Tremors}
-In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often.
-However, some users may tilt their phones during interactions---especially when typing with one hand.
-Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.
+In our experiment we assume the observed user will hold still his/her phone, and not making interactions too often.
+There might be extreme cases where frequent tilting of the screen may cause severe motion blur, degrading the result.
 
-Although our shoulder surfing system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
+Although \textsf{SRPeek} proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.
 

### 2020-08-16 related_work.tex
9 pages

@@
 Image SR is the process of reconstructing an image with a higher spatial resolution.
-Based on the structural pattern, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
+Based on the structural patternss, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
 Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip.
 These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms.
-And a variety of techniques have been proposed for the multi-image SR problem.
-And early works focus on the analysis of images in spatial or frequency domains.
-For example, the Shift-Add algorithm~\cite{farsiu2003robust} analyzes the spatial information by maximizing the pixel-wise possibility of high-resolution image from low-resolution images.
-Besides, approaches for the frequency domain rely on the Fourier transform of images.
-Assuming that the high-resolution scene is band-limited, these algorithms reconstruct high-frequency components from patterns of low-frequency components, removing bands of noise and blur effects simultaneously.
-Unfortunately, all SR techniques however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics~\cite{Youm2016Image}
-%\cl{more citation and table 1 row-3}
-. While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.
 
-Deep learning approaches can also be adopted for Super Resolution.
-For example, SRCNN~\cite{dong2015image} was designed using CNN by replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches.
-It however only focuses on single image SR, as the neural network accepts a single image as input.
-Besides, Generative Adversarial Networks (GAN) were also used to generate photo-realistic images~\cite{ledig2017photo}, with less artifacts and more genuine-looking details perceptible to the human eye.
-To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input.
-Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
-we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
-For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures.
+Recent works on SR are mostly based on Convolutional Neural Networks(CNN)~\cite{dong2015image} and Generative Adversarial Networks(GAN)~\cite{ledig2017photo}, the former often gets closer to ground truth while the latter generates less artifacts and is more pleasing to the human eye.
+To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real, kappeler2016video} use 3 dimensional convolutions to utilize sequentiality and consistency between adjacent frames.
+Some works also modify the dataflow among the network layers to merge neighboring frames~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
+For images without consistency or sequential information, like satellite images, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures.
 They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}.

### 2020-08-16 system_overview.tex
9 pages

@@
 \noindent
-\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen.
-Note that zooming is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if available, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range.
-This way information on the images will be more compact and easier to comprehend by neural networks.
+\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take several images(the number is freely adjustable) with burst mode of the target screen.
+As digital zooming do not put in any extra data, we'll only use maximum optical zooming(if exist) when photographing to reduce the workload of neural networks.
 
@@
 \noindent
-\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will occasionally shift slightly across time due to the movements of its inner mechanism.
+\textbf{Alignment:} The images are then aligned to mitigate tremors.
 Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
@@
 \noindent
-\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network.
-The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size (and the zooming of the camera lens in the Input phase will be adjusted accordingly).
+\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network.
+The characters are normally around 10x10 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.
 
@@
 \noindent
-\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo with our multi-frame super resolution network to generate 36x36 images (4x upscaling).
+\textbf{Processing:} As our SR network accepts only 9x9 patches, we will process all the 9x9 patches (with overlapping) among the input photo to generate 36x36 images (4x upscaling).
 The input is RGB colored, while the output, as we are not interested in color, is black and white.
-In this way, we generate upscaled image segments of all the characters on the target screen.
-The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that once a batch of input images is available, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.
+The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that the attacker can process a batch of images while the next batch is being collected simultaneously.
 
@@
 \noindent
-\textbf{Output:} The outputs of our SR network, the 36x36 patches, are then merged into a whole.
-The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result.
-As we only carve out the texts on the phone and process them, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration can be found in Fig.~\ref{illustration_of_system}).
+\textbf{Output:} The outputs of our SR network, the 36x36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image.
+As we only carve out the texts for processing, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration of the patched image can be found in Fig.~\ref{illustration_of_system}).
 
-These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds.
+These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of 1 to 2 seconds.
 At critical times requiring continuous monitoring so as not to miss transient display, e.g.
@@
   \centering
-     \includegraphics[width=0.48\textwidth]{./pic/workflow_cl.pdf}
+     \includegraphics[width=0.90\linewidth]{./pic/workflow_cl.pdf}
      \caption{Workflow of the \textsf{SRPeek} system.}

### 2020-08-17 design.tex
new version

@@
 \subsection{Design Principle}
-To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
+To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
 %\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
 
-\begin{itemize}
+\begin{itemize}[leftmargin=*]
     \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
@@
     \centering
-       \includegraphics[width=0.5\textwidth]{./pic/network.pdf}
+       \includegraphics[width=0.90\linewidth]{./pic/network.pdf}
        \caption{Core network architecture of SRPeek.}

### 2020-08-17 evaluation.tex
new version

@@
 We evaluate the performance of the network model in different training and testing conditions.
-We perform the following experiments with two Custom Off-The-Shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
+We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
 The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.
@@
     Scenarios & Home & Transport & Theater \\ \midrule
-    Baseline & 5\% & 0 & 0\\ 
+    Naked Eye & 5\% & 0 & 0\\ 
     \midrule
@@
     \midrule
-    Baseline & 5\% & 0 & 5\% & 5\%\\ 
+    Naked Eye & 5\% & 0 & 5\% & 5\%\\ 
     \midrule

### 2020-08-17 implementation.tex
9 pages
new version

@@
 Our experiment consists of 2 smartphones, one for the attacker and one the victim.
-Their distance is between 1 and 2 meters for traditional lenses (for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming.
+Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens.
 Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation.
-An app runs inside the attacker's phone, taking photos in burst mode repeatedly (20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors.
+An app runs inside the attacker's phone, taking photos in burst mode repeatedly (no more than 20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors.
 The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets.
@@
 	\centering
-	\includegraphics[width=0.46\textwidth]{pic/setup.pdf}
+	\includegraphics[width=0.80\linewidth]{pic/setup.pdf}
     \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
@@
 
-Our model accepts 20 images at a time, with a size of 9x9 pixels.
+Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the strokes level) at a time.
+We expect that characters should be upright(the attacker can simply spin his phone).
 The model consists of 5 blocks described in the previous section.
 In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output.
-the 20x32 feature maps are then merged horizontally with the max-min-average process, and the output is 5x32 channels.
-Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5x32 channels to form a dataflow of 6x32 channels for each one of the 20 images.
+the 20$\times$32 feature maps are then merged horizontally with the max-min-average process, and the output is 5$\times$32 channels.
+Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5$\times$32 channels to form a dataflow of 6$\times$32 channels for each one of the images.
 These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block.
-The kernels in each convolutional layer is 3x3.
+The kernels in each convolutional layer is 3$\times$3.
 We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks.
-A single 1x1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer.
+A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer.
 This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs.
-As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9x9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.
+As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

### 2020-08-17 introduction.tex
new version

@@
 \textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
-While the victim's reading private information in public, the attacker uses his commercial smartphone to take 10 to 20 snapshots rapidly of his screen in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
-The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously, not missing any detail.
+While the victim's reading private information in public, the attacker, given that he/she has line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
+The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously.
 Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them.

### 2020-08-17 system_overview.tex
new version

@@
 \textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network.
-The characters are normally around 10x10 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.
+The character size is normally 10 to 20 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.
 
@@
 \noindent
-\textbf{Processing:} As our SR network accepts only 9x9 patches, we will process all the 9x9 patches (with overlapping) among the input photo to generate 36x36 images (4x upscaling).
+\textbf{Processing:} As our SR network accepts only 9$\times$9 patches, we will process all the 9$\times$9 patches (with overlapping) among the input photo to generate 36$\times$36 images (4$\times$ upscaling).
 The input is RGB colored, while the output, as we are not interested in color, is black and white.
@@
 \noindent
-\textbf{Output:} The outputs of our SR network, the 36x36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image.
+\textbf{Output:} The outputs of our SR network, the 36$\times$36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image.
 As we only carve out the texts for processing, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration of the patched image can be found in Fig.~\ref{illustration_of_system}).

### 2020-08-17 abstract.tex
fix typos
newver

@@
 To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye.
-With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
+With the development of smartphones and super resolution (SR) techniques, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model.
 To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR.
-We implement \textsf{SPPeek} in Android.
+We implement \textsf{SRPeek} in Android.
 The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses.
-And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
+And it outperforms the state-of-the-art and fills the blank space of multi-image SR for shoulder surfing attack.
 \end{abstract}

### 2020-08-17 conclusion.tex
newver

@@
 \label{sec-conclusion}
-In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
+In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphones, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
 We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection.

### 2020-08-17 design.tex
newver

@@
 \subsection{Design Principle}
-To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
+To solve the challenges and outperform the state-of-the-art for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
 %\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
@@
 At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
-    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters.
+    \item \textbf{Inconsistency problem, model complexity, and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters.
 This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames.
@@
 The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer.
-As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.
+As mentioned before, in each layer images are processed separately, with the merging layers as revenue for communication, so that the output of each layer is correspondent to the input.
 We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer.
@@
 
-where (p,q) represent the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process.
+where (p,q) represents the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process.
 Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator.

### 2020-08-17 evaluation.tex
newver

@@
 % \end{figure*}
-We evaluate the performance of the network model in different training and testing conditions.
 We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras.
-The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.
+The telephoto camera possesses up to 5$\times$ optical zooming ability which we will utilize fully in our experiments.
+The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system.
 
@@
 
-In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images.
-The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}.
-Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy.
+In these experiments, we train and test the model with the images captured with exactly the same environment parameters.
+The results are shown in Fig.~\ref{fig-control-1} and ~\ref{fig-control-2}.
 The traditional lens group is trained and tested at 1-2 meters distance, while the optical lens, 5-7.5 meters, where less than 5\% of the characters can be read with the naked eye.
@@
 \subsection{Performance In Random Environments}
-We train the model with data captured in different environments, as mentioned before, and test its ability in other environments.
-The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}.
-We can observe that the model performs best in daytime and at closer distances.
-For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens.
-From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens.
+We train the model with data captured with varying environmental parameters, and test its ability at a new environment setting.
+The results are shown in Figure~\ref{fig-random-1} and ~\ref{fig-random-2}.
+The model can achieve an OCR accuracy above 85\% at 1.8m with traditional lens, and above 90\% at 6m with optical lens.
 This verifies the efficiency of our model for environment adaption.
@@
 \subsection{Performance with fewer available images}
-As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene.
-This design is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g.
-password entry, where only the last character of the password is visible.
+As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, which is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g.
+password entry.
+The previous experiments are all conducted with the ideal 20 frames per burst, but in the case study at Sec.~\ref{case-study} and real-life scenarios the attacker only gets to photograph when the screen display remains constant, so there might be fewer images available.
 We evaluated the impact of fewer available images to the performance of the SR model.
@@
 
-In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is available to rule out all possibilities of the displayed characters.
-The optical lens group displayed a steady decent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
+In the traditional lens group, the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is available to rule out all possibilities of the displayed characters.
+The optical lens group displayed a steady descent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
 \begin{figure*}[!t]
@@
 We observed that variations in light and angle parameter in training data is crucial to a robust model.
-In the tradition lens group, the variations within 1 and 2 meters may have a smaller impact to the size of the characters
+In the traditional lens group, the variations within 1 and 2 meters may have a smaller impact on the size of the characters
  so that features extracted at one distance might still exist at another.
@@
 The optical lens group yields similar results except at variations in distance.
-At a range of 6 meters, increases in distance leads to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
+At a range of 6 meters, increases in distance lead to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
 % \begin{figure}[!t]
@@
 We train and test other widely used networks with the same sets of data and evaluate their results.
-We chose SRCNN, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average.
-We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR).
+We chose SRCNN~\cite{dong2015image}, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average.
+We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR~\cite{kappeler2016video}).
 However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results.
@@
 
-The results show that Human can read 95\%, 85\% and 70\% contents in home, transport and theater while the OCR accuracy is 100\%, 10\% and 23\%.
-That verifies human can obtain the most parts of information from the peeking in various environments.
-In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads lower accuracy in transport and theater.
+The results show that humans can read 95\%, 85\% and 70\% contents in home, transport, and theater while the OCR accuracy is 100\%, 10\% and 23\%.
+That verifies that humans can obtain the most parts of information from the peeking in various environments.
+In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads to lower accuracy in transport and theater.
 
@@
 The user may freely interact with the phone when reading.
-We capture images of the phone at the same time to see how our system deal with a moving target screen.
+We capture images of the phone at the same time to see how our system deals with a moving target screen.
 The results are shown in Table~\ref{table-tremor}.
@@
 We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second).
-We use accuracy per character as evaluation metric.
-In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with same structure and different training data).
+We use accuracy per character as the evaluation metric.
+In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with the same structure and different training data).
 The results are shown in Table~\ref{table-task}.

### 2020-08-17 implementation.tex
newver

@@
 In our experiment, we are forced to collect the training dataset on our own instead of using public datasets, as there is no publicly available image dataset built for shoulder-surfing to the best of our knowledge, and because of the uniqueness of our application, i.e.
-blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly avaliable substitudes.
+blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly available substitutes.
 %Modern network architectures work with naturally obtained images, e.g.
@@
 Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens.
-Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation.
-An app runs inside the attacker's phone, taking photos in burst mode repeatedly (no more than 20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors.
+Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly from time to time, which can simulate a handheld situation.
+An app runs inside the attacker's phone, taking photos in burst mode repeatedly(20 images per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors.
 The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets.
@@
 The data was collected at different times of the day and night, with different illumination and at different positions and angles(tilting no more than 30 degrees).
-We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels), modifying these environmental parameters every 2,000 images.
+We collected 800,000 images in this way with a Redmi6A phone (which possesses a camera with 130 million pixels), modifying these environmental parameters every 2,000 images.
 This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.
@@
 \subsection{Model Specifications}
-It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features.
+It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (fewer pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features.
 Thus, the specifications of our model are only for reference and may not work when reproduced on another phone.
@@
 
-Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the strokes level) at a time.
+Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the level of strokes) at a time.
 We expect that characters should be upright(the attacker can simply spin his phone).
@@
 These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block.
-The kernels in each convolutional layer is 3$\times$3.
+The kernels in each convolutional layer are 3$\times$3.
 We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks.
 A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer.
-This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs.
+This model consists of approximately 200,000 parameters and complexity of about 400,000 FLOPs.
 As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

### 2020-08-17 introduction.tex
newver

@@
 Massive efforts have been made to shield users against this threat~\cite{wiedenbeck2006design,papadopoulos2017illusionpin,kumar2007reducing}, but this threat itself is somewhat understudied in comparison.
-In our opinion, the common threat model of an attacker with his/her naked eye is outdated, as with the groundbreaking developments in smartphones and neural networks, we should have considered the possibility that the shoulder surfing attacker is looking through his smartphone's lenses and even equipped with super resolution (SR) algorithms, which is already in use in HUAWEI's phones.
-In our work we'll present an up-to-date threat model as a reference for future works of screen privacy protection.
+In our opinion, the common threat model of an attacker with his/her naked eye is outdated, as with the groundbreaking developments in smartphones and neural networks, we should have considered the possibility that the shoulder surfing attacker is looking through his smartphone's lenses and even equipped with super resolution (SR) algorithms---already in use in several commercial phones---a feature rarely considered in previous works on shoulder surfing.
+In our work, we'll present an up-to-date threat model as a reference for future works of screen privacy protection.
 
-\textbf{Motivation.} Although it's pointed out by Eiband~\cite{eiband2017understanding} that in most occations the shoulder surfer means no harm and merely takes several peeks out of curiosity, we argue that a mere stranger can hardly do any harm, and it is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can really utilize the stolen information and should be the primary object of our defenses.
+\textbf{Motivation.} Although it's pointed out by Eiband~\cite{eiband2017understanding} that in most occasions the shoulder surfer means no harm and merely takes several peeks out of curiosity, we argue that a mere stranger can hardly do any harm, and it is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can utilize the stolen information and should be the primary object of our defenses.
 %The attacker can even be our children stealing electronic payment passwords and spending huge sums in their games~\cite{2017childsteal}. 
-The argument goes the same with smartphones---although uncommon, the utilization of this commonly avaliable equipment can deal much greater harm with longer attacking range and ability of preserving evidence.
-For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
-The privacy concerns have been exacerbated with the rapidly developed mobile camera module these years.
+The argument goes the same with smartphones---although uncommon, the utilization of this commonly available equipment can deal much greater harm with longer attacking range and ability to preserve evidence.
+For example, in a Senate hearing, the Justice Secretary of the Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
+The privacy concerns have been exacerbated by the rapidly developed mobile camera module these years.
 Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones.
-Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second, enabling the usage of multi-frame super resolution (SR) algorithms to further improve the shoulder surfing range.
+Hardware improvements in memory also allow the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second, enabling the usage of multi-frame super resolution (SR) algorithms to further improve the shoulder surfing range.
 
-Unfortunately, none of existing works on screen privacy protection have considered the presence of modern mobile phone cameras and SR algorithms.
-Neumerous defense mechanisms have been proposed, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}, but the additional deployment cost and interaction complexity keeps them from being widely deployed\cite{Chun2019Keep}.
-Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new threat model and propose corresponding countermeasure for modern circumstances.
+Unfortunately, none of the existing works about screen privacy protection has considered the presence of modern mobile phone cameras and SR algorithms.
+Numerous defense mechanisms have been proposed, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}, but the additional deployment cost and interaction complexity keep them from being widely deployed\cite{Chun2019Keep}.
+Given the ubiquitous usages of smartphones and serious damages to the victim, it is imminent to recall attention on this new threat model and propose corresponding countermeasure for modern circumstances.
 
@@
 \textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
-While the victim's reading private information in public, the attacker, given that he/she has line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
+While the victim's reading private information in public, the attacker, given that he/she has acquired line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
 The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously.
@@
 \begin{itemize}[leftmargin=*]
-  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing.
-It can be further exacerbated by straining the magnification of the smartphone lenses.
+  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without especially focusing.
+It can be further exacerbated by straining the magnification of smartphone lenses.
 Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts as Figure~\ref{overview} shows, requiring a reliable ``reconstruction'' than ``interpolation''.
@@
   On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames.
-Thus, it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for integration abilities of the SR algorithms than most other SR applications.
+Thus, it cannot be approximated as video clips using a constant, isotropic Gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for integration abilities of the SR algorithms than most other SR applications.
   % and the only chance of recovering the ground truth is to compare each photo against others. 
 %  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}.
-  \item \textbf{Super resolution with multiple snapshots.} To resolve the blurriness of input snapshots, a SR algorithm on a smartphone is required to recover the blurred contents.
-However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input.
+  \item \textbf{Super resolution with multiple snapshots.} To resolve the blurriness of input snapshots, an SR algorithm on a smartphone is required to recover the blurred contents.
+However, none of the existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input.
 Since smartphones can capture 10 snapshots per second in burst mode.
@@
 The reason has two folds.
-First, massive input leads to the increase in model complexity, making it unsuitable for mobile deployment.
+First, massive input leads to an increase in model complexity, making it unsuitable for mobile deployment.
 Second, the nature of our task requires to do pixel-wise correlation and comparison in the same coordinate with consecutive snapshots throughout our construction process.
-Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.
+Otherwise, we cannot tell if, for example, it is one stroke or two parallel strokes that are shown in these two darker pixels on this snapshot.
   \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server.
-Since 1) the latter requires a stable internet access, and 2) sending multiple snapshots across the Internet will consume time and bandwidth.
+Since 1) the latter requires stable internet access, and 2) sending multiple snapshots across the Internet will consume time and bandwidth.
 Given the required 10 to 20 snapshots to be processed for the ideal content recovery, we have 1-2 seconds as the minimum interval between each output frame, rendering a limited period for calculation with the restricted power and RAM.
-In case where the display on the target screen changes more frequently, fewer snapshots and less processing time are available for each scene.
+In the case where the display on the target screen changes more frequently, fewer snapshots and less processing time are available for each scene.
 Consequently, it cannot only require a more precise network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 snapshots.
   \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct complex characters with multiple strokes, such as Chinese characters shown in Figure~\ref{overview}.
-Composed of multiple strokes, characters are distributed discretely in the pixel-wise snapshot and different with other entities (e.g., faces and natural objects), rendering unique challenges.
+Composed of multiple strokes, characters are distributed discretely in the pixel-wise snapshot and different from other entities (e.g., faces and natural objects), rendering unique challenges.
 In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings.
@@
 \textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval.
-Our experiments in real life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.
+Our experiments in real-life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.
 
@@
   \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
-  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for content recognition, calling for the new privacy concern.
+  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-art for content recognition, calling for the new privacy concern.
 \end{itemize}
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing and SR techniques.
+Section~\ref{sec-related-work} describes the related work, especially the state-of-the-art for shoulder surfing and SR techniques.
 We present the system and network design in Section ~\ref{sec-system-overview} and ~\ref{sec-design}, followed by the implementation in Section~\ref{sec-implementation-and-training} and evaluation in Section ~\ref{sec-evaluation} and ~\ref{case-study}.

### 2020-08-17 limitation_and_discussion.tex
newver

@@
 \textbf{Processing Ability}
-To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time.
-As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
+To achieve best performance the user needs a phone with strong processing capabilities to run the neural network in real-time.
+As neural networks have been commonplace in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images in real-time.
 
@@
 \textbf{Motion and Tremors}
-In our experiment we assume the observed user will hold still his/her phone, and not making interactions too often.
+We assume the observed user will hold still his/her phone, and not making interactions too often.
 There might be extreme cases where frequent tilting of the screen may cause severe motion blur, degrading the result.
@@
 \textbf{Dynamic background.} Most multi-frame SR algorithms are designed based on the assumption that all input images are reflections of the same scene, and ours is not an exception.
-By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influential elements cannot be easily removed.
-These dots do not need to be distinct or colored same as the texts, as multi-frame SR algorithms function with tiny, pixel level differences between frames, making them especially sensitive to microscopic changes.
+By deploying a dynamic background behind the characters, such as tiny dots and lines traveling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influential elements cannot be easily removed.
+These dots do not need to be distinct or colored the same as the texts, as multi-frame SR algorithms function with tiny, pixel level differences between frames, making them especially sensitive to microscopic changes.
 
@@
 These methods fool the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
-Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remains to be implemented in our future work.
+Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remain to be implemented in our future work.

### 2020-08-17 related_work.tex
newver

@@
 To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
-Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding} ~\cite{wiedenbeck2006design}.
+Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding,wiedenbeck2006design}.
 Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm.
@@
 \subsection{Super Resolution}
-Image SR is the process of reconstructing an image with a higher spatial resolution.
+Image Super Resolution is the process of reconstructing an image with a higher spatial resolution.
 Based on the structural patternss, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
-Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip.
-These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms.
+Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots from a smartphone, successive images from a satellite, or adjacent frames on a video clip.
+These algorithms collect extra data from slight differences between these images, often exhibiting better performance than single-image SR algorithms.
 
 Recent works on SR are mostly based on Convolutional Neural Networks(CNN)~\cite{dong2015image} and Generative Adversarial Networks(GAN)~\cite{ledig2017photo}, the former often gets closer to ground truth while the latter generates less artifacts and is more pleasing to the human eye.
-To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real, kappeler2016video} use 3 dimensional convolutions to utilize sequentiality and consistency between adjacent frames.
+To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real,kappeler2016video} use 3 dimensional convolutions to utilize sequentiality and consistency between adjacent frames.
 Some works also modify the dataflow among the network layers to merge neighboring frames~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.

### 2020-08-17 system_overview.tex
newver

@@
 \noindent
-\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take several images(the number is freely adjustable) with burst mode of the target screen.
-As digital zooming do not put in any extra data, we'll only use maximum optical zooming(if exist) when photographing to reduce the workload of neural networks.
+\textbf{Input:} Under the guidance of the attacker, The smartphone will zoom in, take focus, and take several images(the number is freely adjustable) with burst mode of the target screen.
+As digital zooming does not put in any extra data, we'll only use maximum optical zooming(if exist) when photographing to reduce the workload of neural networks.
 
@@
 The input is RGB colored, while the output, as we are not interested in color, is black and white.
-The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that the attacker can process a batch of images while the next batch is being collected simultaneously.
+The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process so that the attacker can process a batch of images while the next batch is being collected simultaneously.
 

### 2020-08-17 conclusion.tex
typo

--- 2020-07-02 conclusion.tex
@@
 \label{sec-conclusion}
-In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
+In this work we designed a holistic system, \textsf{SRPeek}, for shoulder surfing on smartphones, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency.
 We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection.
-It is our wish that this work can stir discussion in the field of screen privacy protection and propagate defense mechanisms across critical mobile apps.
+It is our wish that this work can stir some discussion in the field of screen privacy protection and propagate defense mechanisms across critical mobile apps.
 
 The core of SRPeek is a specially designed multi-frame SR network.
-With its innovative architecture this network outperforms other algorithms of the same field in our application.
+With its innovative architecture, this network outperforms other algorithms of the same field in our application.
 The design ideology enables this network to process higher levels of data integration ability while keeping a low calculation profile, and we believe the elements of this design can be used in other applications with large amounts of data, such as natural language processing or anomaly detection.

### 2020-08-17 design.tex
typo

@@
 \begin{itemize}[leftmargin=*]
-    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
+    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture, all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network.
 The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
@@
        \includegraphics[width=0.90\linewidth]{./pic/network.pdf}
-       \caption{Core network architecture of SRPeek.}
+       \caption{Core network architecture of \textsf{SRPeek}.}
        \label{fig-system}

### 2020-08-17 evaluation.tex
typo

@@
 \subsection{Performance In Random Environments}
-We train the model with data captured with varying environmental parameters, and test its ability at a new environment setting.
+We train the model with data captured with varying environmental parameters and test its ability at a new environment setting.
 The results are shown in Figure~\ref{fig-random-1} and ~\ref{fig-random-2}.
@@
 
-\subsection{Performance with fewer available images}
+\subsection{Performance with Fewer Available Images}
 As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, which is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g.
@@
 The previous experiments are all conducted with the ideal 20 frames per burst, but in the case study at Sec.~\ref{case-study} and real-life scenarios the attacker only gets to photograph when the screen display remains constant, so there might be fewer images available.
-We evaluated the impact of fewer available images to the performance of the SR model.
+We evaluated the impact of fewer available images on the performance of the SR model.
 The results are shown in fig.~\ref{fig:number_adapting}.
@@
 \subsection{Adapting Ability}
-We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments.
+We train the model with fewer groups of data, exposing it to fewer variations of a certain environment parameter when training, and examine the model's performance in random environments.
 The results are shown in Figure~\ref{fig:number_adapting}.
 
-We observed that variations in light and angle parameter in training data is crucial to a robust model.
+We observed that variations in light and angle parameter in training data are crucial to a robust model.
 In the traditional lens group, the variations within 1 and 2 meters may have a smaller impact on the size of the characters
  so that features extracted at one distance might still exist at another.
- However, tilts and angles cause rotations and deformations and severely disturb the feature extraction process.
+ However, tilts and angles of the screen cause rotations and deformations and severely disturb the feature extraction process.
 The optical lens group yields similar results except at variations in distance.
@@
 
-\subsection{Comparison with other architectures}
+\subsection{Comparison with Other Architectures}
 We train and test other widely used networks with the same sets of data and evaluate their results.
-We chose SRCNN~\cite{dong2015image}, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average.
-We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR~\cite{kappeler2016video}).
+We chose SRCNN~\cite{dong2015image}, a commonly used single image SR network, applying it to every single image before merging the results by pixel-level average.
+We also used a multi-frame version of CNN with 3D convolutions, originally designed for video super resolution~\cite{kappeler2016video} (VideoSR).
 However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results.
@@
 
-We build the system on smartphone and evaluate its performance in real-life scenarios (shown in Fig.~\ref{fig-reallife}).
+We build the system on smartphones and evaluate its performance in real-life scenarios (shown in Fig.~\ref{fig-reallife}).
 We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels, no optical zooming) for the attacker and a HUAWEI Mate8 smartphone for the victim, with the former ``1.8m daytime'' setting.
@@
 
-The results show that humans can read 95\%, 85\% and 70\% contents in home, transport, and theater while the OCR accuracy is 100\%, 10\% and 23\%.
+The results show that humans can read 95\%, 85\%, and 70\% contents at home, transport, and theater while the OCR accuracy is 100\%, 10\%, and 23\%.
 That verifies that humans can obtain the most parts of information from the peeking in various environments.
@@
 
-\subsection{Influence of hand tremors}
-We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort (Handheld camera).
+\subsection{Influence of Hand Tremors}
+We ask 5 participants to capture images with handheld smartphones, keeping their hands still to their greatest effort (Handheld camera).
 We process these images and let them read the results.
@@
 
-We can see that with the existence of tremors, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human.
+We can see that with the existence of tremors, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and humans.
 We conclude from the results that hand tremors can impact the performance of our system.
@@
 \subsection{Success rate in different tasks}
-We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second).
+We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text messages, typing text messages, entering PIN, and typing passwords with numbers, English, and special characters(typing at 2 characters per second).
 We use accuracy per character as the evaluation metric.

### 2020-08-17 implementation.tex
typo

@@
 \label{sec-experiment-setting}
-Our experiment consists of 2 smartphones, one for the attacker and one the victim.
+Our experiment consists of 2 smartphones, one for the attacker and one for the victim.
 Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens.
@@
 A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer.
-This model consists of approximately 200,000 parameters and complexity of about 400,000 FLOPs.
+This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs.
 As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

### 2020-08-17 limitation_and_discussion.tex
typo

@@
 \label{sec-limitations-and-discussions}
-There are certain limitations of this work.
+There are certain limitations to this work.
 We require a certain degree of image capturing and processing abilities of the attacker's phone, and we also expect the victim not to exert too much disturbance to the target phone.
@@
 \textbf{Processing Ability}
-To achieve best performance the user needs a phone with strong processing capabilities to run the neural network in real-time.
+To achieve the best performance the user needs a phone with strong processing capabilities to run the neural network in real-time.
 As neural networks have been commonplace in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images in real-time.
@@
 By deploying a dynamic background behind the characters, such as tiny dots and lines traveling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influential elements cannot be easily removed.
-These dots do not need to be distinct or colored the same as the texts, as multi-frame SR algorithms function with tiny, pixel level differences between frames, making them especially sensitive to microscopic changes.
+These dots do not need to be distinct or colored the same as the texts, as multi-frame SR algorithms function with tiny, pixel-level differences between frames, making them especially sensitive to microscopic changes.
 
@@
 With front-facing cameras and face detection algorithms, the smartphone can constantly scan the surrounding passers-by and detect their gaze direction, and give a warning to the user when that gaze points at the screen.
-However, to the extent of our knowledge none of these works have included cameras into their detection scope, but we believe it's practical to implement such features.
+However, to the extent of our knowledge, none of these works have included cameras into their detection scope, but we believe it's practical to implement such features.
 
@@
 \textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network.
-These methods fool the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack.
+These methods fool the feature extraction phases of neural networks so that SRPeek is also vulnerable to this attack.
 Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remain to be implemented in our future work.

### 2020-08-17 related_work.tex
typo

@@
 With the arrival of the information era, privacy issues are becoming increasingly prominent.
-Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}.
+Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, has been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}.
 To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}.
@@
 
-However, compared to the various works focusing on defenses against shoulder surfing, the works studying and modelling this threat is sparse and outdated.
-Most of these works focus on scenarios where the attacker peeks at the phone with his/her naked eye, performing experiments or conducting surveys to research this threat.
+However, compared to the various works focusing on defenses against shoulder surfing, the works studying and modeling this threat are sparse and outdated.
+Most of these works focus on scenarios where the attacker peeks at the phone with his/her naked eye, performing experiments, or conducting surveys to research this threat.
 Eiband et al.~\cite{eiband2017understanding} conducted a user survey to investigate stories of shoulder surfing; Kwon et al.~\cite{kwon2013covert} designed a shoulder surfing approach called covert attentional shoulder surfing, and evaluated its success rates against PIN entry scenarios, presenting a powerful shoulder surfing threat model with the naked eye; and Schaub et al.~\cite{schaub2012password} evaluated shoulder surfing susceptibility, using Levenshtein distances and 7-point Likert scales to evaluate the accuracy and difficulties of shoulder surfing on different virtual keyboards.
-These works, however, lack quantitive modelling of this privacy threat, such as controlling the distances, illumination, angle, etc.
-to evaluate the vulnerability of screen privacy in different scenarios; and these works all focus on the unequipped attacker, so that their attack range is within 1 meter or even closer (where the attacker stands right behind or next to the victim), which is a barely practical scenario.
+These works, however, lack quantitive modeling of this privacy threat, such as controlling the distances, illumination, angle, etc.
+to evaluate the vulnerability of screen privacy in different scenarios, and these works all focus on the unequipped attacker, so that their attack range is within 1 meter or even closer (where the attacker stands right behind or next to the victim), which is a barely practical scenario.
 
 To deal with the threat model of tool-assisted shoulder surfing, Maggi et al.
-designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}.
+designed an automatic shoulder surfing threat model, observing the target smartphone with a digital camera~\cite{maggi2011poster}.
 However, the system contains only recognition algorithms, lacking SR processors to enhance the quality of the image, so that it can only function when the attacker is standing at close range.
-By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
+By tailoring and fusing the SR technology with smartphones possessing powerful lenses and processors, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.8-6m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}.
 Evaluations demonstrate its feasibility and privacy concerns in our daily life.
-We also performed thorough evaluations of our threat model, measuring its abilities with various environment parameters.
+We also performed thorough evaluations of our threat model, measuring its abilities with various environmental parameters.
 To the best of our knowledge, we are the first work to design and model the new form of shoulder surfing attack with the assistance of smartphones and multi-frame SR algorithms.
@@
 Image Super Resolution is the process of reconstructing an image with a higher spatial resolution.
-Based on the structural patternss, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
+Based on the structural patterns, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels.
 Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots from a smartphone, successive images from a satellite, or adjacent frames on a video clip.
@@
 
-Recent works on SR are mostly based on Convolutional Neural Networks(CNN)~\cite{dong2015image} and Generative Adversarial Networks(GAN)~\cite{ledig2017photo}, the former often gets closer to ground truth while the latter generates less artifacts and is more pleasing to the human eye.
-To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real,kappeler2016video} use 3 dimensional convolutions to utilize sequentiality and consistency between adjacent frames.
+Recent works on SR are mostly based on Convolutional Neural Networks(CNN)~\cite{dong2015image} and Generative Adversarial Networks(GAN)~\cite{ledig2017photo}, the former often gets closer to ground truth while the latter generates fewer artifacts and is more pleasing to the human eye.
+To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real,kappeler2016video} use 3-dimensional convolutions to utilize sequentiality and consistency between adjacent frames.
 Some works also modify the dataflow among the network layers to merge neighboring frames~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}.
 For images without consistency or sequential information, like satellite images, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures.
-They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}.
-Due of the extreme blurriness of snapshots, these methods cannot deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.
+They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single-image SR networks~\cite{8834937}.
+Due to the extreme blurriness of snapshots, these methods cannot deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames.
 And they achieve limited performance, shown in Table~\ref{tbl:comparison}.

### 2020-08-17 system_overview.tex
typo

@@
 \label{sec-system-overview} 
-We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
+We implemented a holistic system for shoulder surfing, with the neural network as the core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:
 
@@
 \textbf{Alignment:} The images are then aligned to mitigate tremors.
-Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images.
+Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them for reference to align our images.
 The images are also spun to make the text horizontal in the process.
@@
 At critical times requiring continuous monitoring so as not to miss transient display, e.g.
-password entering, the system can simply lengthen the input phase across that period and process the data afterwards.
+password entering, the system can simply lengthen the input phase across that period and process the data later.
 The workflow of our system is shown in Figure~\ref{fig-workflow}.

### 2020-08-17 evaluation.tex
typo

@@
 The telephoto camera possesses up to 5$\times$ optical zooming ability which we will utilize fully in our experiments.
-The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system.
+The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system(the latter using accuracy per character).
 
@@
 We evaluated the impact of fewer available images on the performance of the SR model.
-The results are shown in fig.~\ref{fig:number_adapting}.
+The results are shown in fig.~\ref{fig-image-tranditional-2} and fig.~\ref{fig-image-optical-2}.
 We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.
@@
 We train the model with fewer groups of data, exposing it to fewer variations of a certain environment parameter when training, and examine the model's performance in random environments.
-The results are shown in Figure~\ref{fig:number_adapting}.
+The results are shown in fig.~\ref{fig-adapt-tranditional} and fig.~\ref{fig-adapt-optical}.
 

### 2020-08-17 introduction.tex
typo

@@
 %The attacker can even be our children stealing electronic payment passwords and spending huge sums in their games~\cite{2017childsteal}. 
-The argument goes the same with smartphones---although uncommon, the utilization of this commonly available equipment can deal much greater harm with longer attacking range and ability to preserve evidence.
+The argument goes the same with cameras---although uncommon, the utilization of this commonly available equipment can deal greater harm with longer attacking range and ability to preserve evidence.
+Furthermore, the vulnerable information is not limited to passwords, as although biometrics and login services can conceal passwords from screens, leakage of texts and emails can also be perilous.
 For example, in a Senate hearing, the Justice Secretary of the Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.
@@
 \textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{overview}. 
-While the victim's reading private information in public, the attacker, given that he/she has acquired line of sight of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
+While the victim's reading private information in public, the attacker, given that he/she has acquired line of sight(LoS) of the screen, uses his commercial smartphone to take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and processes the images with multi-frame SR algorithms to generate a high-resolution result.
 The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously.
@@
 \noindent
-\textbf{Challenges.} Creating a powerful SR based shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time.
+\textbf{Challenges.} Creating a powerful SR based shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real-time.
 And we achieve \textsf{SRPeek} by overcoming four key challenges.

### 2020-08-17 system_overview.tex
typo

@@
 \noindent
-\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network.
+\textbf{Adjustment:} The patches differing from the background color of the screen will be carved out for processing to reduce the workload of the network.
 The character size is normally 10 to 20 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.
@@
 These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of 1 to 2 seconds.
-At critical times requiring continuous monitoring so as not to miss transient display, e.g.
+If continuous monitoring is required to avoid missing the transient display, e.g.
 password entering, the system can simply lengthen the input phase across that period and process the data later.
